\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\hypertarget{arctic-prompts}{%
\section{ARCTIC PROMPTS}\label{arctic-prompts}}

\hypertarget{author-of-the-danger-trail-philip-steels-etc.}{%
\subsection{Author of the danger trail, Philip Steels,
etc.}\label{author-of-the-danger-trail-philip-steels-etc.}}

Author of the danger trail, Philip Steels, etc.

\hypertarget{not-at-this-particular-case-tom-apologized-whittemore.}{%
\subsection{Not at this particular case, Tom, apologized
Whittemore.}\label{not-at-this-particular-case-tom-apologized-whittemore.}}

Not at this particular case, Tom, apologized Whittemore.

\hypertarget{for-the-twentieth-time-that-evening-the-two-men-shook-hands.}{%
\subsection{For the twentieth time that evening the two men shook
hands.}\label{for-the-twentieth-time-that-evening-the-two-men-shook-hands.}}

For the twentieth time that evening the two men shook hands.

\hypertarget{lord-but-im-glad-to-see-you-again-phil.}{%
\subsection{Lord, but I'm glad to see you again,
Phil.}\label{lord-but-im-glad-to-see-you-again-phil.}}

Lord, but I'm glad to see you again, Phil.

\hypertarget{will-we-ever-forget-it.}{%
\subsection{Will we ever forget it.}\label{will-we-ever-forget-it.}}

Will we ever forget it.

\hypertarget{god-bless-em-i-hope-ill-go-on-seeing-them-forever.}{%
\subsection{God bless 'em, I hope I'll go on seeing them
forever.}\label{god-bless-em-i-hope-ill-go-on-seeing-them-forever.}}

God bless 'em, I hope I'll go on seeing them forever.

\hypertarget{and-you-always-want-to-see-it-in-the-superlative-degree.}{%
\subsection{And you always want to see it in the superlative
degree.}\label{and-you-always-want-to-see-it-in-the-superlative-degree.}}

And you always want to see it in the superlative degree.

\hypertarget{gad-your-letter-came-just-in-time.}{%
\subsection{Gad, your letter came just in
time.}\label{gad-your-letter-came-just-in-time.}}

Gad, your letter came just in time.

\hypertarget{he-turned-sharply-and-faced-gregson-across-the-table.}{%
\subsection{He turned sharply, and faced Gregson across the
table.}\label{he-turned-sharply-and-faced-gregson-across-the-table.}}

He turned sharply, and faced Gregson across the table.

\hypertarget{im-playing-a-single-hand-in-what-looks-like-a-losing-game.}{%
\subsection{I'm playing a single hand in what looks like a losing
game.}\label{im-playing-a-single-hand-in-what-looks-like-a-losing-game.}}

I'm playing a single hand in what looks like a losing game.

\hypertarget{if-i-ever-needed-a-fighter-in-my-life-i-need-one-now.}{%
\subsection{If I ever needed a fighter in my life I need one
now.}\label{if-i-ever-needed-a-fighter-in-my-life-i-need-one-now.}}

If I ever needed a fighter in my life I need one now.

\hypertarget{gregson-shoved-back-his-chair-and-rose-to-his-feet.}{%
\subsection{Gregson shoved back his chair and rose to his
feet.}\label{gregson-shoved-back-his-chair-and-rose-to-his-feet.}}

Gregson shoved back his chair and rose to his feet.

\hypertarget{he-was-a-head-shorter-than-his-companion-of-almost-delicate-physique.}{%
\subsection{He was a head shorter than his companion, of almost delicate
physique.}\label{he-was-a-head-shorter-than-his-companion-of-almost-delicate-physique.}}

He was a head shorter than his companion, of almost delicate physique.

\hypertarget{now-youre-coming-down-to-business-phil-he-exclaimed.}{%
\subsection{Now you're coming down to business, Phil, he
exclaimed.}\label{now-youre-coming-down-to-business-phil-he-exclaimed.}}

Now you're coming down to business, Phil, he exclaimed.

\hypertarget{its-the-aurora-borealis.}{%
\subsection{It's the aurora borealis.}\label{its-the-aurora-borealis.}}

It's the aurora borealis.

\hypertarget{theres-fort-churchill-a-rifle-shot-beyond-the-ridge-asleep.}{%
\subsection{There's Fort Churchill, a rifle-shot beyond the ridge,
asleep.}\label{theres-fort-churchill-a-rifle-shot-beyond-the-ridge-asleep.}}

There's Fort Churchill, a rifle-shot beyond the ridge, asleep.

\hypertarget{from-that-moment-his-friendship-for-belize-turns-to-hatred-and-jealousy.}{%
\subsection{From that moment his friendship for Belize turns to hatred
and
jealousy.}\label{from-that-moment-his-friendship-for-belize-turns-to-hatred-and-jealousy.}}

From that moment his friendship for Belize turns to hatred and jealousy.

\hypertarget{there-was-a-change-now.}{%
\subsection{There was a change now.}\label{there-was-a-change-now.}}

There was a change now.

\hypertarget{i-followed-the-line-of-the-proposed-railroad-looking-for-chances.}{%
\subsection{I followed the line of the proposed railroad, looking for
chances.}\label{i-followed-the-line-of-the-proposed-railroad-looking-for-chances.}}

I followed the line of the proposed railroad, looking for chances.

\hypertarget{clubs-and-balls-and-cities-grew-to-be-only-memories.}{%
\subsection{Clubs and balls and cities grew to be only
memories.}\label{clubs-and-balls-and-cities-grew-to-be-only-memories.}}

Clubs and balls and cities grew to be only memories.

\hypertarget{it-fairly-clubbed-me-into-recognizing-it.}{%
\subsection{It fairly clubbed me into recognizing
it.}\label{it-fairly-clubbed-me-into-recognizing-it.}}

It fairly clubbed me into recognizing it.

\hypertarget{hardly-were-our-plans-made-public-before-we-were-met-by-powerful-opposition.}{%
\subsection{Hardly were our plans made public before we were met by
powerful
opposition.}\label{hardly-were-our-plans-made-public-before-we-were-met-by-powerful-opposition.}}

Hardly were our plans made public before we were met by powerful
opposition.

\hypertarget{a-combination-of-canadian-capital-quickly-organized-and-petitioned-for-the-same-privileges.}{%
\subsection{A combination of Canadian capital quickly organized and
petitioned for the same
privileges.}\label{a-combination-of-canadian-capital-quickly-organized-and-petitioned-for-the-same-privileges.}}

A combination of Canadian capital quickly organized and petitioned for
the same privileges.

\hypertarget{it-was-my-reports-from-the-north-which-chiefly-induced-people-to-buy.}{%
\subsection{It was my reports from the north which chiefly induced
people to
buy.}\label{it-was-my-reports-from-the-north-which-chiefly-induced-people-to-buy.}}

It was my reports from the north which chiefly induced people to buy.

\hypertarget{i-was-about-to-do-this-when-cooler-judgment-prevailed.}{%
\subsection{I was about to do this when cooler judgment
prevailed.}\label{i-was-about-to-do-this-when-cooler-judgment-prevailed.}}

I was about to do this when cooler judgment prevailed.

\hypertarget{it-occurred-to-me-that-there-would-have-to-be-an-accounting.}{%
\subsection{It occurred to me that there would have to be an
accounting.}\label{it-occurred-to-me-that-there-would-have-to-be-an-accounting.}}

It occurred to me that there would have to be an accounting.

\hypertarget{to-my-surprise-he-began-to-show-actual-enthusiasm-in-my-favor.}{%
\subsection{To my surprise he began to show actual enthusiasm in my
favor.}\label{to-my-surprise-he-began-to-show-actual-enthusiasm-in-my-favor.}}

To my surprise he began to show actual enthusiasm in my favor.

\hypertarget{robbery-bribery-fraud}{%
\subsection{Robbery, bribery, fraud,}\label{robbery-bribery-fraud}}

Robbery, bribery, fraud,

\hypertarget{their-forces-were-already-moving-into-the-north-country.}{%
\subsection{Their forces were already moving into the north
country.}\label{their-forces-were-already-moving-into-the-north-country.}}

Their forces were already moving into the north country.

\hypertarget{i-had-faith-in-them.}{%
\subsection{I had faith in them.}\label{i-had-faith-in-them.}}

I had faith in them.

\hypertarget{they-were-three-hundred-yards-apart.}{%
\subsection{They were three hundred yards
apart.}\label{they-were-three-hundred-yards-apart.}}

They were three hundred yards apart.

\hypertarget{since-then-some-mysterious-force-has-been-fighting-us-at-every-step.}{%
\subsection{Since then some mysterious force has been fighting us at
every
step.}\label{since-then-some-mysterious-force-has-been-fighting-us-at-every-step.}}

Since then some mysterious force has been fighting us at every step.

\hypertarget{he-unfolded-a-long-typewritten-letter-and-handed-it-to-gregson.}{%
\subsection{He unfolded a long typewritten letter, and handed it to
Gregson.}\label{he-unfolded-a-long-typewritten-letter-and-handed-it-to-gregson.}}

He unfolded a long typewritten letter, and handed it to Gregson.

\hypertarget{men-of-seldens-stamp-dont-stop-at-women-and-children.}{%
\subsection{Men of Selden's stamp don't stop at women and
children.}\label{men-of-seldens-stamp-dont-stop-at-women-and-children.}}

Men of Selden's stamp don't stop at women and children.

\hypertarget{he-stopped-and-philip-nodded-at-the-horrified-question-in-his-eyes.}{%
\subsection{He stopped, and Philip nodded at the horrified question in
his
eyes.}\label{he-stopped-and-philip-nodded-at-the-horrified-question-in-his-eyes.}}

He stopped, and Philip nodded at the horrified question in his eyes.

\hypertarget{she-turned-in-at-the-hotel.}{%
\subsection{She turned in at the
hotel.}\label{she-turned-in-at-the-hotel.}}

She turned in at the hotel.

\hypertarget{i-was-the-only-one-who-remained-sitting.}{%
\subsection{I was the only one who remained
sitting.}\label{i-was-the-only-one-who-remained-sitting.}}

I was the only one who remained sitting.

\hypertarget{well-have-to-watch-our-chances.}{%
\subsection{We'll have to watch our
chances.}\label{well-have-to-watch-our-chances.}}

We'll have to watch our chances.

\hypertarget{the-ship-should-be-in-within-a-week-or-ten-days.}{%
\subsection{The ship should be in within a week or ten
days.}\label{the-ship-should-be-in-within-a-week-or-ten-days.}}

The ship should be in within a week or ten days.

\hypertarget{i-suppose-you-wonder-why-she-is-coming-up-here.}{%
\subsection{I suppose you wonder why she is coming up
here.}\label{i-suppose-you-wonder-why-she-is-coming-up-here.}}

I suppose you wonder why she is coming up here.

\hypertarget{meanwhile-ill-go-out-to-breathe-a-spell.}{%
\subsection{Meanwhile I'll go out to breathe a
spell.}\label{meanwhile-ill-go-out-to-breathe-a-spell.}}

Meanwhile I'll go out to breathe a spell.

\hypertarget{how-could-he-explain-his-possession-of-the-sketch.}{%
\subsection{How could he explain his possession of the
sketch.}\label{how-could-he-explain-his-possession-of-the-sketch.}}

How could he explain his possession of the sketch.

\hypertarget{it-seemed-nearer-to-him-since-he-had-seen-and-talked-with-gregson.}{%
\subsection{It seemed nearer to him since he had seen and talked with
Gregson.}\label{it-seemed-nearer-to-him-since-he-had-seen-and-talked-with-gregson.}}

It seemed nearer to him since he had seen and talked with Gregson.

\hypertarget{her-own-betrayal-of-herself-was-like-tonic-to-philip.}{%
\subsection{Her own betrayal of herself was like tonic to
Philip.}\label{her-own-betrayal-of-herself-was-like-tonic-to-philip.}}

Her own betrayal of herself was like tonic to Philip.

\hypertarget{he-moved-away-as-quietly-as-he-had-come.}{%
\subsection{He moved away as quietly as he had
come.}\label{he-moved-away-as-quietly-as-he-had-come.}}

He moved away as quietly as he had come.

\hypertarget{the-girl-faced-him-her-eyes-shining-with-sudden-fear.}{%
\subsection{The girl faced him, her eyes shining with sudden
fear.}\label{the-girl-faced-him-her-eyes-shining-with-sudden-fear.}}

The girl faced him, her eyes shining with sudden fear.

\hypertarget{close-beside-him-gleamed-the-white-fangs-of-the-wolf-dog.}{%
\subsection{Close beside him gleamed the white fangs of the
wolf-dog.}\label{close-beside-him-gleamed-the-white-fangs-of-the-wolf-dog.}}

Close beside him gleamed the white fangs of the wolf-dog.

\hypertarget{he-looked-at-the-handkerchief-more-closely.}{%
\subsection{He looked at the handkerchief more,
closely.}\label{he-looked-at-the-handkerchief-more-closely.}}

He looked at the handkerchief more, closely.

\hypertarget{gregson-was-asleep-when-he-re-entered-the-cabin.}{%
\subsection{Gregson was asleep when he re-entered the
cabin.}\label{gregson-was-asleep-when-he-re-entered-the-cabin.}}

Gregson was asleep when he re-entered the cabin.

\hypertarget{in-spite-of-their-absurdity-the-words-affected-philip-curiously.}{%
\subsection{In spite of their absurdity the words affected Philip
curiously.}\label{in-spite-of-their-absurdity-the-words-affected-philip-curiously.}}

In spite of their absurdity the words affected Philip curiously.

\hypertarget{the-lace-was-of-a-delicate-ivory-color-faintly-tinted-with-yellow.}{%
\subsection{The lace was of a delicate ivory color, faintly tinted with
yellow.}\label{the-lace-was-of-a-delicate-ivory-color-faintly-tinted-with-yellow.}}

The lace was of a delicate ivory color, faintly tinted with yellow.

\hypertarget{it-was-a-curious-coincidence.}{%
\subsection{It was a curious
coincidence.}\label{it-was-a-curious-coincidence.}}

It was a curious coincidence.

\hypertarget{suddenly-his-fingers-closed-tightly-over-the-handkerchief.}{%
\subsection{Suddenly his fingers closed tightly over the
handkerchief.}\label{suddenly-his-fingers-closed-tightly-over-the-handkerchief.}}

Suddenly his fingers closed tightly over the handkerchief.

\hypertarget{there-was-nothing-on-the-rock.}{%
\subsection{There was nothing on the
rock.}\label{there-was-nothing-on-the-rock.}}

There was nothing on the rock.

\hypertarget{philip-stood-undecided-his-ears-strained-to-catch-the-slightest-sound.}{%
\subsection{Philip stood undecided, his ears strained to catch the
slightest
sound.}\label{philip-stood-undecided-his-ears-strained-to-catch-the-slightest-sound.}}

Philip stood undecided, his ears strained to catch the slightest sound.

\hypertarget{pearces-little-eyes-were-fixed-on-him-shrewdly.}{%
\subsection{Pearce's little eyes were fixed on him
shrewdly.}\label{pearces-little-eyes-were-fixed-on-him-shrewdly.}}

Pearce's little eyes were fixed on him shrewdly.

\hypertarget{i-have-no-idea-replied-philip.}{%
\subsection{I have no idea, replied
Philip.}\label{i-have-no-idea-replied-philip.}}

I have no idea, replied Philip.

\hypertarget{i-came-for-information-more-out-of-curiosity-than-anything-else.}{%
\subsection{I came for information more out of curiosity than anything
else.}\label{i-came-for-information-more-out-of-curiosity-than-anything-else.}}

I came for information more out of curiosity than anything else.

\hypertarget{his-immaculate-appearance-was-gone.}{%
\subsection{His immaculate appearance was
gone.}\label{his-immaculate-appearance-was-gone.}}

His immaculate appearance was gone.

\hypertarget{anyway-no-one-saw-her-like-that.}{%
\subsection{Anyway, no one saw her like
that.}\label{anyway-no-one-saw-her-like-that.}}

Anyway, no one saw her like that.

\hypertarget{philip-snatched-at-the-letter-which-gregson-held-out-to-him.}{%
\subsection{Philip snatched at the letter which Gregson held out to
him.}\label{philip-snatched-at-the-letter-which-gregson-held-out-to-him.}}

Philip snatched at the letter which Gregson held out to him.

\hypertarget{the-men-stared-into-each-others-face.}{%
\subsection{The men stared into each other's
face.}\label{the-men-stared-into-each-others-face.}}

The men stared into each other's face.

\hypertarget{yes-it-was-a-man-who-asked-a-stranger.}{%
\subsection{Yes, it was a man who asked, a
stranger.}\label{yes-it-was-a-man-who-asked-a-stranger.}}

Yes, it was a man who asked, a stranger.

\hypertarget{the-fourth-and-fifth-days-passed-without-any-developments.}{%
\subsection{The fourth and fifth days passed without any
developments.}\label{the-fourth-and-fifth-days-passed-without-any-developments.}}

The fourth and fifth days passed without any developments.

\hypertarget{they-closed-now-until-his-fingers-were-like-cords-of-steel.}{%
\subsection{They closed now until his fingers were like cords of
steel.}\label{they-closed-now-until-his-fingers-were-like-cords-of-steel.}}

They closed now until his fingers were like cords of steel.

\hypertarget{he-saw-jeanne-falter-for-a-moment.}{%
\subsection{He saw Jeanne falter for a
moment.}\label{he-saw-jeanne-falter-for-a-moment.}}

He saw Jeanne falter for a moment.

\hypertarget{surely-i-will-excuse-you-she-cried.}{%
\subsection{Surely I will excuse you, she
cried.}\label{surely-i-will-excuse-you-she-cried.}}

Surely I will excuse you, she cried.

\hypertarget{in-a-flash-philip-followed-its-direction.}{%
\subsection{In a flash Philip followed its
direction.}\label{in-a-flash-philip-followed-its-direction.}}

In a flash Philip followed its direction.

\hypertarget{it-was-his-intention-to-return-to-eileen-and-her-father.}{%
\subsection{It was his intention to return to Eileen and her
father.}\label{it-was-his-intention-to-return-to-eileen-and-her-father.}}

It was his intention to return to Eileen and her father.

\hypertarget{he-would-first-hunt-up-gregson-and-begin-his-work-there.}{%
\subsection{He would first hunt up Gregson and begin his work
there.}\label{he-would-first-hunt-up-gregson-and-begin-his-work-there.}}

He would first hunt up Gregson and begin his work there.

\hypertarget{what-was-the-object-of-your-little-sensation.}{%
\subsection{What was the object of your little
sensation.}\label{what-was-the-object-of-your-little-sensation.}}

What was the object of your little sensation.

\hypertarget{but-who-was-eileens-double.}{%
\subsection{But who was Eileen's
double.}\label{but-who-was-eileens-double.}}

But who was Eileen's double.

\hypertarget{the-promoters-eyes-were-heavy-with-little-puffy-bags-under-them.}{%
\subsection{The promoter's eyes were heavy, with little puffy bags under
them.}\label{the-promoters-eyes-were-heavy-with-little-puffy-bags-under-them.}}

The promoter's eyes were heavy, with little puffy bags under them.

\hypertarget{and-now-down-there-eileen-was-waiting-for-him.}{%
\subsection{And now, down there, Eileen was waiting for
him.}\label{and-now-down-there-eileen-was-waiting-for-him.}}

And now, down there, Eileen was waiting for him.

\hypertarget{there-has-been-a-change-she-interrupted-him.}{%
\subsection{There has been a change, she interrupted
him.}\label{there-has-been-a-change-she-interrupted-him.}}

There has been a change, she interrupted him.

\hypertarget{the-gray-eyes-faltered-the-flush-deepened.}{%
\subsection{The gray eyes faltered; the flush
deepened.}\label{the-gray-eyes-faltered-the-flush-deepened.}}

The gray eyes faltered; the flush deepened.

\hypertarget{it-is-the-fire-partly-she-said.}{%
\subsection{It is the fire, partly, she
said.}\label{it-is-the-fire-partly-she-said.}}

It is the fire, partly, she said.

\hypertarget{then-and-at-supper-he-tried-to-fathom-her.}{%
\subsection{Then, and at supper, he tried to fathom
her.}\label{then-and-at-supper-he-tried-to-fathom-her.}}

Then, and at supper, he tried to fathom her.

\hypertarget{it-was-a-large-canoe.}{%
\subsection{It was a large canoe.}\label{it-was-a-large-canoe.}}

It was a large canoe.

\hypertarget{what-if-jeanne-failed-him.}{%
\subsection{What if Jeanne failed
him.}\label{what-if-jeanne-failed-him.}}

What if Jeanne failed him.

\hypertarget{what-if-she-did-not-come-to-the-rock.}{%
\subsection{What if she did not come to the
rock.}\label{what-if-she-did-not-come-to-the-rock.}}

What if she did not come to the rock.

\hypertarget{his-face-was-streaming-with-blood.}{%
\subsection{His face was streaming with
blood.}\label{his-face-was-streaming-with-blood.}}

His face was streaming with blood.

\hypertarget{a-shadow-was-creeping-over-pierres-eyes.}{%
\subsection{A shadow was creeping over Pierre's
eyes.}\label{a-shadow-was-creeping-over-pierres-eyes.}}

A shadow was creeping over Pierre's eyes.

\hypertarget{scarcely-had-he-uttered-the-name-when-pierres-closing-eyes-shot-open.}{%
\subsection{Scarcely had he uttered the name when Pierre's closing eyes
shot
open.}\label{scarcely-had-he-uttered-the-name-when-pierres-closing-eyes-shot-open.}}

Scarcely had he uttered the name when Pierre's closing eyes shot open.

\hypertarget{a-trickle-of-fresh-blood-ran-over-his-face.}{%
\subsection{A trickle of fresh blood ran over his
face.}\label{a-trickle-of-fresh-blood-ran-over-his-face.}}

A trickle of fresh blood ran over his face.

\hypertarget{death-had-come-with-terrible-suddenness.}{%
\subsection{Death had come with terrible
suddenness.}\label{death-had-come-with-terrible-suddenness.}}

Death had come with terrible suddenness.

\hypertarget{philip-bent-lower-and-stared-into-the-face-of-the-dead-man.}{%
\subsection{Philip bent lower, and stared into the face of the dead
man.}\label{philip-bent-lower-and-stared-into-the-face-of-the-dead-man.}}

Philip bent lower, and stared into the face of the dead man.

\hypertarget{he-made-sure-that-the-magazine-was-loaded-and-resumed-his-paddling.}{%
\subsection{He made sure that the magazine was loaded, and resumed his
paddling.}\label{he-made-sure-that-the-magazine-was-loaded-and-resumed-his-paddling.}}

He made sure that the magazine was loaded, and resumed his paddling.

\hypertarget{the-nightglow-was-treacherous-to-shoot-by.}{%
\subsection{The nightglow was treacherous to shoot
by.}\label{the-nightglow-was-treacherous-to-shoot-by.}}

The nightglow was treacherous to shoot by.

\hypertarget{the-singing-voice-approached-rapidly.}{%
\subsection{The singing voice approached
rapidly.}\label{the-singing-voice-approached-rapidly.}}

The singing voice approached rapidly.

\hypertarget{his-blood-grew-hot-with-rage-at-the-thought.}{%
\subsection{His blood grew hot with rage at the
thought.}\label{his-blood-grew-hot-with-rage-at-the-thought.}}

His blood grew hot with rage at the thought.

\hypertarget{he-went-down-in-midstream-searching-the-shadows-of-both-shores.}{%
\subsection{He went down in midstream, searching the shadows of both
shores.}\label{he-went-down-in-midstream-searching-the-shadows-of-both-shores.}}

He went down in midstream, searching the shadows of both shores.

\hypertarget{for-a-full-minute-he-crouched-and-listened.}{%
\subsection{For a full minute he crouched and
listened.}\label{for-a-full-minute-he-crouched-and-listened.}}

For a full minute he crouched and listened.

\hypertarget{he-had-barely-entered-this-when-he-saw-the-glow-of-a-fire.}{%
\subsection{He had barely entered this when he saw the glow of a
fire.}\label{he-had-barely-entered-this-when-he-saw-the-glow-of-a-fire.}}

He had barely entered this when he saw the glow of a fire.

\hypertarget{a-big-canvas-tent-was-the-first-thing-to-come-within-his-vision.}{%
\subsection{A big canvas tent was the first thing to come within his
vision.}\label{a-big-canvas-tent-was-the-first-thing-to-come-within-his-vision.}}

A big canvas tent was the first thing to come within his vision.

\hypertarget{perhaps-she-had-already-met-her-fate-a-little-deeper-in-the-forest.}{%
\subsection{Perhaps she had already met her fate a little deeper in the
forest.}\label{perhaps-she-had-already-met-her-fate-a-little-deeper-in-the-forest.}}

Perhaps she had already met her fate a little deeper in the forest.

\hypertarget{then-you-can-arrange-yourself-comfortably-among-these-robes-in-the-bow.}{%
\subsection{Then you can arrange yourself comfortably among these robes
in the
bow.}\label{then-you-can-arrange-yourself-comfortably-among-these-robes-in-the-bow.}}

Then you can arrange yourself comfortably among these robes in the bow.

\hypertarget{shall-i-carry-you.}{%
\subsection{Shall I carry you.}\label{shall-i-carry-you.}}

Shall I carry you.

\hypertarget{a-maddening-joy-pounded-in-his-brain.}{%
\subsection{A maddening joy pounded in his
brain.}\label{a-maddening-joy-pounded-in-his-brain.}}

A maddening joy pounded in his brain.

\hypertarget{you-must-sleep-he-urged.}{%
\subsection{You must sleep, he urged.}\label{you-must-sleep-he-urged.}}

You must sleep, he urged.

\hypertarget{you-you-would-not-keep-the-truth-from-me.}{%
\subsection{You, you would not keep the truth from
me.}\label{you-you-would-not-keep-the-truth-from-me.}}

You, you would not keep the truth from me.

\hypertarget{he-will-follow-us-soon.}{%
\subsection{He will follow us soon.}\label{he-will-follow-us-soon.}}

He will follow us soon.

\hypertarget{but-there-came-no-promise-from-the-bow-of-the-canoe.}{%
\subsection{But there came no promise from the bow of the
canoe.}\label{but-there-came-no-promise-from-the-bow-of-the-canoe.}}

But there came no promise from the bow of the canoe.

\hypertarget{she-was-sleeping-under-his-protection-as-sweetly-as-a-child.}{%
\subsection{She was sleeping under his protection as sweetly as a
child.}\label{she-was-sleeping-under-his-protection-as-sweetly-as-a-child.}}

She was sleeping under his protection as sweetly as a child.

\hypertarget{only-it-is-so-wonderful-so-almost-impossible-to-believe.}{%
\subsection{Only, it is so wonderful, so almost impossible to
believe.}\label{only-it-is-so-wonderful-so-almost-impossible-to-believe.}}

Only, it is so wonderful, so almost impossible to believe.

\hypertarget{the-emotion-which-she-had-suppressed-burst-forth-now-in-a-choking-sob.}{%
\subsection{The emotion which she had suppressed burst forth now in a
choking
sob.}\label{the-emotion-which-she-had-suppressed-burst-forth-now-in-a-choking-sob.}}

The emotion which she had suppressed burst forth now in a choking sob.

\hypertarget{if-you-only-could-know-how-i-thank-you.}{%
\subsection{If you only could know how I thank
you.}\label{if-you-only-could-know-how-i-thank-you.}}

If you only could know how I thank you.

\hypertarget{he-waded-into-the-edge-of-the-water-and-began-scrubbing-himself.}{%
\subsection{He waded into the edge of the water and began scrubbing
himself.}\label{he-waded-into-the-edge-of-the-water-and-began-scrubbing-himself.}}

He waded into the edge of the water and began scrubbing himself.

\hypertarget{do-you-know-that-you-are-shaking-my-confidence-in-you.}{%
\subsection{Do you know that you are shaking my confidence in
you.}\label{do-you-know-that-you-are-shaking-my-confidence-in-you.}}

Do you know that you are shaking my confidence in you.

\hypertarget{much-replied-jeanne-as-tersely.}{%
\subsection{Much, replied Jeanne, as
tersely.}\label{much-replied-jeanne-as-tersely.}}

Much, replied Jeanne, as tersely.

\hypertarget{instead-he-joined-her-and-they-ate-like-two-hungry-children.}{%
\subsection{Instead, he joined her; and they ate like two hungry
children.}\label{instead-he-joined-her-and-they-ate-like-two-hungry-children.}}

Instead, he joined her; and they ate like two hungry children.

\hypertarget{he-was-wounded-in-the-arm.}{%
\subsection{He was wounded in the
arm.}\label{he-was-wounded-in-the-arm.}}

He was wounded in the arm.

\hypertarget{i-suppose-you-picked-that-lingo-up-among-the-indians.}{%
\subsection{I suppose you picked that lingo up among the
Indians.}\label{i-suppose-you-picked-that-lingo-up-among-the-indians.}}

I suppose you picked that lingo up among the Indians.

\hypertarget{her-words-sent-a-strange-chill-through-philip.}{%
\subsection{Her words sent a strange chill through
Philip.}\label{her-words-sent-a-strange-chill-through-philip.}}

Her words sent a strange chill through Philip.

\hypertarget{he-had-no-excuse-for-the-feelings-which-were-aroused-in-him.}{%
\subsection{He had no excuse for the feelings which were aroused in
him.}\label{he-had-no-excuse-for-the-feelings-which-were-aroused-in-him.}}

He had no excuse for the feelings which were aroused in him.

\hypertarget{was-it-the-rendezvous-of-those-who-were-striving-to-work-his-ruin.}{%
\subsection{Was it the rendezvous of those who were striving to work his
ruin.}\label{was-it-the-rendezvous-of-those-who-were-striving-to-work-his-ruin.}}

Was it the rendezvous of those who were striving to work his ruin.

\hypertarget{she-added-with-genuine-sympathy-in-her-face-and-voice.}{%
\subsection{She added, with genuine sympathy in her face and
voice.}\label{she-added-with-genuine-sympathy-in-her-face-and-voice.}}

She added, with genuine sympathy in her face and voice.

\hypertarget{pierre-obeys-me-when-we-are-together.}{%
\subsection{Pierre obeys me when we are
together.}\label{pierre-obeys-me-when-we-are-together.}}

Pierre obeys me when we are together.

\hypertarget{jeanne-was-turning-the-bow-shoreward.}{%
\subsection{Jeanne was turning the bow
shoreward.}\label{jeanne-was-turning-the-bow-shoreward.}}

Jeanne was turning the bow shoreward.

\hypertarget{my-right-foot-feels-like-that-of-a-chinese-debutante.}{%
\subsection{My right foot feels like that of a Chinese
debutante.}\label{my-right-foot-feels-like-that-of-a-chinese-debutante.}}

My right foot feels like that of a Chinese debutante.

\hypertarget{they-ate-dinner-at-the-fifth-and-rested-for-two-hours.}{%
\subsection{They ate dinner at the fifth, and rested for two
hours.}\label{they-ate-dinner-at-the-fifth-and-rested-for-two-hours.}}

They ate dinner at the fifth, and rested for two hours.

\hypertarget{two-years-ago-i-gave-up-civilization-for-this.}{%
\subsection{Two years ago I gave up civilization for
this.}\label{two-years-ago-i-gave-up-civilization-for-this.}}

Two years ago I gave up civilization for this.

\hypertarget{she-had-died-from-cold-and-starvation.}{%
\subsection{She had died from cold and
starvation.}\label{she-had-died-from-cold-and-starvation.}}

She had died from cold and starvation.

\hypertarget{it-was-jeanne-singing-softly-over-beyond-the-rocks.}{%
\subsection{It was Jeanne singing softly over beyond the
rocks.}\label{it-was-jeanne-singing-softly-over-beyond-the-rocks.}}

It was Jeanne singing softly over beyond the rocks.

\hypertarget{he-was-determined-now-to-maintain-a-more-certain-hold-upon-himself.}{%
\subsection{He was determined now to maintain a more certain hold upon
himself.}\label{he-was-determined-now-to-maintain-a-more-certain-hold-upon-himself.}}

He was determined now to maintain a more certain hold upon himself.

\hypertarget{each-day-she-became-a-more-vital-part-of-him.}{%
\subsection{Each day she became a more vital part of
him.}\label{each-day-she-became-a-more-vital-part-of-him.}}

Each day she became a more vital part of him.

\hypertarget{it-was-a-temptation-but-he-resisted-it.}{%
\subsection{It was a temptation, but he resisted
it.}\label{it-was-a-temptation-but-he-resisted-it.}}

It was a temptation, but he resisted it.

\hypertarget{this-one-hope-was-destroyed-as-quickly-as-it-was-born.}{%
\subsection{This one hope was destroyed as quickly as it was
born.}\label{this-one-hope-was-destroyed-as-quickly-as-it-was-born.}}

This one hope was destroyed as quickly as it was born.

\hypertarget{her-face-was-against-his-breast.}{%
\subsection{Her face was against his
breast.}\label{her-face-was-against-his-breast.}}

Her face was against his breast.

\hypertarget{she-was-his-now-forever.}{%
\subsection{She was his now, forever.}\label{she-was-his-now-forever.}}

She was his now, forever.

\hypertarget{providence-had-delivered-him-through-the-maelstrom.}{%
\subsection{Providence had delivered him through the
maelstrom.}\label{providence-had-delivered-him-through-the-maelstrom.}}

Providence had delivered him through the maelstrom.

\hypertarget{a-cry-of-joy-burst-from-philips-lips.}{%
\subsection{A cry of joy burst from Philip's
lips.}\label{a-cry-of-joy-burst-from-philips-lips.}}

A cry of joy burst from Philip's lips.

\hypertarget{philip-began-to-feel-that-he-had-foolishly-overestimated-his-strength.}{%
\subsection{Philip began to feel that he had foolishly overestimated his
strength.}\label{philip-began-to-feel-that-he-had-foolishly-overestimated-his-strength.}}

Philip began to feel that he had foolishly overestimated his strength.

\hypertarget{he-obeyed-the-pressure-of-her-hand.}{%
\subsection{He obeyed the pressure of her
hand.}\label{he-obeyed-the-pressure-of-her-hand.}}

He obeyed the pressure of her hand.

\hypertarget{i-am-going-to-surprise-father-and-you-will-go-with-pierre.}{%
\subsection{I am going to surprise father, and you will go with
Pierre.}\label{i-am-going-to-surprise-father-and-you-will-go-with-pierre.}}

I am going to surprise father, and you will go with Pierre.

\hypertarget{about-him-everywhere-were-the-evidences-of-luxury-and-of-age.}{%
\subsection{About him, everywhere, were the evidences of luxury and of
age.}\label{about-him-everywhere-were-the-evidences-of-luxury-and-of-age.}}

About him, everywhere, were the evidences of luxury and of age.

\hypertarget{then-he-stepped-back-with-a-low-cry-of-pleasure.}{%
\subsection{Then he stepped back with a low cry of
pleasure.}\label{then-he-stepped-back-with-a-low-cry-of-pleasure.}}

Then he stepped back with a low cry of pleasure.

\hypertarget{in-the-picture-he-saw-each-moment-a-greater-resemblance-to-jeanne.}{%
\subsection{In the picture he saw each moment a greater resemblance to
Jeanne.}\label{in-the-picture-he-saw-each-moment-a-greater-resemblance-to-jeanne.}}

In the picture he saw each moment a greater resemblance to Jeanne.

\hypertarget{he-told-himself-that-as-he-washed-himself-and-groomed-his-disheveled-clothes.}{%
\subsection{He told himself that as he washed himself and groomed his
disheveled
clothes.}\label{he-told-himself-that-as-he-washed-himself-and-groomed-his-disheveled-clothes.}}

He told himself that as he washed himself and groomed his disheveled
clothes.

\hypertarget{accept-a-fathers-blessing-and-with-it-this.}{%
\subsection{Accept a father's blessing, and with it,
this.}\label{accept-a-fathers-blessing-and-with-it-this.}}

Accept a father's blessing, and with it, this.

\hypertarget{it-seems-like-a-strange-pointing-of-the-hand-of-god.}{%
\subsection{It seems like a strange pointing of the hand of
God.}\label{it-seems-like-a-strange-pointing-of-the-hand-of-god.}}

It seems like a strange pointing of the hand of God.

\hypertarget{such-things-had-occurred-before-he-told-philip.}{%
\subsection{Such things had occurred before, he told
Philip.}\label{such-things-had-occurred-before-he-told-philip.}}

Such things had occurred before, he told Philip.

\hypertarget{ah-i-had-forgotten-he-exclaimed.}{%
\subsection{Ah, I had forgotten, he
exclaimed.}\label{ah-i-had-forgotten-he-exclaimed.}}

Ah, I had forgotten, he exclaimed.

\hypertarget{but-there-was-something-even-more-startling-than-this-resemblance.}{%
\subsection{But there was something even more startling than this
resemblance.}\label{but-there-was-something-even-more-startling-than-this-resemblance.}}

But there was something even more startling than this resemblance.

\hypertarget{i-have-to-be-careful-of-them-as-they-tear-very-easily.}{%
\subsection{I have to be careful of them, as they tear very
easily.}\label{i-have-to-be-careful-of-them-as-they-tear-very-easily.}}

I have to be careful of them, as they tear very easily.

\hypertarget{of-course-that-is-uninteresting-she-continued.}{%
\subsection{Of course, that is uninteresting, she
continued.}\label{of-course-that-is-uninteresting-she-continued.}}

Of course, that is uninteresting, she continued.

\hypertarget{a-moment-before-he-was-intoxicated-by-a-joy-that-was-almost-madness.}{%
\subsection{A moment before he was intoxicated by a joy that was almost
madness.}\label{a-moment-before-he-was-intoxicated-by-a-joy-that-was-almost-madness.}}

A moment before he was intoxicated by a joy that was almost madness.

\hypertarget{now-these-things-had-been-struck-dead-within-him.}{%
\subsection{Now these things had been struck dead within
him.}\label{now-these-things-had-been-struck-dead-within-him.}}

Now these things had been struck dead within him.

\hypertarget{for-an-instant-he-saw-pierre-drawn-like-a-silhouette-against-the-sky.}{%
\subsection{For an instant he saw Pierre drawn like a silhouette against
the
sky.}\label{for-an-instant-he-saw-pierre-drawn-like-a-silhouette-against-the-sky.}}

For an instant he saw Pierre drawn like a silhouette against the sky.

\hypertarget{goodbye-pierre-he-shouted.}{%
\subsection{Goodbye, Pierre, he
shouted.}\label{goodbye-pierre-he-shouted.}}

Goodbye, Pierre, he shouted.

\hypertarget{and-macdougall-was-beyond-the-trail-with-three-weeks-to-spare.}{%
\subsection{And MacDougall was beyond the trail, with three weeks to
spare.}\label{and-macdougall-was-beyond-the-trail-with-three-weeks-to-spare.}}

And MacDougall was beyond the trail, with three weeks to spare.

\hypertarget{philip-thrust-himself-against-it-and-entered.}{%
\subsection{Philip thrust himself against it and
entered.}\label{philip-thrust-himself-against-it-and-entered.}}

Philip thrust himself against it and entered.

\hypertarget{macdougall-tapped-his-forehead-suspiciously-with-a-stubby-forefinger.}{%
\subsection{MacDougall tapped his forehead suspiciously with a stubby
forefinger.}\label{macdougall-tapped-his-forehead-suspiciously-with-a-stubby-forefinger.}}

MacDougall tapped his forehead suspiciously with a stubby forefinger.

\hypertarget{he-was-smooth-shaven-and-his-hair-and-eyes-were-black.}{%
\subsection{He was smooth-shaven, and his hair and eyes were
black.}\label{he-was-smooth-shaven-and-his-hair-and-eyes-were-black.}}

He was smooth-shaven, and his hair and eyes were black.

\hypertarget{wont-you-draw-up-gentlemen.}{%
\subsection{Won't you draw up,
gentlemen.}\label{wont-you-draw-up-gentlemen.}}

Won't you draw up, gentlemen.

\hypertarget{a-strange-fire-burned-in-his-eyes-when-thorpe-turned.}{%
\subsection{A strange fire burned in his eyes when Thorpe
turned.}\label{a-strange-fire-burned-in-his-eyes-when-thorpe-turned.}}

A strange fire burned in his eyes when Thorpe turned.

\hypertarget{he-had-worshiped-her-as-dante-might-have-worshiped-beatrice.}{%
\subsection{He had worshiped her, as Dante might have worshiped
Beatrice.}\label{he-had-worshiped-her-as-dante-might-have-worshiped-beatrice.}}

He had worshiped her, as Dante might have worshiped Beatrice.

\hypertarget{does-that-look-good.}{%
\subsection{Does that look good.}\label{does-that-look-good.}}

Does that look good.

\hypertarget{they-look-as-though-he-had-been-drumming-a-piano-all-his-life.}{%
\subsection{They look as though he had been drumming a piano all his
life.}\label{they-look-as-though-he-had-been-drumming-a-piano-all-his-life.}}

They look as though he had been drumming a piano all his life.

\hypertarget{you-want-to-go-over-and-see-his-gang-throw-dirt.}{%
\subsection{You want to go over and see his gang throw
dirt.}\label{you-want-to-go-over-and-see-his-gang-throw-dirt.}}

You want to go over and see his gang throw dirt.

\hypertarget{take-away-their-foreman-and-they-wouldnt-be-worth-their-grub.}{%
\subsection{Take away their foreman and they wouldn't be worth their
grub.}\label{take-away-their-foreman-and-they-wouldnt-be-worth-their-grub.}}

Take away their foreman and they wouldn't be worth their grub.

\hypertarget{thats-the-sub-foreman-explained-thorpe.}{%
\subsection{That's the sub-foreman, explained
Thorpe.}\label{thats-the-sub-foreman-explained-thorpe.}}

That's the sub-foreman, explained Thorpe.

\hypertarget{philip-made-no-effort-to-follow.}{%
\subsection{Philip made no effort to
follow.}\label{philip-made-no-effort-to-follow.}}

Philip made no effort to follow.

\hypertarget{he-came-first-a-year-ago-and-revealed-himself-to-jeanne.}{%
\subsection{He came first a year ago, and revealed himself to
Jeanne.}\label{he-came-first-a-year-ago-and-revealed-himself-to-jeanne.}}

He came first a year ago, and revealed himself to Jeanne.

\hypertarget{they-are-to-attack-your-camp-tomorrow-night.}{%
\subsection{They are to attack your camp tomorrow
night.}\label{they-are-to-attack-your-camp-tomorrow-night.}}

They are to attack your camp tomorrow night.

\hypertarget{two-days-ago-jeanne-learned-where-her-fathers-men-were-hiding.}{%
\subsection{Two days ago Jeanne learned where her father's men were
hiding.}\label{two-days-ago-jeanne-learned-where-her-fathers-men-were-hiding.}}

Two days ago Jeanne learned where her father's men were hiding.

\hypertarget{i-was-near-the-cabin-and-saw-you.}{%
\subsection{I was near the cabin, and saw
you.}\label{i-was-near-the-cabin-and-saw-you.}}

I was near the cabin, and saw you.

\hypertarget{low-bush-whipped-him-in-the-face-and-left-no-sting.}{%
\subsection{Low bush whipped him in the face and left no
sting.}\label{low-bush-whipped-him-in-the-face-and-left-no-sting.}}

Low bush whipped him in the face and left no sting.

\hypertarget{suddenly-jeanne-stopped-for-an-instant.}{%
\subsection{Suddenly Jeanne stopped for an
instant.}\label{suddenly-jeanne-stopped-for-an-instant.}}

Suddenly Jeanne stopped for an instant.

\hypertarget{there-was-none-of-the-joy-of-meeting-in-his-face.}{%
\subsection{There was none of the joy of meeting in his
face.}\label{there-was-none-of-the-joy-of-meeting-in-his-face.}}

There was none of the joy of meeting in his face.

\hypertarget{and-when-you-come-back-in-a-few-days-bring-eileen.}{%
\subsection{And when you come back in a few days, bring
Eileen.}\label{and-when-you-come-back-in-a-few-days-bring-eileen.}}

And when you come back in a few days, bring Eileen.

\hypertarget{gregson-had-left-the-outer-door-slightly-ajar.}{%
\subsection{Gregson had left the outer door slightly
ajar.}\label{gregson-had-left-the-outer-door-slightly-ajar.}}

Gregson had left the outer door slightly ajar.

\hypertarget{the-date-was-nearly-eighteen-years-old.}{%
\subsection{The date was nearly eighteen years
old.}\label{the-date-was-nearly-eighteen-years-old.}}

The date was nearly eighteen years old.

\hypertarget{they-were-the-presage-of-storm.}{%
\subsection{They were the presage of
storm.}\label{they-were-the-presage-of-storm.}}

They were the presage of storm.

\hypertarget{down-there-the-earth-was-already-swelling-with-life.}{%
\subsection{Down there the earth was already swelling with
life.}\label{down-there-the-earth-was-already-swelling-with-life.}}

Down there the earth was already swelling with life.

\hypertarget{for-the-first-time-in-his-life-he-was-yearning-for-a-scrap.}{%
\subsection{For the first time in his life he was yearning for a
scrap.}\label{for-the-first-time-in-his-life-he-was-yearning-for-a-scrap.}}

For the first time in his life he was yearning for a scrap.

\hypertarget{she-had-been-thoroughly-and-efficiently-mauled.}{%
\subsection{She had been thoroughly and efficiently
mauled.}\label{she-had-been-thoroughly-and-efficiently-mauled.}}

She had been thoroughly and efficiently mauled.

\hypertarget{every-bone-in-her-aged-body-seemed-broken-or-dislocated.}{%
\subsection{Every bone in her aged body seemed broken or
dislocated.}\label{every-bone-in-her-aged-body-seemed-broken-or-dislocated.}}

Every bone in her aged body seemed broken or dislocated.

\hypertarget{tomorrow-im-going-after-that-bear-he-said.}{%
\subsection{Tomorrow I'm going after that bear, he
said.}\label{tomorrow-im-going-after-that-bear-he-said.}}

Tomorrow I'm going after that bear, he said.

\hypertarget{if-not-lets-say-our-prayers-and-go-to-bed.}{%
\subsection{If not, let's say our prayers and go to
bed.}\label{if-not-lets-say-our-prayers-and-go-to-bed.}}

If not, let's say our prayers and go to bed.

\hypertarget{so-cheer-up-and-give-us-your-paw.}{%
\subsection{So cheer up, and give us your
paw.}\label{so-cheer-up-and-give-us-your-paw.}}

So cheer up, and give us your paw.

\hypertarget{this-time-he-did-not-yap-for-mercy.}{%
\subsection{This time he did not yap for
mercy.}\label{this-time-he-did-not-yap-for-mercy.}}

This time he did not yap for mercy.

\hypertarget{and-the-air-was-growing-chilly.}{%
\subsection{And the air was growing
chilly.}\label{and-the-air-was-growing-chilly.}}

And the air was growing chilly.

\hypertarget{dont-you-see-im-chewing-this-thing-in-two.}{%
\subsection{Don't you see, I'm chewing this thing in
two.}\label{dont-you-see-im-chewing-this-thing-in-two.}}

Don't you see, I'm chewing this thing in two.

\hypertarget{the-questions-may-have-come-vaguely-in-his-mind.}{%
\subsection{The questions may have come vaguely in his
mind.}\label{the-questions-may-have-come-vaguely-in-his-mind.}}

The questions may have come vaguely in his mind.

\hypertarget{like-a-flash-he-launched-himself-into-the-feathered-mass-of-the-owl.}{%
\subsection{Like a flash he launched himself into the feathered mass of
the
owl.}\label{like-a-flash-he-launched-himself-into-the-feathered-mass-of-the-owl.}}

Like a flash he launched himself into the feathered mass of the owl.

\hypertarget{ahead-of-them-they-saw-a-glimmer-of-sunshine.}{%
\subsection{Ahead of them they saw a glimmer of
sunshine.}\label{ahead-of-them-they-saw-a-glimmer-of-sunshine.}}

Ahead of them they saw a glimmer of sunshine.

\hypertarget{two-gigantic-owls-were-tearing-at-the-carcass.}{%
\subsection{Two gigantic owls were tearing at the
carcass.}\label{two-gigantic-owls-were-tearing-at-the-carcass.}}

Two gigantic owls were tearing at the carcass.

\hypertarget{the-big-eyed-clucking-moose-birds-were-most-annoying.}{%
\subsection{The big-eyed, clucking moose-birds were most
annoying.}\label{the-big-eyed-clucking-moose-birds-were-most-annoying.}}

The big-eyed, clucking moose-birds were most annoying.

\hypertarget{next-to-them-the-canada-jays-were-most-persistent.}{%
\subsection{Next to them the Canada jays were most
persistent.}\label{next-to-them-the-canada-jays-were-most-persistent.}}

Next to them the Canada jays were most persistent.

\hypertarget{for-a-time-the-exciting-thrill-of-his-adventure-was-gone.}{%
\subsection{For a time the exciting thrill of his adventure was
gone.}\label{for-a-time-the-exciting-thrill-of-his-adventure-was-gone.}}

For a time the exciting thrill of his adventure was gone.

\hypertarget{he-did-not-rush-in.}{%
\subsection{He did not rush in.}\label{he-did-not-rush-in.}}

He did not rush in.

\hypertarget{it-was-edged-with-ice.}{%
\subsection{It was edged with ice.}\label{it-was-edged-with-ice.}}

It was edged with ice.

\hypertarget{he-drank-of-the-water-cautiously.}{%
\subsection{He drank of the water
cautiously.}\label{he-drank-of-the-water-cautiously.}}

He drank of the water cautiously.

\hypertarget{but-a-strange-thing-happened.}{%
\subsection{But a strange thing
happened.}\label{but-a-strange-thing-happened.}}

But a strange thing happened.

\hypertarget{he-began-to-follow-the-footprints-of-the-dog.}{%
\subsection{He began to follow the footprints of the
dog.}\label{he-began-to-follow-the-footprints-of-the-dog.}}

He began to follow the footprints of the dog.

\hypertarget{such-a-dog-the-wise-driver-kills-or-turns-loose.}{%
\subsection{Such a dog the wise driver kills, or turns
loose.}\label{such-a-dog-the-wise-driver-kills-or-turns-loose.}}

Such a dog the wise driver kills, or turns loose.

\hypertarget{sometimes-her-dreams-were-filled-with-visions.}{%
\subsection{Sometimes her dreams were filled with
visions.}\label{sometimes-her-dreams-were-filled-with-visions.}}

Sometimes her dreams were filled with visions.

\hypertarget{thus-had-the-raw-wilderness-prepared-him-for-this-day.}{%
\subsection{Thus had the raw wilderness prepared him for this
day.}\label{thus-had-the-raw-wilderness-prepared-him-for-this-day.}}

Thus had the raw wilderness prepared him for this day.

\hypertarget{he-leapt-again-and-the-club-caught-him-once-more.}{%
\subsection{He leapt again, and the club caught him once
more.}\label{he-leapt-again-and-the-club-caught-him-once-more.}}

He leapt again, and the club caught him once more.

\hypertarget{he-cried-and-swung-the-club-wildly.}{%
\subsection{He cried, and swung the club
wildly.}\label{he-cried-and-swung-the-club-wildly.}}

He cried, and swung the club wildly.

\hypertarget{she-turned-fearing-that-jacques-might-see-what-was-in-her-face.}{%
\subsection{She turned, fearing that Jacques might see what was in her
face.}\label{she-turned-fearing-that-jacques-might-see-what-was-in-her-face.}}

She turned, fearing that Jacques might see what was in her face.

\hypertarget{they-were-following-the-shore-of-a-lake.}{%
\subsection{They were following the shore of a
lake.}\label{they-were-following-the-shore-of-a-lake.}}

They were following the shore of a lake.

\hypertarget{the-wolf-dog-thrust-his-gaunt-muzzle-toward-him.}{%
\subsection{The wolf-dog thrust his gaunt muzzle toward
him.}\label{the-wolf-dog-thrust-his-gaunt-muzzle-toward-him.}}

The wolf-dog thrust his gaunt muzzle toward him.

\hypertarget{from-now-on-were-pals.}{%
\subsection{From now on we're pals.}\label{from-now-on-were-pals.}}

From now on we're pals.

\hypertarget{he-says-he-bought-him-of-jacques-le-beau.}{%
\subsection{He says he bought him of Jacques Le
Beau.}\label{he-says-he-bought-him-of-jacques-le-beau.}}

He says he bought him of Jacques Le Beau.

\hypertarget{how-much-was-it.}{%
\subsection{How much was it.}\label{how-much-was-it.}}

How much was it.

\hypertarget{youth-had-come-back-to-her-freed-from-the-yoke-of-oppression.}{%
\subsection{Youth had come back to her, freed from the yoke of
oppression.}\label{youth-had-come-back-to-her-freed-from-the-yoke-of-oppression.}}

Youth had come back to her, freed from the yoke of oppression.

\hypertarget{it-was-not-a-large-lake-and-almost-round.}{%
\subsection{It was not a large lake, and almost
round.}\label{it-was-not-a-large-lake-and-almost-round.}}

It was not a large lake, and almost round.

\hypertarget{its-diameter-was-not-more-than-two-hundred-yards.}{%
\subsection{Its diameter was not more than two hundred
yards.}\label{its-diameter-was-not-more-than-two-hundred-yards.}}

Its diameter was not more than two hundred yards.

\hypertarget{it-drowned-all-sound-that-brute-agony-and-death-may-have-made.}{%
\subsection{It drowned all sound that brute agony and death may have
made.}\label{it-drowned-all-sound-that-brute-agony-and-death-may-have-made.}}

It drowned all sound that brute agony and death may have made.

\hypertarget{fresh-cases-still-able-to-walk-they-clustered-about-the-spokesman.}{%
\subsection{Fresh cases, still able to walk, they clustered about the
spokesman.}\label{fresh-cases-still-able-to-walk-they-clustered-about-the-spokesman.}}

Fresh cases, still able to walk, they clustered about the spokesman.

\hypertarget{between-him-and-the-beach-was-the-cane-grass-fence-of-the-compound.}{%
\subsection{Between him and the beach was the cane-grass fence of the
compound.}\label{between-him-and-the-beach-was-the-cane-grass-fence-of-the-compound.}}

Between him and the beach was the cane-grass fence of the compound.

\hypertarget{besides-he-was-paid-one-case-of-tobacco-per-head.}{%
\subsection{Besides, he was paid one case of tobacco per
head.}\label{besides-he-was-paid-one-case-of-tobacco-per-head.}}

Besides, he was paid one case of tobacco per head.

\hypertarget{they-die-out-of-spite.}{%
\subsection{They die out of spite.}\label{they-die-out-of-spite.}}

They die out of spite.

\hypertarget{the-other-felt-a-sudden-wave-of-irritation-rush-through-him.}{%
\subsection{The other felt a sudden wave of irritation rush through
him.}\label{the-other-felt-a-sudden-wave-of-irritation-rush-through-him.}}

The other felt a sudden wave of irritation rush through him.

\hypertarget{oppressive-as-the-heat-had-been-it-was-now-even-more-oppressive.}{%
\subsection{Oppressive as the heat had been, it was now even more
oppressive.}\label{oppressive-as-the-heat-had-been-it-was-now-even-more-oppressive.}}

Oppressive as the heat had been, it was now even more oppressive.

\hypertarget{the-ringing-of-the-big-bell-aroused-him.}{%
\subsection{The ringing of the big bell aroused
him.}\label{the-ringing-of-the-big-bell-aroused-him.}}

The ringing of the big bell aroused him.

\hypertarget{at-first-he-puzzled-over-something-untoward-he-was-sure-had-happened.}{%
\subsection{At first he puzzled over something untoward he was sure had
happened.}\label{at-first-he-puzzled-over-something-untoward-he-was-sure-had-happened.}}

At first he puzzled over something untoward he was sure had happened.

\hypertarget{a-dead-man-is-of-no-use-on-a-plantation.}{%
\subsection{A dead man is of no use on a
plantation.}\label{a-dead-man-is-of-no-use-on-a-plantation.}}

A dead man is of no use on a plantation.

\hypertarget{i-dont-know-why-youre-here-at-all.}{%
\subsection{I don't know why you're here at
all.}\label{i-dont-know-why-youre-here-at-all.}}

I don't know why you're here at all.

\hypertarget{what-part-of-the-united-states-is-your-home.}{%
\subsection{What part of the United States is your
home.}\label{what-part-of-the-united-states-is-your-home.}}

What part of the United States is your home.

\hypertarget{my-im-almost-homesick-for-it-already.}{%
\subsection{My, I'm almost homesick for it
already.}\label{my-im-almost-homesick-for-it-already.}}

My, I'm almost homesick for it already.

\hypertarget{she-nodded-and-her-eyes-grew-soft-and-moist.}{%
\subsection{She nodded, and her eyes grew soft and
moist.}\label{she-nodded-and-her-eyes-grew-soft-and-moist.}}

She nodded, and her eyes grew soft and moist.

\hypertarget{i-was-brought-up-the-way-most-girls-in-hawaii-are-brought-up.}{%
\subsection{I was brought up the way most girls in Hawaii are brought
up.}\label{i-was-brought-up-the-way-most-girls-in-hawaii-are-brought-up.}}

I was brought up the way most girls in Hawaii are brought up.

\hypertarget{that-came-before-my-a-b-cs.}{%
\subsection{That came before my A B
C's.}\label{that-came-before-my-a-b-cs.}}

That came before my A B C's.

\hypertarget{it-was-the-same-way-with-our-revolvers-and-rifles.}{%
\subsection{It was the same way with our revolvers and
rifles.}\label{it-was-the-same-way-with-our-revolvers-and-rifles.}}

It was the same way with our revolvers and rifles.

\hypertarget{but-it-contributed-to-the-smash.}{%
\subsection{But it contributed to the
smash.}\label{but-it-contributed-to-the-smash.}}

But it contributed to the smash.

\hypertarget{the-last-one-i-knew-was-an-overseer.}{%
\subsection{The last one I knew was an
overseer.}\label{the-last-one-i-knew-was-an-overseer.}}

The last one I knew was an overseer.

\hypertarget{do-you-know-any-good-land-around-here.}{%
\subsection{Do you know any good land around
here.}\label{do-you-know-any-good-land-around-here.}}

Do you know any good land around here.

\hypertarget{the-resident-commissioner-is-away-in-australia.}{%
\subsection{The Resident Commissioner is away in
Australia.}\label{the-resident-commissioner-is-away-in-australia.}}

The Resident Commissioner is away in Australia.

\hypertarget{i-cannot-follow-you-she-said.}{%
\subsection{I cannot follow you, she
said.}\label{i-cannot-follow-you-she-said.}}

I cannot follow you, she said.

\hypertarget{i-never-allow-what-cant-be-changed-to-annoy-me.}{%
\subsection{I never allow what can't be changed to annoy
me.}\label{i-never-allow-what-cant-be-changed-to-annoy-me.}}

I never allow what can't be changed to annoy me.

\hypertarget{why-the-average-review-is-more-nauseating-than-cod-liver-oil.}{%
\subsection{Why, the average review is more nauseating than cod liver
oil.}\label{why-the-average-review-is-more-nauseating-than-cod-liver-oil.}}

Why, the average review is more nauseating than cod liver oil.

\hypertarget{his-voice-was-passionately-rebellious.}{%
\subsection{His voice was passionately
rebellious.}\label{his-voice-was-passionately-rebellious.}}

His voice was passionately rebellious.

\hypertarget{dont-you-see-i-hate-you.}{%
\subsection{Don't you see I hate you.}\label{dont-you-see-i-hate-you.}}

Don't you see I hate you.

\hypertarget{so-hughie-and-i-did-the-managing-ourselves.}{%
\subsection{So Hughie and I did the managing
ourselves.}\label{so-hughie-and-i-did-the-managing-ourselves.}}

So Hughie and I did the managing ourselves.

\hypertarget{it-happened-to-him-at-the-gallina-society-in-oakland-one-afternoon.}{%
\subsection{It happened to him at the Gallina Society in Oakland one
afternoon.}\label{it-happened-to-him-at-the-gallina-society-in-oakland-one-afternoon.}}

It happened to him at the Gallina Society in Oakland one afternoon.

\hypertarget{he-cried-in-such-genuine-dismay-that-she-broke-into-hearty-laughter.}{%
\subsection{He cried in such genuine dismay that she broke into hearty
laughter.}\label{he-cried-in-such-genuine-dismay-that-she-broke-into-hearty-laughter.}}

He cried in such genuine dismay that she broke into hearty laughter.

\hypertarget{wash-your-hands-of-me.}{%
\subsection{Wash your hands of me.}\label{wash-your-hands-of-me.}}

Wash your hands of me.

\hypertarget{i-think-its-much-nicer-to-quarrel.}{%
\subsection{I think it's much nicer to
quarrel.}\label{i-think-its-much-nicer-to-quarrel.}}

I think it's much nicer to quarrel.

\hypertarget{i-saw-it-when-she-rolled.}{%
\subsection{I saw it when she rolled.}\label{i-saw-it-when-she-rolled.}}

I saw it when she rolled.

\hypertarget{i-only-read-the-quotations.}{%
\subsection{I only read the
quotations.}\label{i-only-read-the-quotations.}}

I only read the quotations.

\hypertarget{he-was-the-soul-of-devotion-to-his-employers.}{%
\subsection{He was the soul of devotion to his
employers.}\label{he-was-the-soul-of-devotion-to-his-employers.}}

He was the soul of devotion to his employers.

\hypertarget{out-of-his-eighteen-hundred-he-laid-aside-sixteen-hundred-each-year.}{%
\subsection{Out of his eighteen hundred, he laid aside sixteen hundred
each
year.}\label{out-of-his-eighteen-hundred-he-laid-aside-sixteen-hundred-each-year.}}

Out of his eighteen hundred, he laid aside sixteen hundred each year.

\hypertarget{you-have-heard-always-how-he-was-the-lover-of-the-princess-naomi.}{%
\subsection{You have heard always how he was the lover of the Princess
Naomi.}\label{you-have-heard-always-how-he-was-the-lover-of-the-princess-naomi.}}

You have heard always how he was the lover of the Princess Naomi.

\hypertarget{they-ought-to-pass-here-some-time-today.}{%
\subsection{They ought to pass here some time
today.}\label{they-ought-to-pass-here-some-time-today.}}

They ought to pass here some time today.

\hypertarget{i-had-been-sad-too-long-already.}{%
\subsection{I had been sad too long
already.}\label{i-had-been-sad-too-long-already.}}

I had been sad too long already.

\hypertarget{all-eyes-however-were-staring-at-him-in-certitude-of-expectancy.}{%
\subsection{All eyes, however, were staring at him in certitude of
expectancy.}\label{all-eyes-however-were-staring-at-him-in-certitude-of-expectancy.}}

All eyes, however, were staring at him in certitude of expectancy.

\hypertarget{he-had-observed-the-business-life-of-hawaii-and-developed-a-vaulting-ambition.}{%
\subsection{He had observed the business life of Hawaii and developed a
vaulting
ambition.}\label{he-had-observed-the-business-life-of-hawaii-and-developed-a-vaulting-ambition.}}

He had observed the business life of Hawaii and developed a vaulting
ambition.

\hypertarget{i-may-manage-to-freight-a-cargo-back-as-well.}{%
\subsection{I may manage to freight a cargo back as
well.}\label{i-may-manage-to-freight-a-cargo-back-as-well.}}

I may manage to freight a cargo back as well.

\hypertarget{obrien-had-been-a-clean-living-young-man-with-ideals.}{%
\subsection{O'Brien had been a clean living young man with
ideals.}\label{obrien-had-been-a-clean-living-young-man-with-ideals.}}

O'Brien had been a clean living young man with ideals.

\hypertarget{he-it-was-that-lived-to-found-the-family-of-the-patino.}{%
\subsection{He it was that lived to found the family of the
Patino.}\label{he-it-was-that-lived-to-found-the-family-of-the-patino.}}

He it was that lived to found the family of the Patino.

\hypertarget{straight-out-they-swam-their-heads-growing-smaller-and-smaller.}{%
\subsection{Straight out they swam, their heads growing smaller and
smaller.}\label{straight-out-they-swam-their-heads-growing-smaller-and-smaller.}}

Straight out they swam, their heads growing smaller and smaller.

\hypertarget{you-wont-die-of-malnutrition-be-sure-of-that.}{%
\subsection{You won't die of malnutrition, be sure of
that.}\label{you-wont-die-of-malnutrition-be-sure-of-that.}}

You won't die of malnutrition, be sure of that.

\hypertarget{see-the-length-of-the-body-and-that-elongated-neck.}{%
\subsection{See the length of the body and that elongated
neck.}\label{see-the-length-of-the-body-and-that-elongated-neck.}}

See the length of the body and that elongated neck.

\hypertarget{they-are-coming-ashore-whoever-they-are.}{%
\subsection{They are coming ashore, whoever they
are.}\label{they-are-coming-ashore-whoever-they-are.}}

They are coming ashore, whoever they are.

\hypertarget{soaked-in-seawater-they-offset-the-heat-rays.}{%
\subsection{Soaked in seawater they offset the heat
rays.}\label{soaked-in-seawater-they-offset-the-heat-rays.}}

Soaked in seawater they offset the heat rays.

\hypertarget{think-of-investing-in-such-an-adventure.}{%
\subsection{Think of investing in such an
adventure.}\label{think-of-investing-in-such-an-adventure.}}

Think of investing in such an adventure.

\hypertarget{nobody-knew-his-history-they-of-the-junta-least-of-all.}{%
\subsection{Nobody knew his history, they of the Junta least of
all.}\label{nobody-knew-his-history-they-of-the-junta-least-of-all.}}

Nobody knew his history, they of the Junta least of all.

\hypertarget{i-have-been-doubly-baptized.}{%
\subsection{I have been doubly
baptized.}\label{i-have-been-doubly-baptized.}}

I have been doubly baptized.

\hypertarget{they-wouldnt-be-sweeping-a-big-vessel-like-the-martha.}{%
\subsection{They wouldn't be sweeping a big vessel like the
Martha.}\label{they-wouldnt-be-sweeping-a-big-vessel-like-the-martha.}}

They wouldn't be sweeping a big vessel like the Martha.

\hypertarget{joan-looked-triumphantly-at-sheldon-who-bowed.}{%
\subsection{Joan looked triumphantly at Sheldon, who
bowed.}\label{joan-looked-triumphantly-at-sheldon-who-bowed.}}

Joan looked triumphantly at Sheldon, who bowed.

\hypertarget{and-i-hope-youve-got-plenty-of-chain-out-captain-young.}{%
\subsection{And I hope you've got plenty of chain out, Captain
Young.}\label{and-i-hope-youve-got-plenty-of-chain-out-captain-young.}}

And I hope you've got plenty of chain out, Captain Young.

\hypertarget{the-discovery-seemed-to-have-been-made-on-the-spur-of-the-moment.}{%
\subsection{The discovery seemed to have been made on the spur of the
moment.}\label{the-discovery-seemed-to-have-been-made-on-the-spur-of-the-moment.}}

The discovery seemed to have been made on the spur of the moment.

\hypertarget{they-handled-two-men-already-both-grub-thieves.}{%
\subsection{They handled two men already, both
grub-thieves.}\label{they-handled-two-men-already-both-grub-thieves.}}

They handled two men already, both grub-thieves.

\hypertarget{eli-harding-asked-as-shunk-started-to-follow.}{%
\subsection{Eli Harding asked, as Shunk started to
follow.}\label{eli-harding-asked-as-shunk-started-to-follow.}}

Eli Harding asked, as Shunk started to follow.

\hypertarget{now-go-ahead-and-tell-me-in-a-straightforward-way-what-has-happened.}{%
\subsection{Now go ahead and tell me in a straightforward way what has
happened.}\label{now-go-ahead-and-tell-me-in-a-straightforward-way-what-has-happened.}}

Now go ahead and tell me in a straightforward way what has happened.

\hypertarget{thats-where-they-cut-off-the-scottish-chiefs-and-killed-all-hands.}{%
\subsection{That's where they cut off the Scottish Chiefs and killed all
hands.}\label{thats-where-they-cut-off-the-scottish-chiefs-and-killed-all-hands.}}

That's where they cut off the Scottish Chiefs and killed all hands.

\hypertarget{and-after-the-bath-a-shave-would-not-be-bad.}{%
\subsection{And after the bath a shave would not be
bad.}\label{and-after-the-bath-a-shave-would-not-be-bad.}}

And after the bath a shave would not be bad.

\hypertarget{now-please-give-a-plain-statement-of-what-occurred.}{%
\subsection{Now please give a plain statement of what
occurred.}\label{now-please-give-a-plain-statement-of-what-occurred.}}

Now please give a plain statement of what occurred.

\hypertarget{you-can-take-a-vacation-on-pay.}{%
\subsection{You can take a vacation on
pay.}\label{you-can-take-a-vacation-on-pay.}}

You can take a vacation on pay.

\hypertarget{they-are-big-trees-and-require-plenty-of-room.}{%
\subsection{They are big trees and require plenty of
room.}\label{they-are-big-trees-and-require-plenty-of-room.}}

They are big trees and require plenty of room.

\hypertarget{and-raoul-listened-again-to-the-tale-of-the-house.}{%
\subsection{And Raoul listened again to the tale of the
house.}\label{and-raoul-listened-again-to-the-tale-of-the-house.}}

And Raoul listened again to the tale of the house.

\hypertarget{there-are-no-kiddies-and-half-grown-youths-among-them.}{%
\subsection{There are no kiddies and half grown youths among
them.}\label{there-are-no-kiddies-and-half-grown-youths-among-them.}}

There are no kiddies and half grown youths among them.

\hypertarget{oolong-atoll-was-one-hundred-and-forty-miles-in-circumference.}{%
\subsection{Oolong Atoll was one hundred and forty miles in
circumference.}\label{oolong-atoll-was-one-hundred-and-forty-miles-in-circumference.}}

Oolong Atoll was one hundred and forty miles in circumference.

\hypertarget{mccoy-found-a-stifling-poisonous-atmosphere-in-the-pent-cabin.}{%
\subsection{McCoy found a stifling, poisonous atmosphere in the pent
cabin.}\label{mccoy-found-a-stifling-poisonous-atmosphere-in-the-pent-cabin.}}

McCoy found a stifling, poisonous atmosphere in the pent cabin.

\hypertarget{it-would-give-me-nervous-prostration.}{%
\subsection{It would give me nervous
prostration.}\label{it-would-give-me-nervous-prostration.}}

It would give me nervous prostration.

\hypertarget{she-said-with-chattering-teeth.}{%
\subsection{She said with chattering
teeth.}\label{she-said-with-chattering-teeth.}}

She said with chattering teeth.

\hypertarget{ill-be-out-of-my-head-in-fifteen-minutes.}{%
\subsection{I'll be out of my head in fifteen
minutes.}\label{ill-be-out-of-my-head-in-fifteen-minutes.}}

I'll be out of my head in fifteen minutes.

\hypertarget{i-do-not-blame-you-for-anything-remember-that.}{%
\subsection{I do not blame you for anything; remember
that.}\label{i-do-not-blame-you-for-anything-remember-that.}}

I do not blame you for anything; remember that.

\hypertarget{if-you-mean-to-insinuate-brentwood-began-hotly.}{%
\subsection{If you mean to insinuate -- Brentwood began
hotly.}\label{if-you-mean-to-insinuate-brentwood-began-hotly.}}

If you mean to insinuate -- Brentwood began hotly.

\hypertarget{the-woman-in-you-is-only-incidental-accidental-and-irrelevant.}{%
\subsection{The woman in you is only incidental, accidental, and
irrelevant.}\label{the-woman-in-you-is-only-incidental-accidental-and-irrelevant.}}

The woman in you is only incidental, accidental, and irrelevant.

\hypertarget{there-was-no-forecasting-this-strange-girls-processes.}{%
\subsection{There was no forecasting this strange girl's
processes.}\label{there-was-no-forecasting-this-strange-girls-processes.}}

There was no forecasting this strange girl's processes.

\hypertarget{but-what-they-want-with-your-toothbrush-is-more-than-i-can-imagine.}{%
\subsection{But what they want with your toothbrush is more than I can
imagine.}\label{but-what-they-want-with-your-toothbrush-is-more-than-i-can-imagine.}}

But what they want with your toothbrush is more than I can imagine.

\hypertarget{give-them-their-choice-between-a-fine-or-an-official-whipping.}{%
\subsection{Give them their choice between a fine or an official
whipping.}\label{give-them-their-choice-between-a-fine-or-an-official-whipping.}}

Give them their choice between a fine or an official whipping.

\hypertarget{keep-an-eye-on-him.}{%
\subsection{Keep an eye on him.}\label{keep-an-eye-on-him.}}

Keep an eye on him.

\hypertarget{those-are-my-oysters-he-said-at-last.}{%
\subsection{Those are my oysters, he said at
last.}\label{those-are-my-oysters-he-said-at-last.}}

Those are my oysters, he said at last.

\hypertarget{they-are-not-regular-oyster-pirates-nicholas-continued.}{%
\subsection{They are not regular oyster pirates, Nicholas
continued.}\label{they-are-not-regular-oyster-pirates-nicholas-continued.}}

They are not regular oyster pirates, Nicholas continued.

\hypertarget{one-by-one-the-boys-were-captured.}{%
\subsection{One by one the boys were
captured.}\label{one-by-one-the-boys-were-captured.}}

One by one the boys were captured.

\hypertarget{the-weeks-had-gone-by-and-no-overt-acts-had-been-attempted.}{%
\subsection{The weeks had gone by, and no overt acts had been
attempted.}\label{the-weeks-had-gone-by-and-no-overt-acts-had-been-attempted.}}

The weeks had gone by, and no overt acts had been attempted.

\hypertarget{here-in-the-midmorning-the-first-casualty-occurred.}{%
\subsection{Here, in the midmorning, the first casualty
occurred.}\label{here-in-the-midmorning-the-first-casualty-occurred.}}

Here, in the midmorning, the first casualty occurred.

\hypertarget{they-were-deep-in-the-primeval-forest.}{%
\subsection{They were deep in the primeval
forest.}\label{they-were-deep-in-the-primeval-forest.}}

They were deep in the primeval forest.

\hypertarget{he-had-been-foiled-in-his-attempt-to-escape.}{%
\subsection{He had been foiled in his attempt to
escape.}\label{he-had-been-foiled-in-his-attempt-to-escape.}}

He had been foiled in his attempt to escape.

\hypertarget{and-twenty-men-could-hold-it-with-spears-and-arrows.}{%
\subsection{And twenty men could hold it with spears and
arrows.}\label{and-twenty-men-could-hold-it-with-spears-and-arrows.}}

And twenty men could hold it with spears and arrows.

\hypertarget{bassett-was-a-fastidious-man.}{%
\subsection{Bassett was a fastidious
man.}\label{bassett-was-a-fastidious-man.}}

Bassett was a fastidious man.

\hypertarget{theres-a-big-english-general-right-now-whose-name-is-roberts.}{%
\subsection{There's a big English general right now whose name is
Roberts.}\label{theres-a-big-english-general-right-now-whose-name-is-roberts.}}

There's a big English general right now whose name is Roberts.

\hypertarget{this-tacit-promise-of-continued-acquaintance-gave-saxon-a-little-joy-thrill.}{%
\subsection{This tacit promise of continued acquaintance gave Saxon a
little
joy-thrill.}\label{this-tacit-promise-of-continued-acquaintance-gave-saxon-a-little-joy-thrill.}}

This tacit promise of continued acquaintance gave Saxon a little
joy-thrill.

\hypertarget{i-tell-you-i-am-disgusted-with-this-adventure-tomfoolery-and-rot.}{%
\subsection{I tell you I am disgusted with this adventure tomfoolery and
rot.}\label{i-tell-you-i-am-disgusted-with-this-adventure-tomfoolery-and-rot.}}

I tell you I am disgusted with this adventure tomfoolery and rot.

\hypertarget{from-my-earliest-recollection-my-sleep-was-a-period-of-terror.}{%
\subsection{From my earliest recollection my sleep was a period of
terror.}\label{from-my-earliest-recollection-my-sleep-was-a-period-of-terror.}}

From my earliest recollection my sleep was a period of terror.

\hypertarget{but-all-my-dreams-violated-this-law.}{%
\subsection{But all my dreams violated this
law.}\label{but-all-my-dreams-violated-this-law.}}

But all my dreams violated this law.

\hypertarget{it-is-very-plausible-to-such-people-a-most-convincing-hypothesis.}{%
\subsection{It is very plausible to such people, a most convincing
hypothesis.}\label{it-is-very-plausible-to-such-people-a-most-convincing-hypothesis.}}

It is very plausible to such people, a most convincing hypothesis.

\hypertarget{but-they-make-the-mistake-of-ignoring-their-own-duality.}{%
\subsection{But they make the mistake of ignoring their own
duality.}\label{but-they-make-the-mistake-of-ignoring-their-own-duality.}}

But they make the mistake of ignoring their own duality.

\hypertarget{i-graduated-last-of-my-class.}{%
\subsection{I graduated last of my
class.}\label{i-graduated-last-of-my-class.}}

I graduated last of my class.

\hypertarget{they-had-no-fixed-values-to-be-altered-by-adjectives-and-adverbs.}{%
\subsection{They had no fixed values, to be altered by adjectives and
adverbs.}\label{they-had-no-fixed-values-to-be-altered-by-adjectives-and-adverbs.}}

They had no fixed values, to be altered by adjectives and adverbs.

\hypertarget{he-was-pressing-beyond-the-limits-of-his-vocabulary.}{%
\subsection{He was pressing beyond the limits of his
vocabulary.}\label{he-was-pressing-beyond-the-limits-of-his-vocabulary.}}

He was pressing beyond the limits of his vocabulary.

\hypertarget{very-early-in-my-life-i-separated-from-my-mother.}{%
\subsection{Very early in my life, I separated from my
mother.}\label{very-early-in-my-life-i-separated-from-my-mother.}}

Very early in my life, I separated from my mother.

\hypertarget{his-infernal-chattering-worries-me-even-now-as-i-think-of-it.}{%
\subsection{His infernal chattering worries me even now as I think of
it.}\label{his-infernal-chattering-worries-me-even-now-as-i-think-of-it.}}

His infernal chattering worries me even now as I think of it.

\hypertarget{white-leghorns-said-mrs-mortimer.}{%
\subsection{White Leghorns, said Mrs
Mortimer.}\label{white-leghorns-said-mrs-mortimer.}}

White Leghorns, said Mrs Mortimer.

\hypertarget{massage-under-tension-was-the-cryptic-reply.}{%
\subsection{Massage under tension, was the cryptic
reply.}\label{massage-under-tension-was-the-cryptic-reply.}}

Massage under tension, was the cryptic reply.

\hypertarget{therefore-hurrah-for-the-game.}{%
\subsection{Therefore, hurrah for the
game.}\label{therefore-hurrah-for-the-game.}}

Therefore, hurrah for the game.

\hypertarget{it-lived-in-perpetual-apprehension-of-that-quarter-of-the-compass.}{%
\subsection{It lived in perpetual apprehension of that quarter of the
compass.}\label{it-lived-in-perpetual-apprehension-of-that-quarter-of-the-compass.}}

It lived in perpetual apprehension of that quarter of the compass.

\hypertarget{broken-tooth-yelled-with-fright-and-pain.}{%
\subsection{Broken-Tooth yelled with fright and
pain.}\label{broken-tooth-yelled-with-fright-and-pain.}}

Broken-Tooth yelled with fright and pain.

\hypertarget{thus-was-momentum-gained-in-the-younger-world.}{%
\subsection{Thus was momentum gained in the Younger
World.}\label{thus-was-momentum-gained-in-the-younger-world.}}

Thus was momentum gained in the Younger World.

\hypertarget{saxon-waited-for-she-knew-a-fresh-idea-had-struck-billy.}{%
\subsection{Saxon waited, for she knew a fresh idea had struck
Billy.}\label{saxon-waited-for-she-knew-a-fresh-idea-had-struck-billy.}}

Saxon waited, for she knew a fresh idea had struck Billy.

\hypertarget{we-had-been-chased-by-them-ourselves-more-than-once.}{%
\subsection{We had been chased by them ourselves, more than
once.}\label{we-had-been-chased-by-them-ourselves-more-than-once.}}

We had been chased by them ourselves, more than once.

\hypertarget{he-was-a-wise-hyena.}{%
\subsection{He was a wise hyena.}\label{he-was-a-wise-hyena.}}

He was a wise hyena.

\hypertarget{production-is-doubling-and-quadrupling-upon-itself.}{%
\subsection{Production is doubling and quadrupling upon
itself.}\label{production-is-doubling-and-quadrupling-upon-itself.}}

Production is doubling and quadrupling upon itself.

\hypertarget{and-the-edinburgh-evening-news-says-with-editorial-gloom.}{%
\subsection{And the Edinburgh Evening News says, with editorial
gloom.}\label{and-the-edinburgh-evening-news-says-with-editorial-gloom.}}

And the Edinburgh Evening News says, with editorial gloom.

\hypertarget{with-my-strength-i-slammed-it-full-into-red-eyes-face.}{%
\subsection{With my strength I slammed it full into Red-Eye's
face.}\label{with-my-strength-i-slammed-it-full-into-red-eyes-face.}}

With my strength I slammed it full into Red-Eye's face.

\hypertarget{the-log-on-which-lop-ear-was-lying-got-adrift.}{%
\subsection{The log on which Lop-Ear was lying got
adrift.}\label{the-log-on-which-lop-ear-was-lying-got-adrift.}}

The log on which Lop-Ear was lying got adrift.

\hypertarget{this-is-a-common-experience-with-all-of-us.}{%
\subsection{This is a common experience with all of
us.}\label{this-is-a-common-experience-with-all-of-us.}}

This is a common experience with all of us.

\hypertarget{he-considered-the-victory-already-his-and-stepped-forward-to-the-meat.}{%
\subsection{He considered the victory already his and stepped forward to
the
meat.}\label{he-considered-the-victory-already-his-and-stepped-forward-to-the-meat.}}

He considered the victory already his and stepped forward to the meat.

\hypertarget{it-was-not-red-eyes-way-to-forego-revenge-so-easily.}{%
\subsection{It was not Red-Eye's way to forego revenge so
easily.}\label{it-was-not-red-eyes-way-to-forego-revenge-so-easily.}}

It was not Red-Eye's way to forego revenge so easily.

\hypertarget{whiz-zip-bang.-lop-ear-screamed-with-sudden-anguish.}{%
\subsection{Whiz-zip-bang. Lop-Ear screamed with sudden
anguish.}\label{whiz-zip-bang.-lop-ear-screamed-with-sudden-anguish.}}

Whiz-zip-bang. Lop-Ear screamed with sudden anguish.

\hypertarget{cherokee-identified-himself-with-his-instinct.}{%
\subsection{Cherokee identified himself with his
instinct.}\label{cherokee-identified-himself-with-his-instinct.}}

Cherokee identified himself with his instinct.

\hypertarget{they-were-less-stooped-than-we-less-springy-in-their-movements.}{%
\subsection{They were less stooped than we, less springy in their
movements.}\label{they-were-less-stooped-than-we-less-springy-in-their-movements.}}

They were less stooped than we, less springy in their movements.

\hypertarget{the-fire-people-like-ourselves-lived-in-caves.}{%
\subsection{The Fire People, like ourselves, lived in
caves.}\label{the-fire-people-like-ourselves-lived-in-caves.}}

The Fire People, like ourselves, lived in caves.

\hypertarget{ah-indeed.}{%
\subsection{Ah, indeed.}\label{ah-indeed.}}

Ah, indeed.

\hypertarget{red-eye-never-committed-a-more-outrageous-deed.}{%
\subsection{Red-Eye never committed a more outrageous
deed.}\label{red-eye-never-committed-a-more-outrageous-deed.}}

Red-Eye never committed a more outrageous deed.

\hypertarget{poor-little-crooked-leg-was-terribly-scared.}{%
\subsection{Poor little Crooked-Leg was terribly
scared.}\label{poor-little-crooked-leg-was-terribly-scared.}}

Poor little Crooked-Leg was terribly scared.

\hypertarget{unconsciously-our-yells-and-exclamations-yielded-to-this-rhythm.}{%
\subsection{Unconsciously, our yells and exclamations yielded to this
rhythm.}\label{unconsciously-our-yells-and-exclamations-yielded-to-this-rhythm.}}

Unconsciously, our yells and exclamations yielded to this rhythm.

\hypertarget{this-is-no-place-for-you.}{%
\subsection{This is no place for you.}\label{this-is-no-place-for-you.}}

This is no place for you.

\hypertarget{hell-knock-you-off-a-few-sticks-in-no-time.}{%
\subsection{He'll knock you off a few sticks in no
time.}\label{hell-knock-you-off-a-few-sticks-in-no-time.}}

He'll knock you off a few sticks in no time.

\hypertarget{red-eye-swung-back-and-forth-on-the-branch-farther-down.}{%
\subsection{Red-Eye swung back and forth on the branch farther
down.}\label{red-eye-swung-back-and-forth-on-the-branch-farther-down.}}

Red-Eye swung back and forth on the branch farther down.

\hypertarget{so-unexpected-was-my-charge-that-i-knocked-him-off-his-feet.}{%
\subsection{So unexpected was my charge that I knocked him off his
feet.}\label{so-unexpected-was-my-charge-that-i-knocked-him-off-his-feet.}}

So unexpected was my charge that I knocked him off his feet.

\hypertarget{encouraged-by-my-conduct-big-face-became-a-sudden-ally.}{%
\subsection{Encouraged by my conduct, Big-Face became a sudden
ally.}\label{encouraged-by-my-conduct-big-face-became-a-sudden-ally.}}

Encouraged by my conduct, Big-Face became a sudden ally.

\hypertarget{the-fighting-had-now-become-intermittent.}{%
\subsection{The fighting had now become
intermittent.}\label{the-fighting-had-now-become-intermittent.}}

The fighting had now become intermittent.

\hypertarget{they-obeyed-him-and-went-here-and-there-at-his-commands.}{%
\subsection{They obeyed him, and went here and there at his
commands.}\label{they-obeyed-him-and-went-here-and-there-at-his-commands.}}

They obeyed him, and went here and there at his commands.

\hypertarget{it-was-like-the-beating-of-hoofs.}{%
\subsection{It was like the beating of
hoofs.}\label{it-was-like-the-beating-of-hoofs.}}

It was like the beating of hoofs.

\hypertarget{why-doggone-you-all-shake-again.}{%
\subsection{Why, doggone you all, shake
again.}\label{why-doggone-you-all-shake-again.}}

Why, doggone you all, shake again.

\hypertarget{seventeen-no-eighteen-days-ago.}{%
\subsection{Seventeen, no, eighteen days
ago.}\label{seventeen-no-eighteen-days-ago.}}

Seventeen, no, eighteen days ago.

\hypertarget{you-mean-for-this-state-general-alberta.}{%
\subsection{You mean for this State, General,
Alberta.}\label{you-mean-for-this-state-general-alberta.}}

You mean for this State, General, Alberta.

\hypertarget{he-seemed-to-fill-it-with-his-tremendous-vitality.}{%
\subsection{He seemed to fill it with his tremendous
vitality.}\label{he-seemed-to-fill-it-with-his-tremendous-vitality.}}

He seemed to fill it with his tremendous vitality.

\hypertarget{she-was-trying-to-pass-the-apron-string-around-him.}{%
\subsection{She was trying to pass the apron string around
him.}\label{she-was-trying-to-pass-the-apron-string-around-him.}}

She was trying to pass the apron string around him.

\hypertarget{get-down-and-dig-in.}{%
\subsection{Get down and dig in.}\label{get-down-and-dig-in.}}

Get down and dig in.

\hypertarget{they-are-greatly-delighted-with-anything-that-is-bright-or-giveth-a-sound.}{%
\subsection{They are greatly delighted with anything that is bright or
giveth a
sound.}\label{they-are-greatly-delighted-with-anything-that-is-bright-or-giveth-a-sound.}}

They are greatly delighted with anything that is bright or giveth a
sound.

\hypertarget{they-only-lifted-seven-hundred-and-fifty.}{%
\subsection{They only lifted seven hundred and
fifty.}\label{they-only-lifted-seven-hundred-and-fifty.}}

They only lifted seven hundred and fifty.

\hypertarget{it-was-simple-in-its-way-and-no-virtue-of-his.}{%
\subsection{It was simple, in its way, and no virtue of
his.}\label{it-was-simple-in-its-way-and-no-virtue-of-his.}}

It was simple, in its way, and no virtue of his.

\hypertarget{is-that-pat-hanrahans-mug-looking-hungry-and-willing.}{%
\subsection{Is that Pat Hanrahan's mug looking hungry and
willing.}\label{is-that-pat-hanrahans-mug-looking-hungry-and-willing.}}

Is that Pat Hanrahan's mug looking hungry and willing.

\hypertarget{it-was-more-like-sugar.}{%
\subsection{It was more like sugar.}\label{it-was-more-like-sugar.}}

It was more like sugar.

\hypertarget{im-sure-going-along-with-you-all-elijah.}{%
\subsection{I'm sure going along with you all,
Elijah.}\label{im-sure-going-along-with-you-all-elijah.}}

I'm sure going along with you all, Elijah.

\hypertarget{here-the-explosion-of-mirth-drowned-him-out.}{%
\subsection{Here the explosion of mirth drowned him
out.}\label{here-the-explosion-of-mirth-drowned-him-out.}}

Here the explosion of mirth drowned him out.

\hypertarget{fresh-meat-they-failed-to-obtain.}{%
\subsection{Fresh meat they failed to
obtain.}\label{fresh-meat-they-failed-to-obtain.}}

Fresh meat they failed to obtain.

\hypertarget{a-burst-of-laughter-was-his-reward.}{%
\subsection{A burst of laughter was his
reward.}\label{a-burst-of-laughter-was-his-reward.}}

A burst of laughter was his reward.

\hypertarget{you-dont-catch-me-at-any-such-foolishness.}{%
\subsection{You don't catch me at any such
foolishness.}\label{you-dont-catch-me-at-any-such-foolishness.}}

You don't catch me at any such foolishness.

\hypertarget{a-month-passed-by-and-bonanza-creek-remained-quiet.}{%
\subsection{A month passed by, and Bonanza Creek remained
quiet.}\label{a-month-passed-by-and-bonanza-creek-remained-quiet.}}

A month passed by, and Bonanza Creek remained quiet.

\hypertarget{they-continued-valiantly-to-lie-but-the-truth-continued-to-outrun-them.}{%
\subsection{They continued valiantly to lie, but the truth continued to
outrun
them.}\label{they-continued-valiantly-to-lie-but-the-truth-continued-to-outrun-them.}}

They continued valiantly to lie, but the truth continued to outrun them.

\hypertarget{earth-and-gravel-seemed-to-fill-the-pan.}{%
\subsection{Earth and gravel seemed to fill the
pan.}\label{earth-and-gravel-seemed-to-fill-the-pan.}}

Earth and gravel seemed to fill the pan.

\hypertarget{but-he-no-longer-cared-quite-so-much-for-that-form-of-diversion.}{%
\subsection{But he no longer cared quite so much for that form of
diversion.}\label{but-he-no-longer-cared-quite-so-much-for-that-form-of-diversion.}}

But he no longer cared quite so much for that form of diversion.

\hypertarget{but-he-did-not-broach-it-preferring-to-mature-it-carefully.}{%
\subsection{But he did not broach it, preferring to mature it
carefully.}\label{but-he-did-not-broach-it-preferring-to-mature-it-carefully.}}

But he did not broach it, preferring to mature it carefully.

\hypertarget{nope-not-the-slightest-idea.}{%
\subsection{Nope, not the slightest
idea.}\label{nope-not-the-slightest-idea.}}

Nope, not the slightest idea.

\hypertarget{it-is-not-an-attempt-to-smash-the-market.}{%
\subsection{It is not an attempt to smash the
market.}\label{it-is-not-an-attempt-to-smash-the-market.}}

It is not an attempt to smash the market.

\hypertarget{we-have-plenty-of-capital-ourselves-and-yet-we-want-more.}{%
\subsection{We have plenty of capital ourselves, and yet we want
more.}\label{we-have-plenty-of-capital-ourselves-and-yet-we-want-more.}}

We have plenty of capital ourselves, and yet we want more.

\hypertarget{these-rumors-may-even-originate-with-us.}{%
\subsection{These rumors may even originate with
us.}\label{these-rumors-may-even-originate-with-us.}}

These rumors may even originate with us.

\hypertarget{a-wildly-exciting-time-was-his-during-the-week-preceding-thursday-the-eighteenth.}{%
\subsection{A wildly exciting time was his during the week preceding
Thursday the
eighteenth.}\label{a-wildly-exciting-time-was-his-during-the-week-preceding-thursday-the-eighteenth.}}

A wildly exciting time was his during the week preceding Thursday the
eighteenth.

\hypertarget{there-is-not-an-iota-of-truth-in-it-certainly-not.}{%
\subsection{There is not an iota of truth in it, certainly
not.}\label{there-is-not-an-iota-of-truth-in-it-certainly-not.}}

There is not an iota of truth in it, certainly not.

\hypertarget{i-just-do-appreciate-it-without-being-able-to-express-my-feelings.}{%
\subsection{I just do appreciate it without being able to express my
feelings.}\label{i-just-do-appreciate-it-without-being-able-to-express-my-feelings.}}

I just do appreciate it without being able to express my feelings.

\hypertarget{in-partnership-with-daylight-the-pair-raided-the-san-jose-interurban.}{%
\subsection{In partnership with Daylight, the pair raided the San Jose
Interurban.}\label{in-partnership-with-daylight-the-pair-raided-the-san-jose-interurban.}}

In partnership with Daylight, the pair raided the San Jose Interurban.

\hypertarget{he-saw-all-men-in-the-business-game-doing-this.}{%
\subsection{He saw all men in the business game doing
this.}\label{he-saw-all-men-in-the-business-game-doing-this.}}

He saw all men in the business game doing this.

\hypertarget{it-issued-a-rate-of-forty-two-dollars-a-car-on-charcoal.}{%
\subsection{It issued a rate of forty two dollars a car on
charcoal.}\label{it-issued-a-rate-of-forty-two-dollars-a-car-on-charcoal.}}

It issued a rate of forty two dollars a car on charcoal.

\hypertarget{he-saw-only-the-effect-in-a-general-sketchy-way.}{%
\subsection{He saw only the effect in a general, sketchy
way.}\label{he-saw-only-the-effect-in-a-general-sketchy-way.}}

He saw only the effect in a general, sketchy way.

\hypertarget{points-of-view-new-ideas-life.}{%
\subsection{Points of view, new ideas,
life.}\label{points-of-view-new-ideas-life.}}

Points of view, new ideas, life.

\hypertarget{but-lifes-worth-more-than-cash-she-argued.}{%
\subsection{But life's worth more than cash, she
argued.}\label{but-lifes-worth-more-than-cash-she-argued.}}

But life's worth more than cash, she argued.

\hypertarget{the-butchers-and-meat-cutters-refused-to-handle-meat-destined-for-unfair-restaurants.}{%
\subsection{The butchers and meat cutters refused to handle meat
destined for unfair
restaurants.}\label{the-butchers-and-meat-cutters-refused-to-handle-meat-destined-for-unfair-restaurants.}}

The butchers and meat cutters refused to handle meat destined for unfair
restaurants.

\hypertarget{your-price-my-son-is-just-about-thirty-per-week.}{%
\subsection{Your price, my son, is just about thirty per
week.}\label{your-price-my-son-is-just-about-thirty-per-week.}}

Your price, my son, is just about thirty per week.

\hypertarget{this-sound-did-not-disturb-the-hush-and-awe-of-the-place.}{%
\subsection{This sound did not disturb the hush and awe of the
place.}\label{this-sound-did-not-disturb-the-hush-and-awe-of-the-place.}}

This sound did not disturb the hush and awe of the place.

\hypertarget{thats-why-its-boundaries-are-all-gouged-and-jagged.}{%
\subsection{That's why its boundaries are all gouged and
jagged.}\label{thats-why-its-boundaries-are-all-gouged-and-jagged.}}

That's why its boundaries are all gouged and jagged.

\hypertarget{how-old-are-you-daddy.}{%
\subsection{How old are you, daddy.}\label{how-old-are-you-daddy.}}

How old are you, daddy.

\hypertarget{but-in-the-canyons-water-was-plentiful-and-also-a-luxuriant-forest-growth.}{%
\subsection{But in the canyons water was plentiful and also a luxuriant
forest
growth.}\label{but-in-the-canyons-water-was-plentiful-and-also-a-luxuriant-forest-growth.}}

But in the canyons water was plentiful and also a luxuriant forest
growth.

\hypertarget{my-names-ferguson.}{%
\subsection{My name's Ferguson.}\label{my-names-ferguson.}}

My name's Ferguson.

\hypertarget{daylight-found-himself-charmed-and-made-curious-by-the-little-man.}{%
\subsection{Daylight found himself charmed and made curious by the
little
man.}\label{daylight-found-himself-charmed-and-made-curious-by-the-little-man.}}

Daylight found himself charmed and made curious by the little man.

\hypertarget{to-his-surprise-her-answer-was-flat-and-uncompromising.}{%
\subsection{To his surprise, her answer was flat and
uncompromising.}\label{to-his-surprise-her-answer-was-flat-and-uncompromising.}}

To his surprise, her answer was flat and uncompromising.

\hypertarget{the-farmer-works-the-soil-and-produces-grain.}{%
\subsection{The farmer works the soil and produces
grain.}\label{the-farmer-works-the-soil-and-produces-grain.}}

The farmer works the soil and produces grain.

\hypertarget{thats-what-carnegie-did.}{%
\subsection{That's what Carnegie did.}\label{thats-what-carnegie-did.}}

That's what Carnegie did.

\hypertarget{i-cant-argue-with-you-and-you-know-that.}{%
\subsection{I can't argue with you, and you know
that.}\label{i-cant-argue-with-you-and-you-know-that.}}

I can't argue with you, and you know that.

\hypertarget{bob-growing-disgusted-turned-back-suddenly-and-attempted-to-pass-mab.}{%
\subsection{Bob, growing disgusted, turned back suddenly and attempted
to pass
Mab.}\label{bob-growing-disgusted-turned-back-suddenly-and-attempted-to-pass-mab.}}

Bob, growing disgusted, turned back suddenly and attempted to pass Mab.

\hypertarget{it-was-my-idea-to-a-tee.}{%
\subsection{It was my idea to a tee.}\label{it-was-my-idea-to-a-tee.}}

It was my idea to a tee.

\hypertarget{mab-she-said.}{%
\subsection{Mab, she said.}\label{mab-she-said.}}

Mab, she said.

\hypertarget{ill-go-over-tomorrow-afternoon.}{%
\subsection{I'll go over tomorrow
afternoon.}\label{ill-go-over-tomorrow-afternoon.}}

I'll go over tomorrow afternoon.

\hypertarget{but-he-reconciled-himself-to-it-by-an-act-of-faith.}{%
\subsection{But he reconciled himself to it by an act of
faith.}\label{but-he-reconciled-himself-to-it-by-an-act-of-faith.}}

But he reconciled himself to it by an act of faith.

\hypertarget{there-is-that-magnificent-bob-eating-his-head-off-in-the-stable.}{%
\subsection{There is that magnificent Bob, eating his head off in the
stable.}\label{there-is-that-magnificent-bob-eating-his-head-off-in-the-stable.}}

There is that magnificent Bob, eating his head off in the stable.

\hypertarget{already-he-had-begun-borrowing-from-the-banks.}{%
\subsection{Already he had begun borrowing from the
banks.}\label{already-he-had-begun-borrowing-from-the-banks.}}

Already he had begun borrowing from the banks.

\hypertarget{its-the-strap-hangers-thatll-keep-us-from-going-under.}{%
\subsection{It's the strap hangers that'll keep us from going
under.}\label{its-the-strap-hangers-thatll-keep-us-from-going-under.}}

It's the strap hangers that'll keep us from going under.

\hypertarget{as-for-himself-werent-the-street-railway-earnings-increasing-steadily.}{%
\subsection{As for himself, weren't the street railway earnings
increasing
steadily.}\label{as-for-himself-werent-the-street-railway-earnings-increasing-steadily.}}

As for himself, weren't the street railway earnings increasing steadily.

\hypertarget{a-rising-tide-of-fat-had-submerged-them.}{%
\subsection{A rising tide of fat had submerged
them.}\label{a-rising-tide-of-fat-had-submerged-them.}}

A rising tide of fat had submerged them.

\hypertarget{call-me-that-again-he-murmured-ecstatically.}{%
\subsection{Call me that again, he murmured
ecstatically.}\label{call-me-that-again-he-murmured-ecstatically.}}

Call me that again, he murmured ecstatically.

\hypertarget{in-the-car-were-unwin-and-harrison-while-jones-sat-with-the-chauffeur.}{%
\subsection{In the car were Unwin and Harrison, while Jones sat with the
chauffeur.}\label{in-the-car-were-unwin-and-harrison-while-jones-sat-with-the-chauffeur.}}

In the car were Unwin and Harrison, while Jones sat with the chauffeur.

\hypertarget{and-heres-another-idea.}{%
\subsection{And here's another idea.}\label{and-heres-another-idea.}}

And here's another idea.

\hypertarget{manuel-had-one-besetting-sin.}{%
\subsection{Manuel had one besetting
sin.}\label{manuel-had-one-besetting-sin.}}

Manuel had one besetting sin.

\hypertarget{the-man-smiled-grimly-and-brought-a-hatchet-and-a-club.}{%
\subsection{The man smiled grimly, and brought a hatchet and a
club.}\label{the-man-smiled-grimly-and-brought-a-hatchet-and-a-club.}}

The man smiled grimly, and brought a hatchet and a club.

\hypertarget{curly-rushed-her-antagonist-who-struck-again-and-leaped-aside.}{%
\subsection{Curly rushed her antagonist, who struck again and leaped
aside.}\label{curly-rushed-her-antagonist-who-struck-again-and-leaped-aside.}}

Curly rushed her antagonist, who struck again and leaped aside.

\hypertarget{his-newborn-cunning-gave-him-poise-and-control.}{%
\subsection{His newborn cunning gave him poise and
control.}\label{his-newborn-cunning-gave-him-poise-and-control.}}

His newborn cunning gave him poise and control.

\hypertarget{perrault-found-one-with-head-buried-in-the-grub-box.}{%
\subsection{Perrault found one with head buried in the grub
box.}\label{perrault-found-one-with-head-buried-in-the-grub-box.}}

Perrault found one with head buried in the grub box.

\hypertarget{it-seemed-the-ordained-order-of-things-that-dogs-should-work.}{%
\subsection{It seemed the ordained order of things that dogs should
work.}\label{it-seemed-the-ordained-order-of-things-that-dogs-should-work.}}

It seemed the ordained order of things that dogs should work.

\hypertarget{and-that-was-the-last-of-francois-and-perrault.}{%
\subsection{And that was the last of Francois and
Perrault.}\label{and-that-was-the-last-of-francois-and-perrault.}}

And that was the last of Francois and Perrault.

\hypertarget{mercedes-screamed-cried-laughed-and-manifested-the-chaotic-abandonment-of-hysteria.}{%
\subsection{Mercedes screamed, cried, laughed, and manifested the
chaotic abandonment of
hysteria.}\label{mercedes-screamed-cried-laughed-and-manifested-the-chaotic-abandonment-of-hysteria.}}

Mercedes screamed, cried, laughed, and manifested the chaotic
abandonment of hysteria.

\hypertarget{the-eldorado-emptied-its-occupants-into-the-street-to-see-the-test.}{%
\subsection{The Eldorado emptied its occupants into the street to see
the
test.}\label{the-eldorado-emptied-its-occupants-into-the-street-to-see-the-test.}}

The Eldorado emptied its occupants into the street to see the test.

\hypertarget{he-could-feel-a-new-stir-in-the-land.}{%
\subsection{He could feel a new stir in the
land.}\label{he-could-feel-a-new-stir-in-the-land.}}

He could feel a new stir in the land.

\hypertarget{so-we-have-to-fit-the-boat-throughout-with-oil-lamps-as-well.}{%
\subsection{So we have to fit the boat throughout with oil lamps as
well.}\label{so-we-have-to-fit-the-boat-throughout-with-oil-lamps-as-well.}}

So we have to fit the boat throughout with oil lamps as well.

\hypertarget{it-will-break-our-hearts-and-our-backs-to-hoist-anchor-by-hand.}{%
\subsection{It will break our hearts and our backs to hoist anchor by
hand.}\label{it-will-break-our-hearts-and-our-backs-to-hoist-anchor-by-hand.}}

It will break our hearts and our backs to hoist anchor by hand.

\hypertarget{there-is-another-virtue-in-these-bulkheads.}{%
\subsection{There is another virtue in these
bulkheads.}\label{there-is-another-virtue-in-these-bulkheads.}}

There is another virtue in these bulkheads.

\hypertarget{but-i-am-at-the-end-of-my-resources.}{%
\subsection{But I am at the end of my
resources.}\label{but-i-am-at-the-end-of-my-resources.}}

But I am at the end of my resources.

\hypertarget{now-our-figuring-was-all-right.}{%
\subsection{Now our figuring was all
right.}\label{now-our-figuring-was-all-right.}}

Now our figuring was all right.

\hypertarget{it-lasted-as-a-deterrent-for-two-days.}{%
\subsection{It lasted as a deterrent for two
days.}\label{it-lasted-as-a-deterrent-for-two-days.}}

It lasted as a deterrent for two days.

\hypertarget{the-added-weight-had-a-velocity-of-fifteen-miles-per-hour.}{%
\subsection{The added weight had a velocity of fifteen miles per
hour.}\label{the-added-weight-had-a-velocity-of-fifteen-miles-per-hour.}}

The added weight had a velocity of fifteen miles per hour.

\hypertarget{it-is-also-an-insidious-deceitful-sun.}{%
\subsection{It is also an insidious, deceitful
sun.}\label{it-is-also-an-insidious-deceitful-sun.}}

It is also an insidious, deceitful sun.

\hypertarget{the-portuguese-boy-crawled-nearer-and-nearer.}{%
\subsection{The Portuguese boy crawled nearer and
nearer.}\label{the-portuguese-boy-crawled-nearer-and-nearer.}}

The Portuguese boy crawled nearer and nearer.

\hypertarget{the-portuguese-boy-passed-the-hawaiian.}{%
\subsection{The Portuguese boy passed the
Hawaiian.}\label{the-portuguese-boy-passed-the-hawaiian.}}

The Portuguese boy passed the Hawaiian.

\hypertarget{when-i-came-to-i-was-waving-my-hat-and-murmuring-ecstatically.}{%
\subsection{When I came to I was waving my hat and murmuring
ecstatically.}\label{when-i-came-to-i-was-waving-my-hat-and-murmuring-ecstatically.}}

When I came to I was waving my hat and murmuring ecstatically.

\hypertarget{by-golly-the-boy-wins.}{%
\subsection{By golly, the boy wins.}\label{by-golly-the-boy-wins.}}

By golly, the boy wins.

\hypertarget{halfway-around-the-track-one-donkey-got-into-an-argument-with-its-rider.}{%
\subsection{Halfway around the track one donkey got into an argument
with its
rider.}\label{halfway-around-the-track-one-donkey-got-into-an-argument-with-its-rider.}}

Halfway around the track one donkey got into an argument with its rider.

\hypertarget{mcveigh-when-he-returns-from-a-trip-to-honolulu.}{%
\subsection{McVeigh when he returns from a trip to
Honolulu.}\label{mcveigh-when-he-returns-from-a-trip-to-honolulu.}}

McVeigh when he returns from a trip to Honolulu.

\hypertarget{obviously-it-was-a-disease-that-could-be-contracted-by-contact.}{%
\subsection{Obviously, it was a disease that could be contracted by
contact.}\label{obviously-it-was-a-disease-that-could-be-contracted-by-contact.}}

Obviously, it was a disease that could be contracted by contact.

\hypertarget{otherwise-no-restriction-is-put-upon-their-seafaring.}{%
\subsection{Otherwise no restriction is put upon their
seafaring.}\label{otherwise-no-restriction-is-put-upon-their-seafaring.}}

Otherwise no restriction is put upon their seafaring.

\hypertarget{they-do-not-know-the-length-of-time-of-incubation.}{%
\subsection{They do not know the length of time of
incubation.}\label{they-do-not-know-the-length-of-time-of-incubation.}}

They do not know the length of time of incubation.

\hypertarget{enters-now-the-psychology-of-the-situation.}{%
\subsection{Enters now the psychology of the
situation.}\label{enters-now-the-psychology-of-the-situation.}}

Enters now the psychology of the situation.

\hypertarget{it-was-not-exactly-a-deportation.}{%
\subsection{It was not exactly a
deportation.}\label{it-was-not-exactly-a-deportation.}}

It was not exactly a deportation.

\hypertarget{quick-was-the-disappointment-in-his-face-yet-smiling-was-the-acquiescence.}{%
\subsection{Quick was the disappointment in his face, yet smiling was
the
acquiescence.}\label{quick-was-the-disappointment-in-his-face-yet-smiling-was-the-acquiescence.}}

Quick was the disappointment in his face, yet smiling was the
acquiescence.

\hypertarget{nevertheless-we-found-ourselves-once-more-in-the-high-seat-of-abundance.}{%
\subsection{Nevertheless we found ourselves once more in the high seat
of
abundance.}\label{nevertheless-we-found-ourselves-once-more-in-the-high-seat-of-abundance.}}

Nevertheless we found ourselves once more in the high seat of abundance.

\hypertarget{wada-and-nakata-were-in-a-bit-of-a-funk.}{%
\subsection{Wada and Nakata were in a bit of a
funk.}\label{wada-and-nakata-were-in-a-bit-of-a-funk.}}

Wada and Nakata were in a bit of a funk.

\hypertarget{the-boy-at-the-wheel-lost-his-head.}{%
\subsection{The boy at the wheel lost his
head.}\label{the-boy-at-the-wheel-lost-his-head.}}

The boy at the wheel lost his head.

\hypertarget{to-her-the-bridge-was-tambo-which-is-the-native-for-taboo.}{%
\subsection{To her the bridge was tambo, which is the native for
taboo.}\label{to-her-the-bridge-was-tambo-which-is-the-native-for-taboo.}}

To her the bridge was tambo, which is the native for taboo.

\hypertarget{a-half-a-case-of-tobacco-was-worth-three-pounds.}{%
\subsection{A half a case of tobacco was worth three
pounds.}\label{a-half-a-case-of-tobacco-was-worth-three-pounds.}}

A half a case of tobacco was worth three pounds.

\hypertarget{what-do-you-mean-by-this-outrageous-conduct.}{%
\subsection{What do you mean by this outrageous
conduct.}\label{what-do-you-mean-by-this-outrageous-conduct.}}

What do you mean by this outrageous conduct.

\hypertarget{but-martin-smiled-a-superior-smile.}{%
\subsection{But Martin smiled a superior
smile.}\label{but-martin-smiled-a-superior-smile.}}

But Martin smiled a superior smile.

\hypertarget{by-that-answer-my-professional-medical-prestige-stood-or-fell.}{%
\subsection{By that answer my professional medical prestige stood or
fell.}\label{by-that-answer-my-professional-medical-prestige-stood-or-fell.}}

By that answer my professional medical prestige stood or fell.

\hypertarget{at-sea-monday-march-16-1908.}{%
\subsection{At sea, Monday, March 16,
1908.}\label{at-sea-monday-march-16-1908.}}

At sea, Monday, March 16, 1908.

\hypertarget{at-sea-wednesday-march-18-1908.}{%
\subsection{At sea, Wednesday, March 18,
1908.}\label{at-sea-wednesday-march-18-1908.}}

At sea, Wednesday, March 18, 1908.

\hypertarget{yes-sir-i-corrected.}{%
\subsection{Yes, sir, I corrected.}\label{yes-sir-i-corrected.}}

Yes, sir, I corrected.

\hypertarget{violent-life-and-athletic-sports-had-never-appealed-to-me.}{%
\subsection{Violent life and athletic sports had never appealed to
me.}\label{violent-life-and-athletic-sports-had-never-appealed-to-me.}}

Violent life and athletic sports had never appealed to me.

\hypertarget{you-live-on-an-income-which-your-father-earned.}{%
\subsection{You live on an income which your father
earned.}\label{you-live-on-an-income-which-your-father-earned.}}

You live on an income which your father earned.

\hypertarget{he-was-worth-nothing-to-the-world.}{%
\subsection{He was worth nothing to the
world.}\label{he-was-worth-nothing-to-the-world.}}

He was worth nothing to the world.

\hypertarget{then-you-dont-believe-in-altruism.}{%
\subsection{Then you don't believe in
altruism.}\label{then-you-dont-believe-in-altruism.}}

Then you don't believe in altruism.

\hypertarget{the-creative-joy-i-murmured.}{%
\subsection{The creative joy, I
murmured.}\label{the-creative-joy-i-murmured.}}

The creative joy, I murmured.

\hypertarget{he-deluged-me-overwhelmed-me-with-argument.}{%
\subsection{He deluged me, overwhelmed me with
argument.}\label{he-deluged-me-overwhelmed-me-with-argument.}}

He deluged me, overwhelmed me with argument.

\hypertarget{ah-it-is-growing-dark-and-darker.}{%
\subsection{Ah, it is growing dark and
darker.}\label{ah-it-is-growing-dark-and-darker.}}

Ah, it is growing dark and darker.

\hypertarget{i-was-hump-cabin-boy-on-the-schooner-ghost.}{%
\subsection{I was Hump, cabin boy on the schooner
Ghost.}\label{i-was-hump-cabin-boy-on-the-schooner-ghost.}}

I was Hump, cabin boy on the schooner Ghost.

\hypertarget{a-sinewy-hand-dripping-with-water-was-clutching-the-rail.}{%
\subsection{A sinewy hand, dripping with water, was clutching the
rail.}\label{a-sinewy-hand-dripping-with-water-was-clutching-the-rail.}}

A sinewy hand, dripping with water, was clutching the rail.

\hypertarget{no-man-ate-of-the-seal-meat-or-the-oil.}{%
\subsection{No man ate of the seal meat or the
oil.}\label{no-man-ate-of-the-seal-meat-or-the-oil.}}

No man ate of the seal meat or the oil.

\hypertarget{i-noticed-blood-spouting-from-kerfoots-left-hand.}{%
\subsection{I noticed blood spouting from Kerfoot's left
hand.}\label{i-noticed-blood-spouting-from-kerfoots-left-hand.}}

I noticed blood spouting from Kerfoot's left hand.

\hypertarget{three-oilers-and-a-fourth-engineer-was-his-greeting.}{%
\subsection{Three oilers and a fourth engineer, was his
greeting.}\label{three-oilers-and-a-fourth-engineer-was-his-greeting.}}

Three oilers and a fourth engineer, was his greeting.

\hypertarget{eighteen-hundred-he-calculated.}{%
\subsection{Eighteen hundred, he
calculated.}\label{eighteen-hundred-he-calculated.}}

Eighteen hundred, he calculated.

\hypertarget{the-sharp-voice-of-wolf-larsen-aroused-me.}{%
\subsection{The sharp voice of Wolf Larsen aroused
me.}\label{the-sharp-voice-of-wolf-larsen-aroused-me.}}

The sharp voice of Wolf Larsen aroused me.

\hypertarget{i-obeyed-and-a-minute-or-two-later-they-stood-before-him.}{%
\subsection{I obeyed, and a minute or two later they stood before
him.}\label{i-obeyed-and-a-minute-or-two-later-they-stood-before-him.}}

I obeyed, and a minute or two later they stood before him.

\hypertarget{but-it-wont-continue-she-said-with-easy-confidence.}{%
\subsection{But it won't continue, she said with easy
confidence.}\label{but-it-wont-continue-she-said-with-easy-confidence.}}

But it won't continue, she said with easy confidence.

\hypertarget{what-i-saw-i-could-not-at-first-believe.}{%
\subsection{What I saw I could not at first
believe.}\label{what-i-saw-i-could-not-at-first-believe.}}

What I saw I could not at first believe.

\hypertarget{the-stout-wood-was-crushed-like-an-eggshell.}{%
\subsection{The stout wood was crushed like an
eggshell.}\label{the-stout-wood-was-crushed-like-an-eggshell.}}

The stout wood was crushed like an eggshell.

\hypertarget{theres-too-much-of-the-schoolboy-in-me.}{%
\subsection{There's too much of the schoolboy in
me.}\label{theres-too-much-of-the-schoolboy-in-me.}}

There's too much of the schoolboy in me.

\hypertarget{i-had-forgotten-their-existence.}{%
\subsection{I had forgotten their
existence.}\label{i-had-forgotten-their-existence.}}

I had forgotten their existence.

\hypertarget{ah-we-were-very-close-together-in-that-moment.}{%
\subsection{Ah, we were very close together in that
moment.}\label{ah-we-were-very-close-together-in-that-moment.}}

Ah, we were very close together in that moment.

\hypertarget{but-she-swung-obediently-on-her-heel-into-the-wind.}{%
\subsection{But she swung obediently on her heel into the
wind.}\label{but-she-swung-obediently-on-her-heel-into-the-wind.}}

But she swung obediently on her heel into the wind.

\hypertarget{they-are-his-tongue-by-which-he-makes-his-knowledge-articulate.}{%
\subsection{They are his tongue, by which he makes his knowledge
articulate.}\label{they-are-his-tongue-by-which-he-makes-his-knowledge-articulate.}}

They are his tongue, by which he makes his knowledge articulate.

\hypertarget{between-the-rush-of-the-cascades-streaks-of-rust-showed-everywhere.}{%
\subsection{Between the rush of the cascades, streaks of rust showed
everywhere.}\label{between-the-rush-of-the-cascades-streaks-of-rust-showed-everywhere.}}

Between the rush of the cascades, streaks of rust showed everywhere.

\hypertarget{hell-never-do-a-tap-of-work-the-whole-voyage.}{%
\subsection{He'll never do a tap of work the whole
Voyage.}\label{hell-never-do-a-tap-of-work-the-whole-voyage.}}

He'll never do a tap of work the whole Voyage.

\hypertarget{captain-west-may-be-a-samurai-but-he-is-also-human.}{%
\subsection{Captain West may be a Samurai, but he is also
human.}\label{captain-west-may-be-a-samurai-but-he-is-also-human.}}

Captain West may be a Samurai, but he is also human.

\hypertarget{and-so-early-in-the-voyage-too.}{%
\subsection{And so early in the voyage,
too.}\label{and-so-early-in-the-voyage-too.}}

And so early in the voyage, too.

\hypertarget{in-the-matter-of-curry-she-is-a-sheer-genius.}{%
\subsection{In the matter of curry she is a sheer
genius.}\label{in-the-matter-of-curry-she-is-a-sheer-genius.}}

In the matter of curry she is a sheer genius.

\hypertarget{the-eastern-heavens-were-equally-spectacular.}{%
\subsection{The eastern heavens were equally
spectacular.}\label{the-eastern-heavens-were-equally-spectacular.}}

The eastern heavens were equally spectacular.

\hypertarget{he-spat-it-out-like-so-much-venom.}{%
\subsection{He spat it out like so much
venom.}\label{he-spat-it-out-like-so-much-venom.}}

He spat it out like so much venom.

\hypertarget{i-saw-mr-pike-nod-his-head-grimly-and-sarcastically.}{%
\subsection{I saw Mr Pike nod his head grimly and
sarcastically.}\label{i-saw-mr-pike-nod-his-head-grimly-and-sarcastically.}}

I saw Mr Pike nod his head grimly and sarcastically.

\hypertarget{he-is-too-keenly-intelligent-too-sharply-sensitive-successfully-to-endure.}{%
\subsection{He is too keenly intelligent, too sharply sensitive,
successfully to
endure.}\label{he-is-too-keenly-intelligent-too-sharply-sensitive-successfully-to-endure.}}

He is too keenly intelligent, too sharply sensitive, successfully to
endure.

\hypertarget{the-night-was-calm-and-snowy.}{%
\subsection{The night was calm and
snowy.}\label{the-night-was-calm-and-snowy.}}

The night was calm and snowy.

\hypertarget{i-sailed-third-mate-in-the-little-vampire-before-you-were-born.}{%
\subsection{I sailed third mate in the little Vampire before you were
born.}\label{i-sailed-third-mate-in-the-little-vampire-before-you-were-born.}}

I sailed third mate in the little Vampire before you were born.

\hypertarget{his-outstretched-arm-dropped-to-his-side-and-he-paused.}{%
\subsection{His outstretched arm dropped to his side, and he
paused.}\label{his-outstretched-arm-dropped-to-his-side-and-he-paused.}}

His outstretched arm dropped to his side, and he paused.

\hypertarget{at-this-moment-i-felt-a-stir-at-my-shoulder.}{%
\subsection{At this moment I felt a stir at my
shoulder.}\label{at-this-moment-i-felt-a-stir-at-my-shoulder.}}

At this moment I felt a stir at my shoulder.

\hypertarget{wada-louis-and-the-steward-are-servants-of-asiatic-breed.}{%
\subsection{Wada, Louis, and the steward are servants of Asiatic
breed.}\label{wada-louis-and-the-steward-are-servants-of-asiatic-breed.}}

Wada, Louis, and the steward are servants of Asiatic breed.

\hypertarget{also-she-has-forbidden-them-smoking-their-pipes-in-the-after-room.}{%
\subsection{Also, she has forbidden them smoking their pipes in the
after-room.}\label{also-she-has-forbidden-them-smoking-their-pipes-in-the-after-room.}}

Also, she has forbidden them smoking their pipes in the after-room.

\hypertarget{i-tried-to-read-george-moore-last-night-and-was-dreadfully-bored.}{%
\subsection{I tried to read George Moore last night, and was dreadfully
bored.}\label{i-tried-to-read-george-moore-last-night-and-was-dreadfully-bored.}}

I tried to read George Moore last night, and was dreadfully bored.

\hypertarget{tom-spink-has-a-harpoon.}{%
\subsection{Tom Spink has a harpoon.}\label{tom-spink-has-a-harpoon.}}

Tom Spink has a harpoon.

\hypertarget{nimrod-replied-with-a-slight-manifestation-of-sensitiveness.}{%
\subsection{Nimrod replied, with a slight manifestation of
sensitiveness.}\label{nimrod-replied-with-a-slight-manifestation-of-sensitiveness.}}

Nimrod replied, with a slight manifestation of sensitiveness.

\hypertarget{and-their-chief-virtue-lies-in-that-they-will-never-wear-out.}{%
\subsection{And their chief virtue lies in that they will never wear
out.}\label{and-their-chief-virtue-lies-in-that-they-will-never-wear-out.}}

And their chief virtue lies in that they will never wear out.

\hypertarget{beyond-dispute-corry-hutchinson-had-married-mabel-holmes.}{%
\subsection{Beyond dispute, Corry Hutchinson had married Mabel
Holmes.}\label{beyond-dispute-corry-hutchinson-had-married-mabel-holmes.}}

Beyond dispute, Corry Hutchinson had married Mabel Holmes.

\hypertarget{no-sir-ee.}{%
\subsection{No-sir-ee.}\label{no-sir-ee.}}

No-sir-ee.

\hypertarget{each-insult-added-to-the-value-of-the-claim.}{%
\subsection{Each insult added to the value of the
claim.}\label{each-insult-added-to-the-value-of-the-claim.}}

Each insult added to the value of the claim.

\hypertarget{for-the-rest-he-was-a-mere-automaton.}{%
\subsection{For the rest, he was a mere
automaton.}\label{for-the-rest-he-was-a-mere-automaton.}}

For the rest, he was a mere automaton.

\hypertarget{the-river-bared-its-bosom-and-snorting-steamboats-challenged-the-wilderness.}{%
\subsection{The river bared its bosom, and snorting steamboats
challenged the
wilderness.}\label{the-river-bared-its-bosom-and-snorting-steamboats-challenged-the-wilderness.}}

The river bared its bosom, and snorting steamboats challenged the
wilderness.

\hypertarget{their-love-burned-with-increasing-brightness.}{%
\subsection{Their love burned with increasing
brightness.}\label{their-love-burned-with-increasing-brightness.}}

Their love burned with increasing brightness.

\hypertarget{they-were-artists-not-biologists.}{%
\subsection{They were artists, not
biologists.}\label{they-were-artists-not-biologists.}}

They were artists, not biologists.

\hypertarget{both-johnny-and-his-mother-shuffled-their-feet-as-they-walked.}{%
\subsection{Both Johnny and his mother shuffled their feet as they
walked.}\label{both-johnny-and-his-mother-shuffled-their-feet-as-they-walked.}}

Both Johnny and his mother shuffled their feet as they walked.

\hypertarget{and-as-in-denial-of-guilt-the-one-legged-boy-replied.}{%
\subsection{And as in denial of guilt, the one-legged boy
replied.}\label{and-as-in-denial-of-guilt-the-one-legged-boy-replied.}}

And as in denial of guilt, the one-legged boy replied.

\hypertarget{burnt-out-like-the-crater-of-a-volcano.}{%
\subsection{Burnt out like the crater of a
volcano.}\label{burnt-out-like-the-crater-of-a-volcano.}}

Burnt out like the crater of a volcano.

\hypertarget{the-boy-obrien-was-specially-maltreated.}{%
\subsection{The boy, O'Brien, was specially
maltreated.}\label{the-boy-obrien-was-specially-maltreated.}}

The boy, O'Brien, was specially maltreated.

\hypertarget{obrien-took-off-his-coat-and-bared-his-right-arm.}{%
\subsection{O'Brien took off his coat and bared his right
arm.}\label{obrien-took-off-his-coat-and-bared-his-right-arm.}}

O'Brien took off his coat and bared his right arm.

\hypertarget{he-bore-no-grudges-and-had-few-enemies.}{%
\subsection{He bore no grudges and had few
enemies.}\label{he-bore-no-grudges-and-had-few-enemies.}}

He bore no grudges and had few enemies.

\hypertarget{and-tom-king-patiently-endured.}{%
\subsection{And Tom King patiently
endured.}\label{and-tom-king-patiently-endured.}}

And Tom King patiently endured.

\hypertarget{king-took-every-advantage-he-knew.}{%
\subsection{King took every advantage he
knew.}\label{king-took-every-advantage-he-knew.}}

King took every advantage he knew.

\hypertarget{the-lines-were-now-very-taut.}{%
\subsection{The lines were now very
taut.}\label{the-lines-were-now-very-taut.}}

The lines were now very taut.

\hypertarget{and-right-there-i-saw-and-knew-it-all.}{%
\subsection{And right there I saw and knew it
all.}\label{and-right-there-i-saw-and-knew-it-all.}}

And right there I saw and knew it all.

\hypertarget{who-the-devil-gave-it-to-you-to-be-judge-and-jury.}{%
\subsection{Who the devil gave it to you to be judge and
jury.}\label{who-the-devil-gave-it-to-you-to-be-judge-and-jury.}}

Who the devil gave it to you to be judge and jury.

\hypertarget{youre-joking-me-sir-the-other-managed-to-articulate.}{%
\subsection{You're joking me, sir, the other managed to
articulate.}\label{youre-joking-me-sir-the-other-managed-to-articulate.}}

You're joking me, sir, the other managed to articulate.

\hypertarget{anything-unusual-or-abnormal-was-sufficient-to-send-a-fellow-to-molokai.}{%
\subsection{Anything unusual or abnormal was sufficient to send a fellow
to
Molokai.}\label{anything-unusual-or-abnormal-was-sufficient-to-send-a-fellow-to-molokai.}}

Anything unusual or abnormal was sufficient to send a fellow to Molokai.

\hypertarget{his-beady-black-eyes-saw-bargains-where-other-men-saw-bankruptcy.}{%
\subsection{His beady black eyes saw bargains where other men saw
bankruptcy.}\label{his-beady-black-eyes-saw-bargains-where-other-men-saw-bankruptcy.}}

His beady black eyes saw bargains where other men saw bankruptcy.

\hypertarget{he-was-an-athlete-and-a-giant.}{%
\subsection{He was an athlete and a
giant.}\label{he-was-an-athlete-and-a-giant.}}

He was an athlete and a giant.

\hypertarget{we-fished-sharks-on-niihau-together.}{%
\subsection{We fished sharks on Niihau
together.}\label{we-fished-sharks-on-niihau-together.}}

We fished sharks on Niihau together.

\hypertarget{the-claudine-was-leaving-next-morning-for-honolulu.}{%
\subsection{The Claudine was leaving next morning for
Honolulu.}\label{the-claudine-was-leaving-next-morning-for-honolulu.}}

The Claudine was leaving next morning for Honolulu.

\hypertarget{in-short-my-joyous-individualism-was-dominated-by-the-orthodox-bourgeois-ethics.}{%
\subsection{In short, my joyous individualism was dominated by the
orthodox bourgeois
ethics.}\label{in-short-my-joyous-individualism-was-dominated-by-the-orthodox-bourgeois-ethics.}}

In short, my joyous individualism was dominated by the orthodox
bourgeois ethics.

\hypertarget{soon-shall-it-be-thrust-back-from-off-prostrate-humanity.}{%
\subsection{Soon shall it be thrust back from off prostrate
humanity.}\label{soon-shall-it-be-thrust-back-from-off-prostrate-humanity.}}

Soon shall it be thrust back from off prostrate humanity.

\hypertarget{yet-in-accordance-with-ernests-test-of-truth-it-worked.}{%
\subsection{Yet, in accordance with Ernest's test of truth, it
worked.}\label{yet-in-accordance-with-ernests-test-of-truth-it-worked.}}

Yet, in accordance with Ernest's test of truth, it worked.

\hypertarget{much-more-ernest-told-them-of-themselves-and-of-his-disillusionment.}{%
\subsection{Much more Ernest told them of themselves and of his
disillusionment.}\label{much-more-ernest-told-them-of-themselves-and-of-his-disillusionment.}}

Much more Ernest told them of themselves and of his disillusionment.

\hypertarget{there-is-more-behind-this-than-a-mere-university-ideal.}{%
\subsection{There is more behind this than a mere university
ideal.}\label{there-is-more-behind-this-than-a-mere-university-ideal.}}

There is more behind this than a mere university ideal.

\hypertarget{no-it-is-a-palace-wherein-there-are-many-servants.}{%
\subsection{No, it is a palace, wherein there are many
servants.}\label{no-it-is-a-palace-wherein-there-are-many-servants.}}

No, it is a palace, wherein there are many servants.

\hypertarget{we-must-give-ourselves-and-not-our-money-alone.}{%
\subsection{We must give ourselves and not our money
alone.}\label{we-must-give-ourselves-and-not-our-money-alone.}}

We must give ourselves and not our money alone.

\hypertarget{we-are-consumed-in-our-own-flesh-pots.}{%
\subsection{We are consumed in our own
flesh-pots.}\label{we-are-consumed-in-our-own-flesh-pots.}}

We are consumed in our own flesh-pots.

\hypertarget{but-here-amongst-ourselves-let-us-speak-out.}{%
\subsection{But here amongst ourselves let us speak
out.}\label{but-here-amongst-ourselves-let-us-speak-out.}}

But here amongst ourselves let us speak out.

\hypertarget{also-there-was-awe-in-their-faces.}{%
\subsection{Also, there was awe in their
faces.}\label{also-there-was-awe-in-their-faces.}}

Also, there was awe in their faces.

\hypertarget{out-of-abstractions-ernest-had-conjured-a-vision-and-made-them-see-it.}{%
\subsection{Out of abstractions Ernest had conjured a vision and made
them see
it.}\label{out-of-abstractions-ernest-had-conjured-a-vision-and-made-them-see-it.}}

Out of abstractions Ernest had conjured a vision and made them see it.

\hypertarget{illuminating-oil-was-becoming-all-profit.}{%
\subsection{Illuminating oil was becoming all
profit.}\label{illuminating-oil-was-becoming-all-profit.}}

Illuminating oil was becoming all profit.

\hypertarget{such-an-act-was-in-direct-violation-of-the-laws-of-the-land.}{%
\subsection{Such an act was in direct violation of the laws of the
land.}\label{such-an-act-was-in-direct-violation-of-the-laws-of-the-land.}}

Such an act was in direct violation of the laws of the land.

\hypertarget{he-was-fond-of-quoting-a-fragment-from-a-certain-poem.}{%
\subsection{He was fond of quoting a fragment from a certain
poem.}\label{he-was-fond-of-quoting-a-fragment-from-a-certain-poem.}}

He was fond of quoting a fragment from a certain poem.

\hypertarget{without-them-he-could-not-run-his-empire.}{%
\subsection{Without them he could not run his
empire.}\label{without-them-he-could-not-run-his-empire.}}

Without them he could not run his empire.

\hypertarget{for-such-countries-nothing-remained-but-reorganization.}{%
\subsection{For such countries nothing remained but
reorganization.}\label{for-such-countries-nothing-remained-but-reorganization.}}

For such countries nothing remained but reorganization.

\hypertarget{they-could-not-continue-their-method-of-producing-surpluses.}{%
\subsection{They could not continue their method of producing
surpluses.}\label{they-could-not-continue-their-method-of-producing-surpluses.}}

They could not continue their method of producing surpluses.

\hypertarget{at-once-would-be-instituted-a-dozen-cooperative-commonwealth-states.}{%
\subsection{At once would be instituted a dozen cooperative commonwealth
states.}\label{at-once-would-be-instituted-a-dozen-cooperative-commonwealth-states.}}

At once would be instituted a dozen cooperative commonwealth states.

\hypertarget{the-oligarchy-wanted-violence-and-it-set-its-agents-provocateurs-to-work.}{%
\subsection{The Oligarchy wanted violence, and it set its agents
provocateurs to
work.}\label{the-oligarchy-wanted-violence-and-it-set-its-agents-provocateurs-to-work.}}

The Oligarchy wanted violence, and it set its agents provocateurs to
work.

\hypertarget{nowhere-did-the-raw-earth-appear.}{%
\subsection{Nowhere did the raw earth
appear.}\label{nowhere-did-the-raw-earth-appear.}}

Nowhere did the raw earth appear.

\hypertarget{the-lush-vegetation-of-that-sheltered-spot-make-a-natural-shield.}{%
\subsection{The lush vegetation of that sheltered spot make a natural
shield.}\label{the-lush-vegetation-of-that-sheltered-spot-make-a-natural-shield.}}

The lush vegetation of that sheltered spot make a natural shield.

\hypertarget{men-who-endure-it-call-it-living-death.}{%
\subsection{Men who endure it, call it living
death.}\label{men-who-endure-it-call-it-living-death.}}

Men who endure it, call it living death.

\hypertarget{as-i-say-he-had-tapped-the-message-very-rapidly.}{%
\subsection{As I say, he had tapped the message very
rapidly.}\label{as-i-say-he-had-tapped-the-message-very-rapidly.}}

As I say, he had tapped the message very rapidly.

\hypertarget{ask-him-i-laughed-then-turned-to-pasquini.}{%
\subsection{Ask him, I laughed, then turned to
Pasquini.}\label{ask-him-i-laughed-then-turned-to-pasquini.}}

Ask him, I laughed, then turned to Pasquini.

\hypertarget{in-what-bucolic-school-of-fence-he-had-been-taught-was-beyond-imagining.}{%
\subsection{In what bucolic school of fence he had been taught was
beyond
imagining.}\label{in-what-bucolic-school-of-fence-he-had-been-taught-was-beyond-imagining.}}

In what bucolic school of fence he had been taught was beyond imagining.

\hypertarget{may-drought-destroy-your-crops.}{%
\subsection{May drought destroy your
crops.}\label{may-drought-destroy-your-crops.}}

May drought destroy your crops.

\hypertarget{dunham-can-your-boy-go-along-with-jesse.}{%
\subsection{Dunham, can your boy go along with
Jesse.}\label{dunham-can-your-boy-go-along-with-jesse.}}

Dunham, can your boy go along with Jesse.

\hypertarget{but-johannes-could-and-did.}{%
\subsection{But Johannes could, and
did.}\label{but-johannes-could-and-did.}}

But Johannes could, and did.

\hypertarget{a-new-preacher-and-a-new-doctrine-come-to-jerusalem.}{%
\subsection{A new preacher and a new doctrine come to
Jerusalem.}\label{a-new-preacher-and-a-new-doctrine-come-to-jerusalem.}}

A new preacher and a new doctrine come to Jerusalem.

\hypertarget{he-would-destroy-all-things-that-are-fixed.}{%
\subsection{He would destroy all things that are
fixed.}\label{he-would-destroy-all-things-that-are-fixed.}}

He would destroy all things that are fixed.

\hypertarget{he-was-an-enthusiast-and-a-desert-dweller.}{%
\subsection{He was an enthusiast and a desert
dweller.}\label{he-was-an-enthusiast-and-a-desert-dweller.}}

He was an enthusiast and a desert dweller.

\hypertarget{what-pascal-glimpsed-with-the-vision-of-a-seer-i-have-lived.}{%
\subsection{What Pascal glimpsed with the vision of a seer, I have
lived.}\label{what-pascal-glimpsed-with-the-vision-of-a-seer-i-have-lived.}}

What Pascal glimpsed with the vision of a seer, I have lived.

\hypertarget{i-should-like-to-engage-just-for-one-whole-life-in-that.}{%
\subsection{I should like to engage just for one whole life in
that.}\label{i-should-like-to-engage-just-for-one-whole-life-in-that.}}

I should like to engage just for one whole life in that.

\hypertarget{yea-so-are-all-the-lesser-animals-of-today-clean.}{%
\subsection{Yea, so are all the lesser animals of today
clean.}\label{yea-so-are-all-the-lesser-animals-of-today-clean.}}

Yea, so are all the lesser animals of today clean.

\hypertarget{the-warden-with-a-quart-of-champagne.}{%
\subsection{The Warden with a quart of
champagne.}\label{the-warden-with-a-quart-of-champagne.}}

The Warden with a quart of champagne.

\hypertarget{without-a-doubt-some-of-them-have-dinner-engagements.}{%
\subsection{Without a doubt, some of them have dinner
engagements.}\label{without-a-doubt-some-of-them-have-dinner-engagements.}}

Without a doubt, some of them have dinner engagements.

\hypertarget{i-had-been-born-with-no-organic-chemical-predisposition-toward-alcohol.}{%
\subsection{I had been born with no organic, chemical predisposition
toward
alcohol.}\label{i-had-been-born-with-no-organic-chemical-predisposition-toward-alcohol.}}

I had been born with no organic, chemical predisposition toward alcohol.

\hypertarget{he-may-anticipate-the-day-of-his-death.}{%
\subsection{He may anticipate the day of his
death.}\label{he-may-anticipate-the-day-of-his-death.}}

He may anticipate the day of his death.

\hypertarget{the-italian-rancho-was-a-bachelor-establishment.}{%
\subsection{The Italian rancho was a bachelor
establishment.}\label{the-italian-rancho-was-a-bachelor-establishment.}}

The Italian rancho was a bachelor establishment.

\hypertarget{i-lost-my-balance-and-pitched-head-foremost-into-the-ooze.}{%
\subsection{I lost my balance and pitched head foremost into the
ooze.}\label{i-lost-my-balance-and-pitched-head-foremost-into-the-ooze.}}

I lost my balance and pitched head foremost into the ooze.

\hypertarget{men-like-joe-goose-dated-existence-from-drunk-to-drunk.}{%
\subsection{Men like Joe Goose dated existence from drunk to
drunk.}\label{men-like-joe-goose-dated-existence-from-drunk-to-drunk.}}

Men like Joe Goose dated existence from drunk to drunk.

\hypertarget{also-churches-and-preachers-i-had-never-known.}{%
\subsection{Also, churches and preachers I had never
known.}\label{also-churches-and-preachers-i-had-never-known.}}

Also, churches and preachers I had never known.

\hypertarget{do-you-know-that-we-weigh-every-pound-of-coal-we-burn.}{%
\subsection{Do you know that we weigh every pound of coal we
burn.}\label{do-you-know-that-we-weigh-every-pound-of-coal-we-burn.}}

Do you know that we weigh every pound of coal we burn.

\hypertarget{this-also-became-part-of-the-daily-schedule.}{%
\subsection{This also became part of the daily
schedule.}\label{this-also-became-part-of-the-daily-schedule.}}

This also became part of the daily schedule.

\hypertarget{all-an-appearance-can-know-is-mirage.}{%
\subsection{All an appearance can know is
mirage.}\label{all-an-appearance-can-know-is-mirage.}}

All an appearance can know is mirage.

\hypertarget{yet-he-dreams-he-is-immortal-i-argue-feebly.}{%
\subsection{Yet he dreams he is immortal, I argue
feebly.}\label{yet-he-dreams-he-is-immortal-i-argue-feebly.}}

Yet he dreams he is immortal, I argue feebly.

\hypertarget{i-am-writing-these-lines-in-honolulu-hawaii.}{%
\subsection{I am writing these lines in Honolulu,
Hawaii.}\label{i-am-writing-these-lines-in-honolulu-hawaii.}}

I am writing these lines in Honolulu, Hawaii.

\hypertarget{jack-london-waikiki-beach-honolulu-oahu.}{%
\subsection{Jack London, Waikiki Beach, Honolulu,
Oahu.}\label{jack-london-waikiki-beach-honolulu-oahu.}}

Jack London, Waikiki Beach, Honolulu, Oahu.

\hypertarget{jerry-was-so-secure-in-his-nook-that-he-did-not-roll-away.}{%
\subsection{Jerry was so secure in his nook that he did not roll
away.}\label{jerry-was-so-secure-in-his-nook-that-he-did-not-roll-away.}}

Jerry was so secure in his nook that he did not roll away.

\hypertarget{why-hes-bought-forty-pounds-of-goods-from-you-already.}{%
\subsection{Why, he's bought forty pounds of goods from you
already.}\label{why-hes-bought-forty-pounds-of-goods-from-you-already.}}

Why, he's bought forty pounds of goods from you already.

\hypertarget{the-last-refugee-had-passed.}{%
\subsection{The last refugee had
passed.}\label{the-last-refugee-had-passed.}}

The last refugee had passed.

\hypertarget{and-the-foundation-stone-of-service-in-his-case-was-obedience.}{%
\subsection{And the foundation stone of service, in his case, was
obedience.}\label{and-the-foundation-stone-of-service-in-his-case-was-obedience.}}

And the foundation stone of service, in his case, was obedience.

\hypertarget{peace-be-unto-you-and-grace-before-the-lord.}{%
\subsection{Peace be unto you and grace before the
Lord.}\label{peace-be-unto-you-and-grace-before-the-lord.}}

Peace be unto you and grace before the Lord.

\hypertarget{his-mouth-opened-words-shaped-vainly-on-his-lips.}{%
\subsection{His mouth opened; words shaped vainly on his
lips.}\label{his-mouth-opened-words-shaped-vainly-on-his-lips.}}

His mouth opened; words shaped vainly on his lips.

\hypertarget{bill-lingered-contemplating-his-work-with-artistic-appreciation.}{%
\subsection{Bill lingered, contemplating his work with artistic
appreciation.}\label{bill-lingered-contemplating-his-work-with-artistic-appreciation.}}

Bill lingered, contemplating his work with artistic appreciation.

\hypertarget{what-the-flaming.}{%
\subsection{What the flaming.}\label{what-the-flaming.}}

What the flaming.

\hypertarget{mrs-mcfees-jaws-brought-together-with-a-snap.}{%
\subsection{Mrs McFee's jaws brought together with a
snap.}\label{mrs-mcfees-jaws-brought-together-with-a-snap.}}

Mrs McFee's jaws brought together with a snap.

\hypertarget{then-it-is-as-i-said-womble-announced-with-finality.}{%
\subsection{Then it is as I said, Womble announced with
finality.}\label{then-it-is-as-i-said-womble-announced-with-finality.}}

Then it is as I said, Womble announced with finality.

\hypertarget{with-them-were-indians-also-three-other-men.}{%
\subsection{With them were Indians, also three other
men.}\label{with-them-were-indians-also-three-other-men.}}

With them were Indians, also three other men.

\hypertarget{dennins-hands-were-released-long-enough-for-him-to-sign-the-document.}{%
\subsection{Dennin's hands were released long enough for him to sign the
document.}\label{dennins-hands-were-released-long-enough-for-him-to-sign-the-document.}}

Dennin's hands were released long enough for him to sign the document.

\hypertarget{now-irvine-was-a-man-of-impulse-a-poet.}{%
\subsection{Now Irvine was a man of impulse, a
poet.}\label{now-irvine-was-a-man-of-impulse-a-poet.}}

Now Irvine was a man of impulse, a poet.

\hypertarget{he-was-just-bursting-with-joy-joy-over-what.}{%
\subsection{He was just bursting with joy, joy over
what.}\label{he-was-just-bursting-with-joy-joy-over-what.}}

He was just bursting with joy, joy over what.

\hypertarget{at-lake-linderman-i-had-one-canoe-very-good-peterborough-canoe.}{%
\subsection{At Lake Linderman I had one canoe, very good Peterborough
canoe.}\label{at-lake-linderman-i-had-one-canoe-very-good-peterborough-canoe.}}

At Lake Linderman I had one canoe, very good Peterborough canoe.

\hypertarget{behind-him-lay-the-thousand-years-long-road-across-all-siberia-and-russia.}{%
\subsection{Behind him lay the thousand-years-long road across all
Siberia and
Russia.}\label{behind-him-lay-the-thousand-years-long-road-across-all-siberia-and-russia.}}

Behind him lay the thousand-years-long road across all Siberia and
Russia.

\hypertarget{he-had-forgotten-to-build-a-fire-and-thaw-out.}{%
\subsection{He had forgotten to build a fire and thaw
out.}\label{he-had-forgotten-to-build-a-fire-and-thaw-out.}}

He had forgotten to build a fire and thaw out.

\hypertarget{i-never-saw-anything-like-her-in-my-life.}{%
\subsection{I never saw anything like her in my
life.}\label{i-never-saw-anything-like-her-in-my-life.}}

I never saw anything like her in my life.

\hypertarget{there-was-no-law-on-the-yukon-save-what-they-made-for-themselves.}{%
\subsection{There was no law on the Yukon save what they made for
themselves.}\label{there-was-no-law-on-the-yukon-save-what-they-made-for-themselves.}}

There was no law on the Yukon save what they made for themselves.

\hypertarget{good-business-man-curly-obrien-was-saying.}{%
\subsection{Good business man, Curly, O'Brien was
saying.}\label{good-business-man-curly-obrien-was-saying.}}

Good business man, Curly, O'Brien was saying.

\hypertarget{there-werent-any-missions-and-he-was-the-man-to-know.}{%
\subsection{There weren't any missions, and he was the man to
know.}\label{there-werent-any-missions-and-he-was-the-man-to-know.}}

There weren't any missions, and he was the man to know.

\hypertarget{and-the-big-persian-knew-of-his-existence-before-he-did-of-hers.}{%
\subsection{And the big Persian knew of his existence before he did of
hers.}\label{and-the-big-persian-knew-of-his-existence-before-he-did-of-hers.}}

And the big Persian knew of his existence before he did of hers.

\hypertarget{once-the-jews-harp-began-emitting-its-barbaric-rhythms-michael-was-helpless.}{%
\subsection{Once the jews harp began emitting its barbaric rhythms,
Michael was
helpless.}\label{once-the-jews-harp-began-emitting-its-barbaric-rhythms-michael-was-helpless.}}

Once the jews harp began emitting its barbaric rhythms, Michael was
helpless.

\hypertarget{but-well-just-postpone-this.}{%
\subsection{But we'll just postpone
this.}\label{but-well-just-postpone-this.}}

But we'll just postpone this.

\hypertarget{there-was-the-emma-louisa.}{%
\subsection{There was the Emma
Louisa.}\label{there-was-the-emma-louisa.}}

There was the Emma Louisa.

\hypertarget{this-is-my-fifth-voyage.}{%
\subsection{This is my fifth voyage.}\label{this-is-my-fifth-voyage.}}

This is my fifth voyage.

\hypertarget{it-was-this-proposition-that-started-the-big-idea-in-daughtrys-mind.}{%
\subsection{It was this proposition that started the big idea in
Daughtry's
mind.}\label{it-was-this-proposition-that-started-the-big-idea-in-daughtrys-mind.}}

It was this proposition that started the big idea in Daughtry's mind.

\hypertarget{daughtry-elaborated-on-the-counting-trick-by-bringing-cocky-along.}{%
\subsection{Daughtry elaborated on the counting trick by bringing Cocky
along.}\label{daughtry-elaborated-on-the-counting-trick-by-bringing-cocky-along.}}

Daughtry elaborated on the counting trick by bringing Cocky along.

\hypertarget{enjoy-it-he-did-but-principally-for-stewards-sake.}{%
\subsection{Enjoy it he did, but principally for Steward's
sake.}\label{enjoy-it-he-did-but-principally-for-stewards-sake.}}

Enjoy it he did, but principally for Steward's sake.

\hypertarget{i-have-long-noted-your-thirst-unquenchable.}{%
\subsection{I have long noted your thirst
unquenchable.}\label{i-have-long-noted-your-thirst-unquenchable.}}

I have long noted your thirst unquenchable.

\hypertarget{wonder-if-hes-a-lion-dog-charles-suggested.}{%
\subsection{Wonder if he's a lion dog, Charles
suggested.}\label{wonder-if-hes-a-lion-dog-charles-suggested.}}

Wonder if he's a lion dog, Charles suggested.

\hypertarget{we-dont-see-ourselves-as-foolish.}{%
\subsection{We don't see ourselves as
foolish.}\label{we-dont-see-ourselves-as-foolish.}}

We don't see ourselves as foolish.

\hypertarget{he-had-comparatively-no-advantages-at-first.}{%
\subsection{He had comparatively no advantages at
first.}\label{he-had-comparatively-no-advantages-at-first.}}

He had comparatively no advantages at first.

\hypertarget{he-had-proved-it-today-with-his-amateurish-and-sophomoric-productions.}{%
\subsection{He had proved it today, with his amateurish and sophomoric
productions.}\label{he-had-proved-it-today-with-his-amateurish-and-sophomoric-productions.}}

He had proved it today, with his amateurish and sophomoric productions.

\hypertarget{i-was-sick-once-typhoid.}{%
\subsection{I was sick once --
typhoid.}\label{i-was-sick-once-typhoid.}}

I was sick once -- typhoid.

\hypertarget{in-a-way-he-is-my-protege.}{%
\subsection{In a way he is my
protege.}\label{in-a-way-he-is-my-protege.}}

In a way he is my protege.

\hypertarget{we-are-both-children-together.}{%
\subsection{We are both children
together.}\label{we-are-both-children-together.}}

We are both children together.

\hypertarget{its-only-his-indigestion-i-find-fault-with.}{%
\subsection{It's only his indigestion I find fault
with.}\label{its-only-his-indigestion-i-find-fault-with.}}

It's only his indigestion I find fault with.

\hypertarget{shed-make-a-good-wife-for-the-cashier.}{%
\subsection{She'd make a good wife for the
cashier.}\label{shed-make-a-good-wife-for-the-cashier.}}

She'd make a good wife for the cashier.

\hypertarget{gad-do-i-remember-it.}{%
\subsection{Gad, do I remember it.}\label{gad-do-i-remember-it.}}

Gad, do I remember it.

\hypertarget{you-got-out-by-fighting-and-i-through-a-pretty-girl.}{%
\subsection{You got out by fighting, and I through a pretty
girl.}\label{you-got-out-by-fighting-and-i-through-a-pretty-girl.}}

You got out by fighting, and I through a pretty girl.

\hypertarget{i-can-see-that-knife-now.}{%
\subsection{I can see that knife now.}\label{i-can-see-that-knife-now.}}

I can see that knife now.

\hypertarget{when-i-cant-see-beauty-in-woman-i-want-to-die.}{%
\subsection{When I can't see beauty in woman I want to
die.}\label{when-i-cant-see-beauty-in-woman-i-want-to-die.}}

When I can't see beauty in woman I want to die.

\hypertarget{his-slim-fingers-closed-like-steel-about-philips.}{%
\subsection{His slim fingers closed like steel about
Philip's.}\label{his-slim-fingers-closed-like-steel-about-philips.}}

His slim fingers closed like steel about Philip's.

\hypertarget{he-seized-gregson-by-the-arm-and-led-him-to-the-door.}{%
\subsection{He seized Gregson by the arm and led him to the
door.}\label{he-seized-gregson-by-the-arm-and-led-him-to-the-door.}}

He seized Gregson by the arm and led him to the door.

\hypertarget{hear-the-indian-dogs-wailing-down-at-churchill.}{%
\subsection{Hear the Indian dogs wailing down at
Churchill.}\label{hear-the-indian-dogs-wailing-down-at-churchill.}}

Hear the Indian dogs wailing down at Churchill.

\hypertarget{burke-himself-had-criticized-it-because-of-the-smile.}{%
\subsection{Burke himself had criticized it because of the
smile.}\label{burke-himself-had-criticized-it-because-of-the-smile.}}

Burke himself had criticized it because of the smile.

\hypertarget{id-say-there-was-going-to-be-a-glorious-scrap.}{%
\subsection{I'd say there was going to be a glorious
scrap.}\label{id-say-there-was-going-to-be-a-glorious-scrap.}}

I'd say there was going to be a glorious scrap.

\hypertarget{he-turned-the-map-to-gregson-pointing-with-his-finger.}{%
\subsection{He turned the map to Gregson, pointing with his
finger.}\label{he-turned-the-map-to-gregson-pointing-with-his-finger.}}

He turned the map to Gregson, pointing with his finger.

\hypertarget{his-eyes-never-took-themselves-for-an-instant-from-his-companions-face.}{%
\subsection{His eyes never took themselves for an instant from his
companion's
face.}\label{his-eyes-never-took-themselves-for-an-instant-from-his-companions-face.}}

His eyes never took themselves for an instant from his companion's face.

\hypertarget{something-that-whittemore-had-not-yet-said-thrilled-him.}{%
\subsection{Something that Whittemore had not yet said thrilled
him.}\label{something-that-whittemore-had-not-yet-said-thrilled-him.}}

Something that Whittemore had not yet said thrilled him.

\hypertarget{lakes-and-rivers-hundreds-of-them-thousands-of-them.}{%
\subsection{Lakes and rivers, hundreds of them, thousands of
them.}\label{lakes-and-rivers-hundreds-of-them-thousands-of-them.}}

Lakes and rivers, hundreds of them, thousands of them.

\hypertarget{whitefish-gregson-whitefish-and-trout.}{%
\subsection{Whitefish, Gregson, whitefish and
trout.}\label{whitefish-gregson-whitefish-and-trout.}}

Whitefish, Gregson, whitefish and trout.

\hypertarget{they-robbed-me-a-few-years-later.}{%
\subsection{They robbed me a few years
later.}\label{they-robbed-me-a-few-years-later.}}

They robbed me a few years later.

\hypertarget{he-chuckled-as-he-pulled-out-his-pipe-and-began-filling-it.}{%
\subsection{He chuckled as he pulled out his pipe and began filling
it.}\label{he-chuckled-as-he-pulled-out-his-pipe-and-began-filling-it.}}

He chuckled as he pulled out his pipe and began filling it.

\hypertarget{everything-was-working-smoothly-better-than-i-had-expected.}{%
\subsection{Everything was working smoothly, better than I had
expected.}\label{everything-was-working-smoothly-better-than-i-had-expected.}}

Everything was working smoothly, better than I had expected.

\hypertarget{i-was-completely-lost-in-my-work.}{%
\subsection{I was completely lost in my
work.}\label{i-was-completely-lost-in-my-work.}}

I was completely lost in my work.

\hypertarget{his-slim-hands-gripped-the-edges-of-the-table.}{%
\subsection{His slim hands gripped the edges of the
table.}\label{his-slim-hands-gripped-the-edges-of-the-table.}}

His slim hands gripped the edges of the table.

\hypertarget{he-made-no-reply-as-he-waited-for-whittemore-to-continue.}{%
\subsection{He made no reply as he waited for Whittemore to
continue.}\label{he-made-no-reply-as-he-waited-for-whittemore-to-continue.}}

He made no reply as he waited for Whittemore to continue.

\hypertarget{philip-dropped-back-into-his-chair.}{%
\subsection{Philip dropped back into his
chair.}\label{philip-dropped-back-into-his-chair.}}

Philip dropped back into his chair.

\hypertarget{if-i-was-out-of-the-game-it-would-be-easily-made.}{%
\subsection{If I was out of the game it would be easily
made.}\label{if-i-was-out-of-the-game-it-would-be-easily-made.}}

If I was out of the game it would be easily made.

\hypertarget{macdougall-my-engineer-believes-it.}{%
\subsection{MacDougall, my engineer, believes
it.}\label{macdougall-my-engineer-believes-it.}}

MacDougall, my engineer, believes it.

\hypertarget{it-is-growing-every-day-every-hour.}{%
\subsection{It is growing, every day, every
hour.}\label{it-is-growing-every-day-every-hour.}}

It is growing, every day, every hour.

\hypertarget{now-you-understand.}{%
\subsection{Now, you understand.}\label{now-you-understand.}}

Now, you understand.

\hypertarget{you-have-associated-with-some-of-these-men.}{%
\subsection{You have associated with some of these
men.}\label{you-have-associated-with-some-of-these-men.}}

You have associated with some of these men.

\hypertarget{and-theres-no-chivalry-no-quarter-shown-in-this-fight.}{%
\subsection{And there's no chivalry, no quarter shown in this
fight.}\label{and-theres-no-chivalry-no-quarter-shown-in-this-fight.}}

And there's no chivalry, no quarter shown in this fight.

\hypertarget{lord-fitzhugh-is-the-key-to-the-whole-situation.}{%
\subsection{Lord Fitzhugh is the key to the whole
situation.}\label{lord-fitzhugh-is-the-key-to-the-whole-situation.}}

Lord Fitzhugh is the key to the whole situation.

\hypertarget{all-operations-have-been-carried-on-from-montreal-and-toronto.}{%
\subsection{All operations have been carried on from Montreal and
Toronto.}\label{all-operations-have-been-carried-on-from-montreal-and-toronto.}}

All operations have been carried on from Montreal and Toronto.

\hypertarget{gregson-held-a-lighted-match-until-it-burnt-his-fingertips.}{%
\subsection{Gregson held a lighted match until it burnt his
fingertips.}\label{gregson-held-a-lighted-match-until-it-burnt-his-fingertips.}}

Gregson held a lighted match until it burnt his fingertips.

\hypertarget{gregson-had-seated-himself-under-the-lamp-and-was-sharpening-a-pencil.}{%
\subsection{Gregson had seated himself under the lamp and was sharpening
a
pencil.}\label{gregson-had-seated-himself-under-the-lamp-and-was-sharpening-a-pencil.}}

Gregson had seated himself under the lamp and was sharpening a pencil.

\hypertarget{he-caught-himself-with-a-jerk.}{%
\subsection{He caught himself with a
jerk.}\label{he-caught-himself-with-a-jerk.}}

He caught himself with a jerk.

\hypertarget{how-does-your-wager-look-now.}{%
\subsection{How does your wager look
now.}\label{how-does-your-wager-look-now.}}

How does your wager look now.

\hypertarget{he-confessed-that-the-sketch-had-startled-him.}{%
\subsection{He confessed that the sketch had startled
him.}\label{he-confessed-that-the-sketch-had-startled-him.}}

He confessed that the sketch had startled him.

\hypertarget{after-all-the-picture-was-only-a-resemblance.}{%
\subsection{After all, the picture was only a
resemblance.}\label{after-all-the-picture-was-only-a-resemblance.}}

After all, the picture was only a resemblance.

\hypertarget{he-wondered-too-where-roscoe-was.}{%
\subsection{He wondered, too, where Roscoe
was.}\label{he-wondered-too-where-roscoe-was.}}

He wondered, too, where Roscoe was.

\hypertarget{philip-knew-that-she-was-not-an-indian.}{%
\subsection{Philip knew that she was not an
Indian.}\label{philip-knew-that-she-was-not-an-indian.}}

Philip knew that she was not an Indian.

\hypertarget{in-her-haste-to-get-away-she-had-forgotten-these-things.}{%
\subsection{In her haste to get away she had forgotten these
things.}\label{in-her-haste-to-get-away-she-had-forgotten-these-things.}}

In her haste to get away she had forgotten these things.

\hypertarget{philip-took-a-step-toward-gregson-half-determined-to-awaken-him.}{%
\subsection{Philip took a step toward Gregson, half determined to awaken
him.}\label{philip-took-a-step-toward-gregson-half-determined-to-awaken-him.}}

Philip took a step toward Gregson, half determined to awaken him.

\hypertarget{the-thought-set-his-blood-tingling.}{%
\subsection{The thought set his blood
tingling.}\label{the-thought-set-his-blood-tingling.}}

The thought set his blood tingling.

\hypertarget{but-if-pierre-did-not-return-until-tomorrow.}{%
\subsection{But if Pierre did not return, until
tomorrow.}\label{but-if-pierre-did-not-return-until-tomorrow.}}

But if Pierre did not return, until tomorrow.

\hypertarget{ten-minutes-had-not-elapsed-since-he-had-dropped-the-handkerchief.}{%
\subsection{Ten minutes had not elapsed since he had dropped the
handkerchief.}\label{ten-minutes-had-not-elapsed-since-he-had-dropped-the-handkerchief.}}

Ten minutes had not elapsed since he had dropped the handkerchief.

\hypertarget{it-wont-be-for-sale.}{%
\subsection{It won't be for sale.}\label{it-wont-be-for-sale.}}

It won't be for sale.

\hypertarget{for-a-few-moments-he-ate-in-silence.}{%
\subsection{For a few moments he ate in
silence.}\label{for-a-few-moments-he-ate-in-silence.}}

For a few moments he ate in silence.

\hypertarget{philip-did-not-pursue-the-subject.}{%
\subsection{Philip did not pursue the
subject.}\label{philip-did-not-pursue-the-subject.}}

Philip did not pursue the subject.

\hypertarget{philip-produced-a-couple-of-cigars-and-took-a-chair-opposite-him.}{%
\subsection{Philip produced a couple of cigars and took a chair opposite
him.}\label{philip-produced-a-couple-of-cigars-and-took-a-chair-opposite-him.}}

Philip produced a couple of cigars and took a chair opposite him.

\hypertarget{suppose-you-saw-me-at-work-through-the-window.}{%
\subsection{Suppose you saw me at work through the
window.}\label{suppose-you-saw-me-at-work-through-the-window.}}

Suppose you saw me at work through the window.

\hypertarget{he-looked-like-one-who-had-passed-through-an-uncomfortable-hour-or-two.}{%
\subsection{He looked like one who had passed through an uncomfortable
hour or
two.}\label{he-looked-like-one-who-had-passed-through-an-uncomfortable-hour-or-two.}}

He looked like one who had passed through an uncomfortable hour or two.

\hypertarget{there-was-nothing-more-except-a-large-ink-blot-under-the-words.}{%
\subsection{There was nothing more, except a large ink blot under the
words.}\label{there-was-nothing-more-except-a-large-ink-blot-under-the-words.}}

There was nothing more, except a large ink blot under the words.

\hypertarget{all-this-day-gregson-remained-in-the-cabin.}{%
\subsection{All this day Gregson remained in the
cabin.}\label{all-this-day-gregson-remained-in-the-cabin.}}

All this day Gregson remained in the cabin.

\hypertarget{the-sixth-day-he-spent-in-the-cabin-with-gregson.}{%
\subsection{The sixth day he spent in the cabin with
Gregson.}\label{the-sixth-day-he-spent-in-the-cabin-with-gregson.}}

The sixth day he spent in the cabin with Gregson.

\hypertarget{the-flush-was-gone-from-her-face.}{%
\subsection{The flush was gone from her
face.}\label{the-flush-was-gone-from-her-face.}}

The flush was gone from her face.

\hypertarget{that-is-why-i-am-am-rattled-he-laughed.}{%
\subsection{That is why I am, am rattled, he
laughed.}\label{that-is-why-i-am-am-rattled-he-laughed.}}

That is why I am, am rattled, he laughed.

\hypertarget{he-understood-the-meaning-of-the-look.}{%
\subsection{He understood the meaning of the
look.}\label{he-understood-the-meaning-of-the-look.}}

He understood the meaning of the look.

\hypertarget{she-was-even-more-beautiful-than-when-i-saw-her-before.}{%
\subsection{She was even more beautiful than when I saw her,
before.}\label{she-was-even-more-beautiful-than-when-i-saw-her-before.}}

She was even more beautiful than when I saw her, before.

\hypertarget{ill-give-a-thousand-if-you-produce-her-retorted-gregson.}{%
\subsection{I'll give a thousand if you produce her, retorted
Gregson.}\label{ill-give-a-thousand-if-you-produce-her-retorted-gregson.}}

I'll give a thousand if you produce her, retorted Gregson.

\hypertarget{they-have-won-popular-sentiment-through-the-newspapers.}{%
\subsection{They have won popular sentiment through the
newspapers.}\label{they-have-won-popular-sentiment-through-the-newspapers.}}

They have won popular sentiment through the newspapers.

\hypertarget{we-must-achieve-our-own-salvation.}{%
\subsection{We must achieve our own
salvation.}\label{we-must-achieve-our-own-salvation.}}

We must achieve our own salvation.

\hypertarget{in-moments-of-mental-energy-philip-was-restless.}{%
\subsection{In moments of mental energy Philip was
restless.}\label{in-moments-of-mental-energy-philip-was-restless.}}

In moments of mental energy Philip was restless.

\hypertarget{he-would-keep-his-faith-with-gregson-for-the-promised-day-or-two.}{%
\subsection{He would keep his faith with Gregson for the promised day or
two.}\label{he-would-keep-his-faith-with-gregson-for-the-promised-day-or-two.}}

He would keep his faith with Gregson for the promised day or two.

\hypertarget{something-about-it-seemed-to-fascinate-him-to-challenge-his-presence.}{%
\subsection{Something about it seemed to fascinate him, to challenge his
presence.}\label{something-about-it-seemed-to-fascinate-him-to-challenge-his-presence.}}

Something about it seemed to fascinate him, to challenge his presence.

\hypertarget{now-it-was-missing-from-the-wall.}{%
\subsection{Now it was missing from the
wall.}\label{now-it-was-missing-from-the-wall.}}

Now it was missing from the wall.

\hypertarget{he-boiled-himself-some-coffee-and-sat-down-to-wait.}{%
\subsection{He boiled himself some coffee and sat down to
wait.}\label{he-boiled-himself-some-coffee-and-sat-down-to-wait.}}

He boiled himself some coffee and sat down to wait.

\hypertarget{im-going-down-there-with-you-and-im-going-to-fight.}{%
\subsection{I'm going down there with you, and I'm going to
fight.}\label{im-going-down-there-with-you-and-im-going-to-fight.}}

I'm going down there with you, and I'm going to fight.

\hypertarget{now-have-you-got-anything-to-say-against-me-mr-philip.}{%
\subsection{Now have you got anything to say against me, Mr
Philip.}\label{now-have-you-got-anything-to-say-against-me-mr-philip.}}

Now have you got anything to say against me, Mr Philip.

\hypertarget{if-i-meet-her-again-i-shall-apologize-said-eileen.}{%
\subsection{If I meet her again I shall apologize, said
Eileen.}\label{if-i-meet-her-again-i-shall-apologize-said-eileen.}}

If I meet her again I shall apologize, said Eileen.

\hypertarget{below-him-the-shadow-was-broken-into-a-pool-of-rippling-starlight.}{%
\subsection{Below him the shadow was broken into a pool of rippling
starlight.}\label{below-him-the-shadow-was-broken-into-a-pool-of-rippling-starlight.}}

Below him the shadow was broken into a pool of rippling starlight.

\hypertarget{only-the-chance-sound-had-led-him-to-observe-them.}{%
\subsection{Only the chance sound had led him to observe
them.}\label{only-the-chance-sound-had-led-him-to-observe-them.}}

Only the chance sound had led him to observe them.

\hypertarget{could-the-incident-have-anything-to-do-with-jeanne-and-pierre.}{%
\subsection{Could the incident have anything to do with Jeanne and
Pierre.}\label{could-the-incident-have-anything-to-do-with-jeanne-and-pierre.}}

Could the incident have anything to do with Jeanne and Pierre.

\hypertarget{there-was-no-chance-to-fire-without-hitting-him.}{%
\subsection{There was no chance to fire without hitting
him.}\label{there-was-no-chance-to-fire-without-hitting-him.}}

There was no chance to fire without hitting him.

\hypertarget{there-was-no-answer-from-the-other-side.}{%
\subsection{There was no answer from the other
side.}\label{there-was-no-answer-from-the-other-side.}}

There was no answer from the other side.

\hypertarget{then-he-hastened-on-as-pierre-had-guided-him.}{%
\subsection{Then he hastened on, as Pierre had guided
him.}\label{then-he-hastened-on-as-pierre-had-guided-him.}}

Then he hastened on, as Pierre had guided him.

\hypertarget{with-these-arguments-he-convinced-himself-that-he-should-go-on-alone.}{%
\subsection{With these arguments he convinced himself that he should go
on
alone.}\label{with-these-arguments-he-convinced-himself-that-he-should-go-on-alone.}}

With these arguments he convinced himself that he should go on alone.

\hypertarget{yet-behind-them-there-was-another-and-more-powerful-motive.}{%
\subsection{Yet, behind them there was another and more powerful
motive.}\label{yet-behind-them-there-was-another-and-more-powerful-motive.}}

Yet, behind them there was another and more powerful motive.

\hypertarget{in-that-case-he-could-not-miss-them-if-he-used-caution.}{%
\subsection{In that case he could not miss them, if he used
caution.}\label{in-that-case-he-could-not-miss-them-if-he-used-caution.}}

In that case he could not miss them, if he used caution.

\hypertarget{before-philip-could-recover-himself-jeannes-startled-guards-were-upon-him.}{%
\subsection{Before Philip could recover himself Jeanne's startled guards
were upon
him.}\label{before-philip-could-recover-himself-jeannes-startled-guards-were-upon-him.}}

Before Philip could recover himself Jeanne's startled guards were upon
him.

\hypertarget{it-is-the-nearest-refuge.}{%
\subsection{It is the nearest refuge.}\label{it-is-the-nearest-refuge.}}

It is the nearest refuge.

\hypertarget{there-was-pride-and-strength-the-ring-of-triumph-in-his-voice.}{%
\subsection{There was pride and strength, the ring of triumph in his
voice.}\label{there-was-pride-and-strength-the-ring-of-triumph-in-his-voice.}}

There was pride and strength, the ring of triumph in his voice.

\hypertarget{the-truth-of-it-set-jeanne-quivering.}{%
\subsection{The truth of it set Jeanne
quivering.}\label{the-truth-of-it-set-jeanne-quivering.}}

The truth of it set Jeanne quivering.

\hypertarget{tomorrow-it-will-be-strong-enough-for-you-to-stand-upon.}{%
\subsection{Tomorrow it will be strong enough for you to stand
upon.}\label{tomorrow-it-will-be-strong-enough-for-you-to-stand-upon.}}

Tomorrow it will be strong enough for you to stand upon.

\hypertarget{you-were-going-to-leave-after-you-saw-me-on-the-rock.}{%
\subsection{You were going to leave after you saw me on the
rock.}\label{you-were-going-to-leave-after-you-saw-me-on-the-rock.}}

You were going to leave after you saw me on the rock.

\hypertarget{he-bit-his-tongue-and-cursed-himself-at-this-fresh-break.}{%
\subsection{He bit his tongue, and cursed himself at this fresh
break.}\label{he-bit-his-tongue-and-cursed-himself-at-this-fresh-break.}}

He bit his tongue, and cursed himself at this fresh break.

\hypertarget{in-it-there-was-something-that-was-almost-tragedy.}{%
\subsection{In it there was something that was almost
tragedy.}\label{in-it-there-was-something-that-was-almost-tragedy.}}

In it there was something that was almost tragedy.

\hypertarget{your-face-is-red-with-blood.}{%
\subsection{Your face is red with
blood.}\label{your-face-is-red-with-blood.}}

Your face is red with blood.

\hypertarget{her-eyes-smiled-truth-at-him-as-he-came-up-the-bank.}{%
\subsection{Her eyes smiled truth at him as he came up the
bank.}\label{her-eyes-smiled-truth-at-him-as-he-came-up-the-bank.}}

Her eyes smiled truth at him as he came up the bank.

\hypertarget{he-can-care-for-himself.}{%
\subsection{He can care for himself.}\label{he-can-care-for-himself.}}

He can care for himself.

\hypertarget{they-will-search-for-us-between-their-camp-and-churchill.}{%
\subsection{They will search for us between their camp and
Churchill.}\label{they-will-search-for-us-between-their-camp-and-churchill.}}

They will search for us between their camp and Churchill.

\hypertarget{until-i-die-he-exclaimed.}{%
\subsection{Until I die, he
exclaimed.}\label{until-i-die-he-exclaimed.}}

Until I die, he exclaimed.

\hypertarget{her-beautiful-hair-was-done-up-in-shining-coils.}{%
\subsection{Her beautiful hair was done up in shining
coils.}\label{her-beautiful-hair-was-done-up-in-shining-coils.}}

Her beautiful hair was done up in shining coils.

\hypertarget{the-churchill-narrowed-and-its-current-became-swifter-as-they-progressed.}{%
\subsection{The Churchill narrowed and its current became swifter as
they
progressed.}\label{the-churchill-narrowed-and-its-current-became-swifter-as-they-progressed.}}

The Churchill narrowed and its current became swifter as they
progressed.

\hypertarget{for-a-full-half-minute-jeanne-looked-at-him-without-speaking.}{%
\subsection{For a full half minute Jeanne looked at him without
speaking.}\label{for-a-full-half-minute-jeanne-looked-at-him-without-speaking.}}

For a full half minute Jeanne looked at him without speaking.

\hypertarget{i-want-to-die-in-it.}{%
\subsection{I want to die in it.}\label{i-want-to-die-in-it.}}

I want to die in it.

\hypertarget{darkness-hid-him-from-jeanne.}{%
\subsection{Darkness hid him from
Jeanne.}\label{darkness-hid-him-from-jeanne.}}

Darkness hid him from Jeanne.

\hypertarget{and-yet-if-she-came-he-had-no-words-to-say.}{%
\subsection{And yet if she came he had no words to
say.}\label{and-yet-if-she-came-he-had-no-words-to-say.}}

And yet if she came he had no words to say.

\hypertarget{he-heard-a-sound-which-brought-him-quickly-into-consciousness-of-day.}{%
\subsection{He heard a sound which brought him quickly into
consciousness of
day.}\label{he-heard-a-sound-which-brought-him-quickly-into-consciousness-of-day.}}

He heard a sound which brought him quickly into consciousness of day.

\hypertarget{within-himself-he-called-it-no-longer-his-own.}{%
\subsection{Within himself he called it no longer his
own.}\label{within-himself-he-called-it-no-longer-his-own.}}

Within himself he called it no longer his own.

\hypertarget{besides-that-noise-makes-me-deaf.}{%
\subsection{Besides, that noise makes me
deaf.}\label{besides-that-noise-makes-me-deaf.}}

Besides, that noise makes me deaf.

\hypertarget{philip-looked-back-from-the-crest-and-saw-jeanne-leaning-over-the-canoe.}{%
\subsection{Philip looked back from the crest and saw Jeanne leaning
over the
canoe.}\label{philip-looked-back-from-the-crest-and-saw-jeanne-leaning-over-the-canoe.}}

Philip looked back from the crest and saw Jeanne leaning over the canoe.

\hypertarget{fifty-yards-ahead-of-her-were-the-first-of-the-rocks.}{%
\subsection{Fifty yards ahead of her were the first of the
rocks.}\label{fifty-yards-ahead-of-her-were-the-first-of-the-rocks.}}

Fifty yards ahead of her were the first of the rocks.

\hypertarget{there-was-one-chance-and-only-one-of-saving-jeanne.}{%
\subsection{There was one chance, and only one, of saving
Jeanne.}\label{there-was-one-chance-and-only-one-of-saving-jeanne.}}

There was one chance, and only one, of saving Jeanne.

\hypertarget{youre-a-devil-for-fighting-and-will-surely-win.}{%
\subsection{You're a devil for fighting, and will surely
win.}\label{youre-a-devil-for-fighting-and-will-surely-win.}}

You're a devil for fighting, and will surely win.

\hypertarget{ill-only-be-in-the-way.}{%
\subsection{I'll only be in the way.}\label{ill-only-be-in-the-way.}}

I'll only be in the way.

\hypertarget{he-lifted-his-eyes-and-a-strange-cry-burst-from-his-lips.}{%
\subsection{He lifted his eyes, and a strange cry burst from his
lips.}\label{he-lifted-his-eyes-and-a-strange-cry-burst-from-his-lips.}}

He lifted his eyes, and a strange cry burst from his lips.

\hypertarget{shooting-pains-passed-like-flashes-of-electricity-through-his-body.}{%
\subsection{Shooting pains passed like flashes of electricity through
his
body.}\label{shooting-pains-passed-like-flashes-of-electricity-through-his-body.}}

Shooting pains passed like flashes of electricity through his body.

\hypertarget{i-know-that-you-are-in-charge-there-and-jeanne-knows.}{%
\subsection{I know that you are in charge there, and Jeanne
knows.}\label{i-know-that-you-are-in-charge-there-and-jeanne-knows.}}

I know that you are in charge there, and Jeanne knows.

\hypertarget{for-a-full-minute-the-two-men-stared-into-each-others-face.}{%
\subsection{For a full minute the two men stared into each other's
face.}\label{for-a-full-minute-the-two-men-stared-into-each-others-face.}}

For a full minute the two men stared into each other's face.

\hypertarget{he-was-sure-now-of-but-few-things.}{%
\subsection{He was sure, now, of but few
things.}\label{he-was-sure-now-of-but-few-things.}}

He was sure, now, of but few things.

\hypertarget{it-was-a-miracle-and-i-owe-you-my-life.}{%
\subsection{It was a miracle, and I owe you my
life.}\label{it-was-a-miracle-and-i-owe-you-my-life.}}

It was a miracle, and I owe you my life.

\hypertarget{philip-ate-lightly-of-the-food-which-pierre-had-ready-for-him.}{%
\subsection{Philip ate lightly of the food which Pierre had ready for
him.}\label{philip-ate-lightly-of-the-food-which-pierre-had-ready-for-him.}}

Philip ate lightly of the food which Pierre had ready for him.

\hypertarget{such-men-believe-when-they-come-together.}{%
\subsection{Such men believe, when they come
together.}\label{such-men-believe-when-they-come-together.}}

Such men believe, when they come together.

\hypertarget{the-journey-was-continued-at-dawn.}{%
\subsection{The journey was continued at
dawn.}\label{the-journey-was-continued-at-dawn.}}

The journey was continued at dawn.

\hypertarget{jeanne-and-pierre-both-gazed-toward-the-great-rock.}{%
\subsection{Jeanne and Pierre both gazed toward the great
rock.}\label{jeanne-and-pierre-both-gazed-toward-the-great-rock.}}

Jeanne and Pierre both gazed toward the great rock.

\hypertarget{there-was-something-pathetic-in-the-girls-attitude-now.}{%
\subsection{There was something pathetic in the girl's attitude
now.}\label{there-was-something-pathetic-in-the-girls-attitude-now.}}

There was something pathetic in the girl's attitude now.

\hypertarget{he-moved-his-position-and-the-illusion-was-gone.}{%
\subsection{He moved his position, and the illusion was
gone.}\label{he-moved-his-position-and-the-illusion-was-gone.}}

He moved his position, and the illusion was gone.

\hypertarget{for-two-hours-not-a-word-passed-between-them.}{%
\subsection{For two hours not a word passed between
them.}\label{for-two-hours-not-a-word-passed-between-them.}}

For two hours not a word passed between them.

\hypertarget{i-have-hunted-along-this-ridge-replied-philip.}{%
\subsection{I have hunted along this ridge, replied
Philip.}\label{i-have-hunted-along-this-ridge-replied-philip.}}

I have hunted along this ridge, replied Philip.

\hypertarget{thats-thorpes-said-the-young-engineer.}{%
\subsection{That's Thorpe's, said the young
engineer.}\label{thats-thorpes-said-the-young-engineer.}}

That's Thorpe's, said the young engineer.

\hypertarget{we-saw-your-light-and-thought-you-wouldnt-mind-a-call.}{%
\subsection{We saw your light, and thought you wouldn't mind a
call.}\label{we-saw-your-light-and-thought-you-wouldnt-mind-a-call.}}

We saw your light, and thought you wouldn't mind a call.

\hypertarget{billinger-may-arrive-in-time.}{%
\subsection{Billinger may arrive in
time.}\label{billinger-may-arrive-in-time.}}

Billinger may arrive in time.

\hypertarget{theres-the-hitch-replied-thorpe-rolling-a-cigarette.}{%
\subsection{There's the hitch, replied Thorpe, rolling a
cigarette.}\label{theres-the-hitch-replied-thorpe-rolling-a-cigarette.}}

There's the hitch, replied Thorpe, rolling a cigarette.

\hypertarget{i-want-my-men-to-work-by-themselves.}{%
\subsection{I want my men to work by
themselves.}\label{i-want-my-men-to-work-by-themselves.}}

I want my men to work by themselves.

\hypertarget{philip-saw-macdougall-soon-after-his-short-talk-with-thorpe.}{%
\subsection{Philip saw MacDougall soon after his short talk with
Thorpe.}\label{philip-saw-macdougall-soon-after-his-short-talk-with-thorpe.}}

Philip saw MacDougall soon after his short talk with Thorpe.

\hypertarget{neither-could-they-understand-the-growing-disaffection-among-thorpes-men.}{%
\subsection{Neither could they understand the growing disaffection among
Thorpe's
men.}\label{neither-could-they-understand-the-growing-disaffection-among-thorpes-men.}}

Neither could they understand the growing disaffection among Thorpe's
men.

\hypertarget{two-weeks-passed-and-in-that-time-thorpe-left-camp-three-times.}{%
\subsection{Two weeks passed, and in that time Thorpe left camp three
times.}\label{two-weeks-passed-and-in-that-time-thorpe-left-camp-three-times.}}

Two weeks passed, and in that time Thorpe left camp three times.

\hypertarget{it-was-the-third-or-fourth-time-that-philip-had-heard-macdougall-swear.}{%
\subsection{It was the third or fourth time that Philip had heard
MacDougall
swear.}\label{it-was-the-third-or-fourth-time-that-philip-had-heard-macdougall-swear.}}

It was the third or fourth time that Philip had heard MacDougall swear.

\hypertarget{blood-was-oozing-slowly-from-the-wounded-mans-right-breast.}{%
\subsection{Blood was oozing slowly from the wounded man's right
breast.}\label{blood-was-oozing-slowly-from-the-wounded-mans-right-breast.}}

Blood was oozing slowly from the wounded man's right breast.

\hypertarget{he-destroyed-everything-that-had-belonged-to-the-woman.}{%
\subsection{He destroyed everything that had belonged to the
woman.}\label{he-destroyed-everything-that-had-belonged-to-the-woman.}}

He destroyed everything that had belonged to the woman.

\hypertarget{philip-bent-low-over-pierre.}{%
\subsection{Philip bent low over
Pierre.}\label{philip-bent-low-over-pierre.}}

Philip bent low over Pierre.

\hypertarget{did-thorpe-go-to-see-any-one-in-churchill.}{%
\subsection{Did Thorpe go to see any one in
Churchill.}\label{did-thorpe-go-to-see-any-one-in-churchill.}}

Did Thorpe go to see any one in Churchill.

\hypertarget{she-saw-the-answer-in-his-face.}{%
\subsection{She saw the answer in his
face.}\label{she-saw-the-answer-in-his-face.}}

She saw the answer in his face.

\hypertarget{thorpe-and-his-men-were-to-destroy-this-camp-and-kill-you.}{%
\subsection{Thorpe and his men were to destroy this camp, and kill
you.}\label{thorpe-and-his-men-were-to-destroy-this-camp-and-kill-you.}}

Thorpe and his men were to destroy this camp, and kill you.

\hypertarget{there-is-no-need-of-further-detail-now-for-you-can-understand.}{%
\subsection{There is no need of further detail, now -- for you can
understand.}\label{there-is-no-need-of-further-detail-now-for-you-can-understand.}}

There is no need of further detail, now -- for you can understand.

\hypertarget{there-followed-a-roar-that-shook-the-earth.}{%
\subsection{There followed a roar that shook the
earth.}\label{there-followed-a-roar-that-shook-the-earth.}}

There followed a roar that shook the earth.

\hypertarget{blind-with-rage-he-darted-in.}{%
\subsection{Blind with rage, he darted
in.}\label{blind-with-rage-he-darted-in.}}

Blind with rage, he darted in.

\hypertarget{in-it-was-the-joy-of-life.}{%
\subsection{In it was the joy of
life.}\label{in-it-was-the-joy-of-life.}}

In it was the joy of life.

\hypertarget{swiftly-his-eyes-measured-the-situation.}{%
\subsection{Swiftly his eyes measured the
situation.}\label{swiftly-his-eyes-measured-the-situation.}}

Swiftly his eyes measured the situation.

\hypertarget{but-this-little-defect-did-not-worry-him.}{%
\subsection{But this little defect did not worry
him.}\label{but-this-little-defect-did-not-worry-him.}}

But this little defect did not worry him.

\hypertarget{and-then-steadily-he-began-to-chew.}{%
\subsection{And then, steadily, he began to
chew.}\label{and-then-steadily-he-began-to-chew.}}

And then, steadily, he began to chew.

\hypertarget{together-they-ate-the-rabbit.}{%
\subsection{Together they ate the
rabbit.}\label{together-they-ate-the-rabbit.}}

Together they ate the rabbit.

\hypertarget{they-edged-nearer-and-stood-shoulder-to-shoulder-facing-their-world.}{%
\subsection{They edged nearer, and stood shoulder to shoulder facing
their
world.}\label{they-edged-nearer-and-stood-shoulder-to-shoulder-facing-their-world.}}

They edged nearer, and stood shoulder to shoulder facing their world.

\hypertarget{it-was-beating-and-waiting-in-the-ambush-of-those-black-pits.}{%
\subsection{It was beating and waiting in the ambush of those black
pits.}\label{it-was-beating-and-waiting-in-the-ambush-of-those-black-pits.}}

It was beating and waiting in the ambush of those black pits.

\hypertarget{something-vastly-more-thrilling-had-come-into-it-now.}{%
\subsection{Something vastly more thrilling had come into it
now.}\label{something-vastly-more-thrilling-had-come-into-it-now.}}

Something vastly more thrilling had come into it now.

\hypertarget{it-took-him-half-an-hour-to-reach-the-edge-of-it.}{%
\subsection{It took him half an hour to reach the edge of
it.}\label{it-took-him-half-an-hour-to-reach-the-edge-of-it.}}

It took him half an hour to reach the edge of it.

\hypertarget{but-there-was-no-longer-the-mother-yearning-in-his-heart.}{%
\subsection{But there was no longer the mother yearning in his
heart.}\label{but-there-was-no-longer-the-mother-yearning-in-his-heart.}}

But there was no longer the mother yearning in his heart.

\hypertarget{besides-had-he-not-whipped-the-big-owl-in-the-forest.}{%
\subsection{Besides, had he not whipped the big owl in the
forest.}\label{besides-had-he-not-whipped-the-big-owl-in-the-forest.}}

Besides, had he not whipped the big owl in the forest.

\hypertarget{after-all-it-was-simply-a-mistake-in-judgment.}{%
\subsection{After all, it was simply a mistake in
judgment.}\label{after-all-it-was-simply-a-mistake-in-judgment.}}

After all, it was simply a mistake in judgment.

\hypertarget{had-it-struck-squarely-it-would-have-killed-him.}{%
\subsection{Had it struck squarely it would have killed
him.}\label{had-it-struck-squarely-it-would-have-killed-him.}}

Had it struck squarely it would have killed him.

\hypertarget{the-indian-even-poked-his-stick-into-the-thick-ground-spruce.}{%
\subsection{The Indian even poked his stick into the thick ground
spruce.}\label{the-indian-even-poked-his-stick-into-the-thick-ground-spruce.}}

The Indian even poked his stick into the thick ground spruce.

\hypertarget{pebbles-and-dirt-flew-along-with-hair-and-fur.}{%
\subsection{Pebbles and dirt flew along with hair and
fur.}\label{pebbles-and-dirt-flew-along-with-hair-and-fur.}}

Pebbles and dirt flew along with hair and fur.

\hypertarget{and-he-was-filled-with-a-strange-and-foreboding-fear.}{%
\subsection{And he was filled with a strange and foreboding
fear.}\label{and-he-was-filled-with-a-strange-and-foreboding-fear.}}

And he was filled with a strange and foreboding fear.

\hypertarget{it-was-steel-a-fisher-trap.}{%
\subsection{It was steel, a fisher
trap.}\label{it-was-steel-a-fisher-trap.}}

It was steel, a fisher trap.

\hypertarget{ow-a-wild-dog-he-growled.}{%
\subsection{OW, a wild dog, he
growled.}\label{ow-a-wild-dog-he-growled.}}

OW, a wild dog, he growled.

\hypertarget{he-was-a-pariah-a-wanderer-without-a-friend-or-a-home.}{%
\subsection{He was a pariah; a wanderer without a friend or a
home.}\label{he-was-a-pariah-a-wanderer-without-a-friend-or-a-home.}}

He was a pariah; a wanderer without a friend or a home.

\hypertarget{that-is-the-strange-part-of-it.}{%
\subsection{That is the strange part of
it.}\label{that-is-the-strange-part-of-it.}}

That is the strange part of it.

\hypertarget{his-freshly-caught-furs-he-flung-to-the-floor.}{%
\subsection{His freshly caught furs he flung to the
floor.}\label{his-freshly-caught-furs-he-flung-to-the-floor.}}

His freshly caught furs he flung to the floor.

\hypertarget{for-that-reason-le-beau-had-chosen-him-to-fight-the-big-fight.}{%
\subsection{For that reason Le Beau had chosen him to fight the big
fight.}\label{for-that-reason-le-beau-had-chosen-him-to-fight-the-big-fight.}}

For that reason Le Beau had chosen him to fight the big fight.

\hypertarget{in-the-crib-the-baby-sat-up-and-began-to-prattle.}{%
\subsection{In the crib the baby sat up and began to
prattle.}\label{in-the-crib-the-baby-sat-up-and-began-to-prattle.}}

In the crib the baby sat up and began to prattle.

\hypertarget{she-obeyed-shrinking-back-with-the-baby-in-her-arms.}{%
\subsection{She obeyed, shrinking back with the baby in her
arms.}\label{she-obeyed-shrinking-back-with-the-baby-in-her-arms.}}

She obeyed, shrinking back with the baby in her arms.

\hypertarget{his-teeth-shut-with-a-last-click.}{%
\subsection{His teeth shut with a last
click.}\label{his-teeth-shut-with-a-last-click.}}

His teeth shut with a last click.

\hypertarget{it-was-over-when-he-made-his-way-through-the-ring-of-spectators.}{%
\subsection{It was over when he made his way through the ring of
spectators.}\label{it-was-over-when-he-made-his-way-through-the-ring-of-spectators.}}

It was over when he made his way through the ring of spectators.

\hypertarget{in-a-flash-he-was-on-his-feet-facing-him.}{%
\subsection{In a flash he was on his feet, facing
him.}\label{in-a-flash-he-was-on-his-feet-facing-him.}}

In a flash he was on his feet, facing him.

\hypertarget{he-thought-he-saw-a-shudder-pass-through-the-factors-shoulders.}{%
\subsection{He thought he saw a shudder pass through the Factor's
shoulders.}\label{he-thought-he-saw-a-shudder-pass-through-the-factors-shoulders.}}

He thought he saw a shudder pass through the Factor's shoulders.

\hypertarget{the-moon-had-already-begun-its-westward-decline.}{%
\subsection{The moon had already begun its westward
decline.}\label{the-moon-had-already-begun-its-westward-decline.}}

The moon had already begun its westward decline.

\hypertarget{they-laughed-like-two-happy-children.}{%
\subsection{They laughed like two happy
children.}\label{they-laughed-like-two-happy-children.}}

They laughed like two happy children.

\hypertarget{he-pulled-and-the-log-crashed-down-to-break-his-back.}{%
\subsection{He pulled, and the log crashed down to break his
back.}\label{he-pulled-and-the-log-crashed-down-to-break-his-back.}}

He pulled, and the log crashed down to break his back.

\hypertarget{fast-but-endure.}{%
\subsection{Fast, but endure.}\label{fast-but-endure.}}

Fast, but endure.

\hypertarget{a-little-before-dawn-of-the-day-following-the-fire-relief-came.}{%
\subsection{A little before dawn of the day following, the fire relief
came.}\label{a-little-before-dawn-of-the-day-following-the-fire-relief-came.}}

A little before dawn of the day following, the fire relief came.

\hypertarget{the-indian-felt-the-worship-of-her-warm-in-his-heart.}{%
\subsection{The Indian felt the worship of her warm in his
heart.}\label{the-indian-felt-the-worship-of-her-warm-in-his-heart.}}

The Indian felt the worship of her warm in his heart.

\hypertarget{he-drew-in-a-deep-breath-as-he-looked-at-them.}{%
\subsection{He drew in a deep breath as he looked at
them.}\label{he-drew-in-a-deep-breath-as-he-looked-at-them.}}

He drew in a deep breath as he looked at them.

\hypertarget{then-he-shouted-shut-up.}{%
\subsection{Then he shouted, Shut up.}\label{then-he-shouted-shut-up.}}

Then he shouted, Shut up.

\hypertarget{he-changed-his-seat-for-a-steamer-reclining-chair.}{%
\subsection{He changed his seat for a steamer reclining
chair.}\label{he-changed-his-seat-for-a-steamer-reclining-chair.}}

He changed his seat for a steamer reclining chair.

\hypertarget{on-the-far-corner-of-the-compound-fence-a-hawk-brooded.}{%
\subsection{On the far corner of the compound fence a hawk
brooded.}\label{on-the-far-corner-of-the-compound-fence-a-hawk-brooded.}}

On the far corner of the compound fence a hawk brooded.

\hypertarget{to-these-he-gave-castor-oil.}{%
\subsection{To these he gave castor
oil.}\label{to-these-he-gave-castor-oil.}}

To these he gave castor oil.

\hypertarget{hatred-and-murder-and-lust-for-revenge-they-possessed-to-overflowing.}{%
\subsection{Hatred and murder and lust for revenge they possessed to
overflowing.}\label{hatred-and-murder-and-lust-for-revenge-they-possessed-to-overflowing.}}

Hatred and murder and lust for revenge they possessed to overflowing.

\hypertarget{sheldon-glanced-at-the-thermometer.}{%
\subsection{Sheldon glanced at the
thermometer.}\label{sheldon-glanced-at-the-thermometer.}}

Sheldon glanced at the thermometer.

\hypertarget{ill-see-to-poor-hughie.}{%
\subsection{I'll see to poor Hughie.}\label{ill-see-to-poor-hughie.}}

I'll see to poor Hughie.

\hypertarget{her-gray-eyes-were-flashing-and-her-lips-were-quivering.}{%
\subsection{Her gray eyes were flashing, and her lips were
quivering.}\label{her-gray-eyes-were-flashing-and-her-lips-were-quivering.}}

Her gray eyes were flashing, and her lips were quivering.

\hypertarget{also-i-want-information.}{%
\subsection{Also, I want information.}\label{also-i-want-information.}}

Also, I want information.

\hypertarget{let-them-go-out-and-eat-with-my-boys.}{%
\subsection{Let them go out and eat with my
boys.}\label{let-them-go-out-and-eat-with-my-boys.}}

Let them go out and eat with my boys.

\hypertarget{i-i-beg-pardon-he-drawled.}{%
\subsection{I, I beg pardon, he
drawled.}\label{i-i-beg-pardon-he-drawled.}}

I, I beg pardon, he drawled.

\hypertarget{and-you-preferred-a-cannibal-isle-and-a-cartridge-belt.}{%
\subsection{And you preferred a cannibal isle and a cartridge
belt.}\label{and-you-preferred-a-cannibal-isle-and-a-cartridge-belt.}}

And you preferred a cannibal isle and a cartridge belt.

\hypertarget{i-was-in-new-york-when-the-crash-came.}{%
\subsection{I was in New York when the crash
came.}\label{i-was-in-new-york-when-the-crash-came.}}

I was in New York when the crash came.

\hypertarget{no-i-did-not-fall-among-thieves.}{%
\subsection{No, I did not fall among
thieves.}\label{no-i-did-not-fall-among-thieves.}}

No, I did not fall among thieves.

\hypertarget{such-things-in-her-brain-were-like-so-many-oaths-on-her-lips.}{%
\subsection{Such things in her brain were like so many oaths on her
lips.}\label{such-things-in-her-brain-were-like-so-many-oaths-on-her-lips.}}

Such things in her brain were like so many oaths on her lips.

\hypertarget{your-being-wrecked-here-has-been-a-godsend-to-me.}{%
\subsection{Your being wrecked here has been a godsend to
me.}\label{your-being-wrecked-here-has-been-a-godsend-to-me.}}

Your being wrecked here has been a godsend to me.

\hypertarget{i-cant-go-elsewhere-by-your-own-account.}{%
\subsection{I can't go elsewhere, by your own
account.}\label{i-cant-go-elsewhere-by-your-own-account.}}

I can't go elsewhere, by your own account.

\hypertarget{her-achievements-with-cocoanuts-were-a-revelation.}{%
\subsection{Her achievements with cocoanuts were a
revelation.}\label{her-achievements-with-cocoanuts-were-a-revelation.}}

Her achievements with cocoanuts were a revelation.

\hypertarget{he-glanced-down-at-her-helplessly-and-moistened-his-lips.}{%
\subsection{He glanced down at her helplessly, and moistened his
lips.}\label{he-glanced-down-at-her-helplessly-and-moistened-his-lips.}}

He glanced down at her helplessly, and moistened his lips.

\hypertarget{that-is-what-distinguishes-all-of-us-from-the-lower-animals.}{%
\subsection{That is what distinguishes all of us from the lower
animals.}\label{that-is-what-distinguishes-all-of-us-from-the-lower-animals.}}

That is what distinguishes all of us from the lower animals.

\hypertarget{idealism-led-him-to-philosophic-anarchy-and-his-family-threw-him-off.}{%
\subsection{Idealism led him to philosophic anarchy, and his family
threw him
off.}\label{idealism-led-him-to-philosophic-anarchy-and-his-family-threw-him-off.}}

Idealism led him to philosophic anarchy, and his family threw him off.

\hypertarget{he-also-contended-that-better-confidence-was-established-by-carrying-no-weapons.}{%
\subsection{He also contended that better confidence was established by
carrying no
weapons.}\label{he-also-contended-that-better-confidence-was-established-by-carrying-no-weapons.}}

He also contended that better confidence was established by carrying no
weapons.

\hypertarget{outsiders-are-allowed-five-minute-speeches-the-sick-man-urged.}{%
\subsection{Outsiders are allowed five minute speeches, the sick man
urged.}\label{outsiders-are-allowed-five-minute-speeches-the-sick-man-urged.}}

Outsiders are allowed five minute speeches, the sick man urged.

\hypertarget{so-was-packards-finish-suicide.}{%
\subsection{So was Packard's finish
suicide.}\label{so-was-packards-finish-suicide.}}

So was Packard's finish suicide.

\hypertarget{joan-cried-with-shining-eyes.}{%
\subsection{Joan cried, with shining
eyes.}\label{joan-cried-with-shining-eyes.}}

Joan cried, with shining eyes.

\hypertarget{nobody-knows-how-the-natives-got-them.}{%
\subsection{Nobody knows how the natives got
them.}\label{nobody-knows-how-the-natives-got-them.}}

Nobody knows how the natives got them.

\hypertarget{how-can-you-manage-all-alone-mr-young.}{%
\subsection{How can you manage all alone, Mr
Young.}\label{how-can-you-manage-all-alone-mr-young.}}

How can you manage all alone, Mr Young.

\hypertarget{the-planters-are-already-considering-the-matter.}{%
\subsection{The planters are already considering the
matter.}\label{the-planters-are-already-considering-the-matter.}}

The planters are already considering the matter.

\hypertarget{i-use-great-trouble-advisedly.}{%
\subsection{I use great trouble
advisedly.}\label{i-use-great-trouble-advisedly.}}

I use great trouble advisedly.

\hypertarget{dear-sir-your-second-victim-has-fallen-on-schedule-time.}{%
\subsection{Dear Sir, Your second victim has fallen on schedule
time.}\label{dear-sir-your-second-victim-has-fallen-on-schedule-time.}}

Dear Sir, Your second victim has fallen on schedule time.

\hypertarget{we-leave-the-eventuality-to-time-and-law.}{%
\subsection{We leave the eventuality to time and
law.}\label{we-leave-the-eventuality-to-time-and-law.}}

We leave the eventuality to time and law.

\hypertarget{i-also-understand-that-similar-branch-organizations-have-made-their-appearance-in-europe.}{%
\subsection{I also understand that similar branch organizations have
made their appearance in
Europe.}\label{i-also-understand-that-similar-branch-organizations-have-made-their-appearance-in-europe.}}

I also understand that similar branch organizations have made their
appearance in Europe.

\hypertarget{society-is-shaken-to-its-foundations.}{%
\subsection{Society is shaken to its
foundations.}\label{society-is-shaken-to-its-foundations.}}

Society is shaken to its foundations.

\hypertarget{a-month-in-australia-would-finish-me.}{%
\subsection{A month in Australia would finish
me.}\label{a-month-in-australia-would-finish-me.}}

A month in Australia would finish me.

\hypertarget{down-through-the-perfume-weighted-air-fluttered-the-snowy-fluffs-of-the-cottonwoods.}{%
\subsection{Down through the perfume weighted air fluttered the snowy
fluffs of the
cottonwoods.}\label{down-through-the-perfume-weighted-air-fluttered-the-snowy-fluffs-of-the-cottonwoods.}}

Down through the perfume weighted air fluttered the snowy fluffs of the
cottonwoods.

\hypertarget{you-were-destroying-my-life.}{%
\subsection{You were destroying my
life.}\label{you-were-destroying-my-life.}}

You were destroying my life.

\hypertarget{horses-and-rifles-had-been-her-toys-camp-and-trail-her-nursery.}{%
\subsection{Horses and rifles had been her toys, camp and trail her
nursery.}\label{horses-and-rifles-had-been-her-toys-camp-and-trail-her-nursery.}}

Horses and rifles had been her toys, camp and trail her nursery.

\hypertarget{im-as-good-as-a-man-she-urged.}{%
\subsection{I'm as good as a man, she
urged.}\label{im-as-good-as-a-man-she-urged.}}

I'm as good as a man, she urged.

\hypertarget{you-read-the-quotations-in-todays-paper.}{%
\subsection{You read the quotations in today's
paper.}\label{you-read-the-quotations-in-todays-paper.}}

You read the quotations in today's paper.

\hypertarget{hes-terribly-touchy-about-his-black-wards-as-he-calls-them.}{%
\subsection{He's terribly touchy about his black wards, as he calls
them.}\label{hes-terribly-touchy-about-his-black-wards-as-he-calls-them.}}

He's terribly touchy about his black wards, as he calls them.

\hypertarget{whatever-he-guessed-he-locked-away-in-the-taboo-room-of-naomi.}{%
\subsection{Whatever he guessed he locked away in the taboo room of
Naomi.}\label{whatever-he-guessed-he-locked-away-in-the-taboo-room-of-naomi.}}

Whatever he guessed he locked away in the taboo room of Naomi.

\hypertarget{this-is-eighteen-eighty.}{%
\subsection{This is eighteen eighty.}\label{this-is-eighteen-eighty.}}

This is eighteen eighty.

\hypertarget{death-is-and-has-been-ever-since-old-maui-died.}{%
\subsection{Death is and has been ever since old Maui
died.}\label{death-is-and-has-been-ever-since-old-maui-died.}}

Death is and has been ever since old Maui died.

\hypertarget{some-boy-she-laughed-acquiescence.}{%
\subsection{Some boy, she laughed
acquiescence.}\label{some-boy-she-laughed-acquiescence.}}

Some boy, she laughed acquiescence.

\hypertarget{let-us-talk-it-over-and-find-a-way-out.}{%
\subsection{Let us talk it over and find a way
out.}\label{let-us-talk-it-over-and-find-a-way-out.}}

Let us talk it over and find a way out.

\hypertarget{it-is-a-good-property-and-worth-more-than-that.}{%
\subsection{It is a good property, and worth more than
that.}\label{it-is-a-good-property-and-worth-more-than-that.}}

It is a good property, and worth more than that.

\hypertarget{i-wish-you-were-more-adaptable-joan-retorted.}{%
\subsection{I wish you were more adaptable, Joan
retorted.}\label{i-wish-you-were-more-adaptable-joan-retorted.}}

I wish you were more adaptable, Joan retorted.

\hypertarget{such-is-my-passage-engaged-on-the-steamer.}{%
\subsection{Such is my passage engaged on the
steamer.}\label{such-is-my-passage-engaged-on-the-steamer.}}

Such is my passage engaged on the steamer.

\hypertarget{the-issue-was-not-in-doubt.}{%
\subsection{The issue was not in
doubt.}\label{the-issue-was-not-in-doubt.}}

The issue was not in doubt.

\hypertarget{well-there-are-better-men-in-hawaii-thats-all.}{%
\subsection{Well, there are better men in Hawaii, that's
all.}\label{well-there-are-better-men-in-hawaii-thats-all.}}

Well, there are better men in Hawaii, that's all.

\hypertarget{harry-bancroft-dave-lied.}{%
\subsection{Harry Bancroft, Dave
lied.}\label{harry-bancroft-dave-lied.}}

Harry Bancroft, Dave lied.

\hypertarget{its-a-yankee-joan-cried.}{%
\subsection{It's a Yankee, Joan cried.}\label{its-a-yankee-joan-cried.}}

It's a Yankee, Joan cried.

\hypertarget{he-was-the-leader-and-tudor-was-his-lieutenant.}{%
\subsection{He was the leader, and Tudor was his
lieutenant.}\label{he-was-the-leader-and-tudor-was-his-lieutenant.}}

He was the leader, and Tudor was his lieutenant.

\hypertarget{they-likewise-are-disinclined-to-being-eaten.}{%
\subsection{They likewise are disinclined to being
eaten.}\label{they-likewise-are-disinclined-to-being-eaten.}}

They likewise are disinclined to being eaten.

\hypertarget{but-to-culture-the-revolution-thus-far-had-exhausted-the-junta.}{%
\subsection{But to culture the Revolution thus far had exhausted the
Junta.}\label{but-to-culture-the-revolution-thus-far-had-exhausted-the-junta.}}

But to culture the Revolution thus far had exhausted the Junta.

\hypertarget{the-president-of-the-united-states-was-his-friend.}{%
\subsection{The President of the United States was his
friend.}\label{the-president-of-the-united-states-was-his-friend.}}

The President of the United States was his friend.

\hypertarget{your-face-was-the-personification-of-duplicity.}{%
\subsection{Your face was the personification of
duplicity.}\label{your-face-was-the-personification-of-duplicity.}}

Your face was the personification of duplicity.

\hypertarget{shorty-turned-to-their-employers.}{%
\subsection{Shorty turned to their
employers.}\label{shorty-turned-to-their-employers.}}

Shorty turned to their employers.

\hypertarget{you-were-engaged.}{%
\subsection{You were engaged.}\label{you-were-engaged.}}

You were engaged.

\hypertarget{i-saw-it-all-myself-and-it-was-splendid.}{%
\subsection{I saw it all myself, and it was
splendid.}\label{i-saw-it-all-myself-and-it-was-splendid.}}

I saw it all myself, and it was splendid.

\hypertarget{now-run-along-and-tell-them-to-hurry.}{%
\subsection{Now run along, and tell them to
hurry.}\label{now-run-along-and-tell-them-to-hurry.}}

Now run along, and tell them to hurry.

\hypertarget{whats-that-grub-thief-got-to-do-with-it.}{%
\subsection{What's that grub-thief got to do with
it.}\label{whats-that-grub-thief-got-to-do-with-it.}}

What's that grub-thief got to do with it.

\hypertarget{it-was-a-superb-picture.}{%
\subsection{It was a superb picture.}\label{it-was-a-superb-picture.}}

It was a superb picture.

\hypertarget{so-she-said-the-irate-skipper-dashed-on.}{%
\subsection{So she said, the irate skipper dashed
on.}\label{so-she-said-the-irate-skipper-dashed-on.}}

So she said, the irate skipper dashed on.

\hypertarget{and-watch-out-for-wet-feet-was-his-parting-advice.}{%
\subsection{And watch out for wet feet, was his parting
advice.}\label{and-watch-out-for-wet-feet-was-his-parting-advice.}}

And watch out for wet feet, was his parting advice.

\hypertarget{raoul-yelled-in-order-to-make-himself-heard.}{%
\subsection{Raoul yelled, in order to make himself
heard.}\label{raoul-yelled-in-order-to-make-himself-heard.}}

Raoul yelled, in order to make himself heard.

\hypertarget{oolong-was-two-hundred-and-fifty-miles-from-the-nearest-land.}{%
\subsection{Oolong was two hundred and fifty miles from the nearest
land.}\label{oolong-was-two-hundred-and-fifty-miles-from-the-nearest-land.}}

Oolong was two hundred and fifty miles from the nearest land.

\hypertarget{they-just-lay-off-in-the-bush-and-plugged-away.}{%
\subsection{They just lay off in the bush and plugged
away.}\label{they-just-lay-off-in-the-bush-and-plugged-away.}}

They just lay off in the bush and plugged away.

\hypertarget{the-very-thought-of-the-effort-to-swim-over-was-nauseating.}{%
\subsection{The very thought of the effort to swim over was
nauseating.}\label{the-very-thought-of-the-effort-to-swim-over-was-nauseating.}}

The very thought of the effort to swim over was nauseating.

\hypertarget{and-there-was-a-dog-that-barked.}{%
\subsection{And there was a dog that
barked.}\label{and-there-was-a-dog-that-barked.}}

And there was a dog that barked.

\hypertarget{there-are-four-all-low-mccoy-answered.}{%
\subsection{There are four, all low, McCoy
answered.}\label{there-are-four-all-low-mccoy-answered.}}

There are four, all low, McCoy answered.

\hypertarget{the-women-they-carried-away-with-them-to-the-big-valley.}{%
\subsection{The women they carried away with them to the Big
Valley.}\label{the-women-they-carried-away-with-them-to-the-big-valley.}}

The women they carried away with them to the Big Valley.

\hypertarget{the-japanese-understood-as-we-could-never-school-ourselves-or-hope-to-understand.}{%
\subsection{The Japanese understood as we could never school ourselves
or hope to
understand.}\label{the-japanese-understood-as-we-could-never-school-ourselves-or-hope-to-understand.}}

The Japanese understood as we could never school ourselves or hope to
understand.

\hypertarget{they-had-been-on-the-same-lay-as-ourselves.}{%
\subsection{They had been on the same lay as
ourselves.}\label{they-had-been-on-the-same-lay-as-ourselves.}}

They had been on the same lay as ourselves.

\hypertarget{you-are-positively-soulless-he-said-savagely.}{%
\subsection{You are positively soulless, he said
savagely.}\label{you-are-positively-soulless-he-said-savagely.}}

You are positively soulless, he said savagely.

\hypertarget{harrison-is-still-my-chauffeur.}{%
\subsection{Harrison is still my
chauffeur.}\label{harrison-is-still-my-chauffeur.}}

Harrison is still my chauffeur.

\hypertarget{the-boy-grew-and-prospered.}{%
\subsection{The boy grew and
prospered.}\label{the-boy-grew-and-prospered.}}

The boy grew and prospered.

\hypertarget{he-wanted-to-give-the-finish-to-this-foe-already-so-far-gone.}{%
\subsection{He wanted to give the finish to this foe already so far
gone.}\label{he-wanted-to-give-the-finish-to-this-foe-already-so-far-gone.}}

He wanted to give the finish to this foe already so far gone.

\hypertarget{exciting-times-are-the-lot-of-the-fish-patrol.}{%
\subsection{Exciting times are the lot of the fish
patrol.}\label{exciting-times-are-the-lot-of-the-fish-patrol.}}

Exciting times are the lot of the fish patrol.

\hypertarget{i-know-they-are-my-oysters.}{%
\subsection{I know they are my
oysters.}\label{i-know-they-are-my-oysters.}}

I know they are my oysters.

\hypertarget{by-this-time-charley-was-as-enraged-as-the-greek.}{%
\subsection{By this time Charley was as enraged as the
Greek.}\label{by-this-time-charley-was-as-enraged-as-the-greek.}}

By this time Charley was as enraged as the Greek.

\hypertarget{they-must-have-been-swept-away-by-the-chaotic-currents.}{%
\subsection{They must have been swept away by the chaotic
currents.}\label{they-must-have-been-swept-away-by-the-chaotic-currents.}}

They must have been swept away by the chaotic currents.

\hypertarget{it-resembled-tea-less-than-lager-beer-resembles-champagne.}{%
\subsection{It resembled tea less than lager beer resembles
champagne.}\label{it-resembled-tea-less-than-lager-beer-resembles-champagne.}}

It resembled tea less than lager beer resembles champagne.

\hypertarget{the-very-opposite-is-true-they-are-discouraged-vagabonds.}{%
\subsection{The very opposite is true; they are discouraged
vagabonds.}\label{the-very-opposite-is-true-they-are-discouraged-vagabonds.}}

The very opposite is true; they are discouraged vagabonds.

\hypertarget{at-the-same-time-spears-and-arrows-began-to-fall-among-the-invaders.}{%
\subsection{At the same time spears and arrows began to fall among the
invaders.}\label{at-the-same-time-spears-and-arrows-began-to-fall-among-the-invaders.}}

At the same time spears and arrows began to fall among the invaders.

\hypertarget{then-again-tudor-had-such-an-irritating-way-about-him.}{%
\subsection{Then, again, Tudor had such an irritating way about
him.}\label{then-again-tudor-had-such-an-irritating-way-about-him.}}

Then, again, Tudor had such an irritating way about him.

\hypertarget{outwardly-he-maintained-a-calm-and-smiling-aspect.}{%
\subsection{Outwardly, he maintained a calm and smiling
aspect.}\label{outwardly-he-maintained-a-calm-and-smiling-aspect.}}

Outwardly, he maintained a calm and smiling aspect.

\hypertarget{tudor-surveyed-him-with-withering-disgust.}{%
\subsection{Tudor surveyed him with withering
disgust.}\label{tudor-surveyed-him-with-withering-disgust.}}

Tudor surveyed him with withering disgust.

\hypertarget{you-fired-me-out-of-your-house-in-short.}{%
\subsection{You fired me out of your house, in
short.}\label{you-fired-me-out-of-your-house-in-short.}}

You fired me out of your house, in short.

\hypertarget{her-mouth-opened-but-instead-of-speaking-she-drew-a-long-sigh.}{%
\subsection{Her mouth opened, but instead of speaking she drew a long
sigh.}\label{her-mouth-opened-but-instead-of-speaking-she-drew-a-long-sigh.}}

Her mouth opened, but instead of speaking she drew a long sigh.

\hypertarget{its-worth-eight-dollars.}{%
\subsection{It's worth eight dollars.}\label{its-worth-eight-dollars.}}

It's worth eight dollars.

\hypertarget{and-he-did-hurt-my-arm.}{%
\subsection{And he did hurt my arm.}\label{and-he-did-hurt-my-arm.}}

And he did hurt my arm.

\hypertarget{saxons-onto-her-job.}{%
\subsection{Saxon's onto her job.}\label{saxons-onto-her-job.}}

Saxon's onto her job.

\hypertarget{only-once-did-i-confide-the-strangeness-of-it-all-to-another.}{%
\subsection{Only once did I confide the strangeness of it all to
another.}\label{only-once-did-i-confide-the-strangeness-of-it-all-to-another.}}

Only once did I confide the strangeness of it all to another.

\hypertarget{but-this-time-it-was-saxon-who-rebelled.}{%
\subsection{But this time it was Saxon who
rebelled.}\label{but-this-time-it-was-saxon-who-rebelled.}}

But this time it was Saxon who rebelled.

\hypertarget{i-was-not-to-cry-out-in-the-face-of-fear.}{%
\subsection{I was not to cry out in the face of
fear.}\label{i-was-not-to-cry-out-in-the-face-of-fear.}}

I was not to cry out in the face of fear.

\hypertarget{and-now-put-yourself-in-my-place-for-a-moment.}{%
\subsection{And now put yourself in my place for a
moment.}\label{and-now-put-yourself-in-my-place-for-a-moment.}}

And now put yourself in my place for a moment.

\hypertarget{the-boy-threw-back-his-head-with-pride.}{%
\subsection{The boy threw back his head with
pride.}\label{the-boy-threw-back-his-head-with-pride.}}

The boy threw back his head with pride.

\hypertarget{saxon-nodded-and-the-boy-frowned.}{%
\subsection{Saxon nodded, and the boy
frowned.}\label{saxon-nodded-and-the-boy-frowned.}}

Saxon nodded, and the boy frowned.

\hypertarget{why-not-like-any-railroad-station-or-ferry-depot.}{%
\subsection{Why not like any railroad station or ferry
depot.}\label{why-not-like-any-railroad-station-or-ferry-depot.}}

Why not like any railroad station or ferry depot.

\hypertarget{we-could-throw-stones-with-our-feet.}{%
\subsection{We could throw stones with our
feet.}\label{we-could-throw-stones-with-our-feet.}}

We could throw stones with our feet.

\hypertarget{it-was-put-together-in-a-casual-helter-skelter-sort-of-way.}{%
\subsection{It was put together in a casual, helter-skelter sort of
way.}\label{it-was-put-together-in-a-casual-helter-skelter-sort-of-way.}}

It was put together in a casual, helter-skelter sort of way.

\hypertarget{these-were-merely-stout-sticks-an-inch-or-so-in-diameter.}{%
\subsection{These were merely stout sticks an inch or so in
diameter.}\label{these-were-merely-stout-sticks-an-inch-or-so-in-diameter.}}

These were merely stout sticks an inch or so in diameter.

\hypertarget{then-it-was-that-a-strange-thing-happened.}{%
\subsection{Then it was that a strange thing
happened.}\label{then-it-was-that-a-strange-thing-happened.}}

Then it was that a strange thing happened.

\hypertarget{from-the-source-of-light-a-harsh-voice-said.}{%
\subsection{From the source of light a harsh voice
said.}\label{from-the-source-of-light-a-harsh-voice-said.}}

From the source of light a harsh voice said.

\hypertarget{but-i-did-not-enjoy-it-long.}{%
\subsection{But I did not enjoy it
long.}\label{but-i-did-not-enjoy-it-long.}}

But I did not enjoy it long.

\hypertarget{we-were-now-good-friends.}{%
\subsection{We were now good friends.}\label{we-were-now-good-friends.}}

We were now good friends.

\hypertarget{two-of-the-folk-were-already-up.}{%
\subsection{Two of the Folk were already
up.}\label{two-of-the-folk-were-already-up.}}

Two of the Folk were already up.

\hypertarget{now-animals-do-not-like-mockery.}{%
\subsection{Now animals do not like
mockery.}\label{now-animals-do-not-like-mockery.}}

Now animals do not like mockery.

\hypertarget{he-gave-one-last-snarl-and-slid-from-view-among-the-trees.}{%
\subsection{He gave one last snarl and slid from view among the
trees.}\label{he-gave-one-last-snarl-and-slid-from-view-among-the-trees.}}

He gave one last snarl and slid from view among the trees.

\hypertarget{again-the-girls-applauded-and-mrs-hall-cried.}{%
\subsection{Again the girls applauded, and Mrs Hall
cried.}\label{again-the-girls-applauded-and-mrs-hall-cried.}}

Again the girls applauded, and Mrs Hall cried.

\hypertarget{just-the-same-id-sooner-be-myself-than-have-book-indigestion.}{%
\subsection{Just the same I'd sooner be myself than have book
indigestion.}\label{just-the-same-id-sooner-be-myself-than-have-book-indigestion.}}

Just the same I'd sooner be myself than have book indigestion.

\hypertarget{some-of-the-smaller-veins-had-doubtless-been-ruptured.}{%
\subsection{Some of the smaller veins had doubtless been
ruptured.}\label{some-of-the-smaller-veins-had-doubtless-been-ruptured.}}

Some of the smaller veins had doubtless been ruptured.

\hypertarget{but-we-were-without-this-momentum.}{%
\subsection{But we were without this
momentum.}\label{but-we-were-without-this-momentum.}}

But we were without this momentum.

\hypertarget{there-was-one-difficulty-however.}{%
\subsection{There was one difficulty,
however.}\label{there-was-one-difficulty-however.}}

There was one difficulty, however.

\hypertarget{the-hyena-proceeded-to-dine.}{%
\subsection{The hyena proceeded to
dine.}\label{the-hyena-proceeded-to-dine.}}

The hyena proceeded to dine.

\hypertarget{the-time-was-considered-auspicious.}{%
\subsection{The time was considered
auspicious.}\label{the-time-was-considered-auspicious.}}

The time was considered auspicious.

\hypertarget{or-have-they-already-devised-one.}{%
\subsection{Or have they already devised
one.}\label{or-have-they-already-devised-one.}}

Or have they already devised one.

\hypertarget{we-would-not-spend-another-such-night.}{%
\subsection{We would not spend another such
night.}\label{we-would-not-spend-another-such-night.}}

We would not spend another such night.

\hypertarget{at-first-his-progress-was-slow-and-erratic.}{%
\subsection{At first his progress was slow and
erratic.}\label{at-first-his-progress-was-slow-and-erratic.}}

At first his progress was slow and erratic.

\hypertarget{he-placed-his-paw-on-one-and-its-movements-were-accelerated.}{%
\subsection{He placed his paw on one, and its movements were
accelerated.}\label{he-placed-his-paw-on-one-and-its-movements-were-accelerated.}}

He placed his paw on one, and its movements were accelerated.

\hypertarget{the-awe-of-man-rushed-over-him-again.}{%
\subsection{The awe of man rushed over him
again.}\label{the-awe-of-man-rushed-over-him-again.}}

The awe of man rushed over him again.

\hypertarget{the-fire-men-wore-animal-skins-around-their-waists-and-across-their-shoulders.}{%
\subsection{The Fire-Men wore animal skins around their waists and
across their
shoulders.}\label{the-fire-men-wore-animal-skins-around-their-waists-and-across-their-shoulders.}}

The Fire-Men wore animal skins around their waists and across their
shoulders.

\hypertarget{between-him-and-all-domestic-animals-there-must-be-no-hostilities.}{%
\subsection{Between him and all domestic animals there must be no
hostilities.}\label{between-him-and-all-domestic-animals-there-must-be-no-hostilities.}}

Between him and all domestic animals there must be no hostilities.

\hypertarget{for-a-much-longer-time-lop-ear-and-i-remained-and-watched.}{%
\subsection{For a much longer time Lop-Ear and I remained and
watched.}\label{for-a-much-longer-time-lop-ear-and-i-remained-and-watched.}}

For a much longer time Lop-Ear and I remained and watched.

\hypertarget{all-right-sir-replied-jock-with-great-regret.}{%
\subsection{All right, Sir, replied Jock with great
regret.}\label{all-right-sir-replied-jock-with-great-regret.}}

All right, Sir, replied Jock with great regret.

\hypertarget{at-times-i-wondered-where-sir-archibald-got-his-style.}{%
\subsection{At times I wondered where Sir Archibald got his
style.}\label{at-times-i-wondered-where-sir-archibald-got-his-style.}}

At times I wondered where Sir Archibald got his style.

\hypertarget{why-should-a-fellow-throw-up-the-sponge-after-the-first-round.}{%
\subsection{Why should a fellow throw up the sponge after the first
round.}\label{why-should-a-fellow-throw-up-the-sponge-after-the-first-round.}}

Why should a fellow throw up the sponge after the first round.

\hypertarget{his-hand-shot-out-and-clutched-crooked-leg-by-the-neck.}{%
\subsection{His hand shot out and clutched Crooked-Leg by the
neck.}\label{his-hand-shot-out-and-clutched-crooked-leg-by-the-neck.}}

His hand shot out and clutched Crooked-Leg by the neck.

\hypertarget{miss-brodies-smile-was-slightly-sarcastic.}{%
\subsection{Miss Brodie's smile was slightly
sarcastic.}\label{miss-brodies-smile-was-slightly-sarcastic.}}

Miss Brodie's smile was slightly sarcastic.

\hypertarget{does-the-old-boy-often-go-off-at-half-cock-that-way.}{%
\subsection{Does the old boy often go off at half-cock that
way.}\label{does-the-old-boy-often-go-off-at-half-cock-that-way.}}

Does the old boy often go off at half-cock that way.

\hypertarget{a-flying-arrow-passed-between-us.}{%
\subsection{A flying arrow passed between
us.}\label{a-flying-arrow-passed-between-us.}}

A flying arrow passed between us.

\hypertarget{i-pulled-suddenly-with-all-my-might.}{%
\subsection{I pulled, suddenly, with all my
might.}\label{i-pulled-suddenly-with-all-my-might.}}

I pulled, suddenly, with all my might.

\hypertarget{here-we-allow-our-solicitors-to-look-after-our-legal-work.}{%
\subsection{Here we allow our solicitors to look after our legal
work.}\label{here-we-allow-our-solicitors-to-look-after-our-legal-work.}}

Here we allow our solicitors to look after our legal work.

\hypertarget{his-previous-wives-had-never-lived-long-enough-to-bear-him-children.}{%
\subsection{His previous wives had never lived long enough to bear him
children.}\label{his-previous-wives-had-never-lived-long-enough-to-bear-him-children.}}

His previous wives had never lived long enough to bear him children.

\hypertarget{it-was-our-river-emerging-like-ourselves-from-the-great-swamp.}{%
\subsection{It was our river emerging like ourselves from the great
swamp.}\label{it-was-our-river-emerging-like-ourselves-from-the-great-swamp.}}

It was our river emerging like ourselves from the great swamp.

\hypertarget{cameron-looked-at-his-hands-with-their-long-sinewy-fingers.}{%
\subsection{Cameron looked at his hands with their long, sinewy
fingers.}\label{cameron-looked-at-his-hands-with-their-long-sinewy-fingers.}}

Cameron looked at his hands with their long, sinewy fingers.

\hypertarget{we-got-few-vegetables-and-fruits-and-became-fish-eaters.}{%
\subsection{We got few vegetables and fruits, and became fish
eaters.}\label{we-got-few-vegetables-and-fruits-and-became-fish-eaters.}}

We got few vegetables and fruits, and became fish eaters.

\hypertarget{we-never-made-another-migration.}{%
\subsection{We never made another
migration.}\label{we-never-made-another-migration.}}

We never made another migration.

\hypertarget{nor-was-elam-harnish-an-exception.}{%
\subsection{Nor was Elam Harnish an
exception.}\label{nor-was-elam-harnish-an-exception.}}

Nor was Elam Harnish an exception.

\hypertarget{a-little-treatment-massage-with-some-help-from-the-doctor.}{%
\subsection{A little treatment, massage, with some help from the
doctor.}\label{a-little-treatment-massage-with-some-help-from-the-doctor.}}

A little treatment, massage, with some help from the doctor.

\hypertarget{the-29th-very-foggy.}{%
\subsection{The 29th very foggy.}\label{the-29th-very-foggy.}}

The 29th very foggy.

\hypertarget{dig-in-youre-sure-good-was-daylights-answer.}{%
\subsection{Dig in; you're sure good, was Daylight's
answer.}\label{dig-in-youre-sure-good-was-daylights-answer.}}

Dig in; you're sure good, was Daylight's answer.

\hypertarget{the-apron-string-loomed-near-and-he-shied-like-an-unbroken-colt.}{%
\subsection{The apron string loomed near and he shied like an unbroken
colt.}\label{the-apron-string-loomed-near-and-he-shied-like-an-unbroken-colt.}}

The apron string loomed near and he shied like an unbroken colt.

\hypertarget{he-had-been-born-with-this-endowment.}{%
\subsection{He had been born with this
endowment.}\label{he-had-been-born-with-this-endowment.}}

He had been born with this endowment.

\hypertarget{and-this-was-their-sole-conversation-throughout-the-meal.}{%
\subsection{And this was their sole conversation throughout the
meal.}\label{and-this-was-their-sole-conversation-throughout-the-meal.}}

And this was their sole conversation throughout the meal.

\hypertarget{though-the-aurora-still-flamed-another-day-had-begun.}{%
\subsection{Though the aurora still flamed, another day had
begun.}\label{though-the-aurora-still-flamed-another-day-had-begun.}}

Though the aurora still flamed, another day had begun.

\hypertarget{he-did-not-believe-in-the-burning-of-daylight-for-such-a-luxury.}{%
\subsection{He did not believe in the burning of daylight for such a
luxury.}\label{he-did-not-believe-in-the-burning-of-daylight-for-such-a-luxury.}}

He did not believe in the burning of daylight for such a luxury.

\hypertarget{again-he-had-done-the-big-thing.}{%
\subsection{Again he had done the big
thing.}\label{again-he-had-done-the-big-thing.}}

Again he had done the big thing.

\hypertarget{daylight-was-tired-profoundly-tired.}{%
\subsection{Daylight was tired, profoundly
tired.}\label{daylight-was-tired-profoundly-tired.}}

Daylight was tired, profoundly tired.

\hypertarget{the-regret-in-his-voice-was-provocative-of-a-second-burst-of-laughter.}{%
\subsection{The regret in his voice was provocative of a second burst of
laughter.}\label{the-regret-in-his-voice-was-provocative-of-a-second-burst-of-laughter.}}

The regret in his voice was provocative of a second burst of laughter.

\hypertarget{instead-he-arrived-on-the-night-of-the-second-day.}{%
\subsection{Instead, he arrived on the night of the second
day.}\label{instead-he-arrived-on-the-night-of-the-second-day.}}

Instead, he arrived on the night of the second day.

\hypertarget{their-supply-of-grub-was-gone.}{%
\subsection{Their supply of grub was
gone.}\label{their-supply-of-grub-was-gone.}}

Their supply of grub was gone.

\hypertarget{crickets-began-to-chirp-and-more-geese-and-ducks-flew-overhead.}{%
\subsection{Crickets began to chirp, and more geese and ducks flew
overhead.}\label{crickets-began-to-chirp-and-more-geese-and-ducks-flew-overhead.}}

Crickets began to chirp, and more geese and ducks flew overhead.

\hypertarget{not-till-the-twentieth-of-may-did-the-river-break.}{%
\subsection{Not till the twentieth of May did the river
break.}\label{not-till-the-twentieth-of-may-did-the-river-break.}}

Not till the twentieth of May did the river break.

\hypertarget{it-was-a-gigantic-inadequacy.}{%
\subsection{It was a gigantic
inadequacy.}\label{it-was-a-gigantic-inadequacy.}}

It was a gigantic inadequacy.

\hypertarget{our-mr-howison-will-call-upon-you-at-your-hotel.}{%
\subsection{Our Mr Howison will call upon you at your
hotel.}\label{our-mr-howison-will-call-upon-you-at-your-hotel.}}

Our Mr Howison will call upon you at your hotel.

\hypertarget{he-had-been-so-easy.}{%
\subsection{He had been so easy.}\label{he-had-been-so-easy.}}

He had been so easy.

\hypertarget{change-chairs-daylight-commanded.}{%
\subsection{Change chairs, Daylight
commanded.}\label{change-chairs-daylight-commanded.}}

Change chairs, Daylight commanded.

\hypertarget{id-sooner-have-my-chips-back.}{%
\subsection{I'd sooner have my chips
back.}\label{id-sooner-have-my-chips-back.}}

I'd sooner have my chips back.

\hypertarget{they-only-had-a-little-thirty-thousand-dollar-fire.}{%
\subsection{They only had a little thirty thousand dollar
fire.}\label{they-only-had-a-little-thirty-thousand-dollar-fire.}}

They only had a little thirty thousand dollar fire.

\hypertarget{his-partners-had-starved-and-died-on-the-stewart.}{%
\subsection{His partners had starved and died on the
Stewart.}\label{his-partners-had-starved-and-died-on-the-stewart.}}

His partners had starved and died on the Stewart.

\hypertarget{as-to-how-she-dressed-he-had-no-ideas-at-all.}{%
\subsection{As to how she dressed, he had no ideas at
all.}\label{as-to-how-she-dressed-he-had-no-ideas-at-all.}}

As to how she dressed, he had no ideas at all.

\hypertarget{it-does-was-her-audacious-answer.}{%
\subsection{It does, was her audacious
answer.}\label{it-does-was-her-audacious-answer.}}

It does, was her audacious answer.

\hypertarget{oh-its-just-a-novel-a-love-story.}{%
\subsection{Oh, it's just a novel, a love
story.}\label{oh-its-just-a-novel-a-love-story.}}

Oh, it's just a novel, a love story.

\hypertarget{whoever-lived-on-the-ranch-did-that.}{%
\subsection{Whoever lived on the ranch did
that.}\label{whoever-lived-on-the-ranch-did-that.}}

Whoever lived on the ranch did that.

\hypertarget{how-old-are-you-mother.}{%
\subsection{How old are you, mother.}\label{how-old-are-you-mother.}}

How old are you, mother.

\hypertarget{here-he-got-a-fresh-thrill.}{%
\subsection{Here he got a fresh
thrill.}\label{here-he-got-a-fresh-thrill.}}

Here he got a fresh thrill.

\hypertarget{it-was-unobtrusive-yet-it-was-there.}{%
\subsection{It was unobtrusive, yet it was
there.}\label{it-was-unobtrusive-yet-it-was-there.}}

It was unobtrusive, yet it was there.

\hypertarget{well-ill-be-plumb-gosh-darned.}{%
\subsection{Well, I'll be plumb gosh
darned.}\label{well-ill-be-plumb-gosh-darned.}}

Well, I'll be plumb gosh darned.

\hypertarget{these-quick-little-joys-of-hers-were-sources-of-joy-to-him.}{%
\subsection{These quick little joys of hers were sources of joy to
him.}\label{these-quick-little-joys-of-hers-were-sources-of-joy-to-him.}}

These quick little joys of hers were sources of joy to him.

\hypertarget{i-play-that-choice-wide-open-to-win.}{%
\subsection{I play that choice wide open to
win.}\label{i-play-that-choice-wide-open-to-win.}}

I play that choice wide open to win.

\hypertarget{each-improvement-makes-the-value-of-everything-else-pump-up.}{%
\subsection{Each improvement makes the value of everything else pump
up.}\label{each-improvement-makes-the-value-of-everything-else-pump-up.}}

Each improvement makes the value of everything else pump up.

\hypertarget{but-how-are-you-going-to-do-it.}{%
\subsection{But how are you going to do
it.}\label{but-how-are-you-going-to-do-it.}}

But how are you going to do it.

\hypertarget{lots-of-men-take-women-buggy-riding.}{%
\subsection{Lots of men take women buggy
riding.}\label{lots-of-men-take-women-buggy-riding.}}

Lots of men take women buggy riding.

\hypertarget{daylight-made-no-answer-and-the-door-closed-behind-him.}{%
\subsection{Daylight made no answer, and the door closed behind
him.}\label{daylight-made-no-answer-and-the-door-closed-behind-him.}}

Daylight made no answer, and the door closed behind him.

\hypertarget{theres-not-an-iota-of-truth-in-it.}{%
\subsection{There's not an iota of truth in
it.}\label{theres-not-an-iota-of-truth-in-it.}}

There's not an iota of truth in it.

\hypertarget{but-ever-his-gaze-returned-to-that-crouched-venus-on-the-piano.}{%
\subsection{But ever his gaze returned to that Crouched Venus on the
piano.}\label{but-ever-his-gaze-returned-to-that-crouched-venus-on-the-piano.}}

But ever his gaze returned to that Crouched Venus on the piano.

\hypertarget{would-you-be-satisfied-with-that-one-hundredth-part-of-me.}{%
\subsection{Would you be satisfied with that one hundredth part of
me.}\label{would-you-be-satisfied-with-that-one-hundredth-part-of-me.}}

Would you be satisfied with that one hundredth part of me.

\hypertarget{in-such-a-tumbling-of-values-was-no-time-to-sell.}{%
\subsection{In such a tumbling of values was no time to
sell.}\label{in-such-a-tumbling-of-values-was-no-time-to-sell.}}

In such a tumbling of values was no time to sell.

\hypertarget{stand-off-butcher-and-baker-and-all-the-rest.}{%
\subsection{Stand off butcher and baker and all the
rest.}\label{stand-off-butcher-and-baker-and-all-the-rest.}}

Stand off butcher and baker and all the rest.

\hypertarget{matthewson-whos-this-bookkeeper-rogers.}{%
\subsection{Matthewson, who's this bookkeeper,
Rogers.}\label{matthewson-whos-this-bookkeeper-rogers.}}

Matthewson, who's this bookkeeper, Rogers.

\hypertarget{now-just-what-do-you-want-to-know.}{%
\subsection{Now just what do you want to
know.}\label{now-just-what-do-you-want-to-know.}}

Now just what do you want to know.

\hypertarget{i-want-to-know-how-all-this-is-possible.}{%
\subsection{I want to know how all this is
possible.}\label{i-want-to-know-how-all-this-is-possible.}}

I want to know how all this is possible.

\hypertarget{its-that-much-junk.}{%
\subsection{It's that much junk.}\label{its-that-much-junk.}}

It's that much junk.

\hypertarget{there-was-proper-division-of-labor-in-the-work-they-individually-performed.}{%
\subsection{There was proper division of labor in the work they
individually
performed.}\label{there-was-proper-division-of-labor-in-the-work-they-individually-performed.}}

There was proper division of labor in the work they individually
performed.

\hypertarget{he-loved-to-play-chinese-lottery.}{%
\subsection{He loved to play Chinese
lottery.}\label{he-loved-to-play-chinese-lottery.}}

He loved to play Chinese lottery.

\hypertarget{the-law-of-club-and-fang}{%
\subsection{The Law of Club and Fang}\label{the-law-of-club-and-fang}}

The Law of Club and Fang

\hypertarget{the-temperature-dropped-to-fifty-below-zero-and-remained-there-the-whole-trip.}{%
\subsection{The temperature dropped to fifty below zero and remained
there the whole
trip.}\label{the-temperature-dropped-to-fifty-below-zero-and-remained-there-the-whole-trip.}}

The temperature dropped to fifty below zero and remained there the whole
trip.

\hypertarget{and-as-never-before-he-was-ready-to-obey.}{%
\subsection{And as never before, he was ready to
obey.}\label{and-as-never-before-he-was-ready-to-obey.}}

And as never before, he was ready to obey.

\hypertarget{this-state-of-mind-comes-of-an-undue-prominence-of-the-ego.}{%
\subsection{This state of mind comes of an undue prominence of the
ego.}\label{this-state-of-mind-comes-of-an-undue-prominence-of-the-ego.}}

This state of mind comes of an undue prominence of the ego.

\hypertarget{there-are-the-canals-of-china-and-the-yang-tse-river.}{%
\subsection{There are the canals of China, and the Yang-tse
River.}\label{there-are-the-canals-of-china-and-the-yang-tse-river.}}

There are the canals of China, and the Yang-tse River.

\hypertarget{we-threaten-to-be-of-the-one-mind-before-the-voyage-is-completed.}{%
\subsection{We threaten to be of the one mind before the voyage is
completed.}\label{we-threaten-to-be-of-the-one-mind-before-the-voyage-is-completed.}}

We threaten to be of the one mind before the voyage is completed.

\hypertarget{she-was-built-primarily-to-sail.}{%
\subsection{She was built primarily to
sail.}\label{she-was-built-primarily-to-sail.}}

She was built primarily to sail.

\hypertarget{in-the-bohemian-club-of-san-francisco-there-are-some-crack-sailors.}{%
\subsection{In the Bohemian Club of San Francisco there are some crack
sailors.}\label{in-the-bohemian-club-of-san-francisco-there-are-some-crack-sailors.}}

In the Bohemian Club of San Francisco there are some crack sailors.

\hypertarget{my-age-in-years-is-twenty-two.}{%
\subsection{My age, in years, is twenty
two.}\label{my-age-in-years-is-twenty-two.}}

My age, in years, is twenty two.

\hypertarget{i-forgot-how-easily-i-had-taught-myself-from-the-printed-page.}{%
\subsection{I forgot how easily I had taught myself from the printed
page.}\label{i-forgot-how-easily-i-had-taught-myself-from-the-printed-page.}}

I forgot how easily I had taught myself from the printed page.

\hypertarget{any-average-young-fellow-can-teach-himself-in-a-week.}{%
\subsection{Any average young fellow can teach himself in a
week.}\label{any-average-young-fellow-can-teach-himself-in-a-week.}}

Any average young fellow can teach himself in a week.

\hypertarget{please-do-not-think-that-i-already-know-it-all.}{%
\subsection{Please do not think that I already know it
all.}\label{please-do-not-think-that-i-already-know-it-all.}}

Please do not think that I already know it all.

\hypertarget{you-see-we-were-teaching-ourselves.}{%
\subsection{You see, we were teaching
ourselves.}\label{you-see-we-were-teaching-ourselves.}}

You see, we were teaching ourselves.

\hypertarget{and-now-behold-the-perversity-of-things.}{%
\subsection{And now behold the perversity of
things.}\label{and-now-behold-the-perversity-of-things.}}

And now behold the perversity of things.

\hypertarget{yield-yourself-to-the-waters-that-are-ripping-and-tearing-at-you.}{%
\subsection{Yield yourself to the waters that are ripping and tearing at
you.}\label{yield-yourself-to-the-waters-that-are-ripping-and-tearing-at-you.}}

Yield yourself to the waters that are ripping and tearing at you.

\hypertarget{mr-mcveigh-told-me-about-him.}{%
\subsection{Mr McVeigh told me about
him.}\label{mr-mcveigh-told-me-about-him.}}

Mr McVeigh told me about him.

\hypertarget{unlike-joshua-he-stood-in-no-need-of-divine-assistance.}{%
\subsection{Unlike Joshua, he stood in no need of divine
assistance.}\label{unlike-joshua-he-stood-in-no-need-of-divine-assistance.}}

Unlike Joshua, he stood in no need of divine assistance.

\hypertarget{to-say-the-least-captain-cook-was-a-rather-thorough-going-empiricist.}{%
\subsection{To say the least, Captain Cook was a rather thorough going
empiricist.}\label{to-say-the-least-captain-cook-was-a-rather-thorough-going-empiricist.}}

To say the least, Captain Cook was a rather thorough going empiricist.

\hypertarget{man-could-not-conquer-them.}{%
\subsection{Man could not conquer
them.}\label{man-could-not-conquer-them.}}

Man could not conquer them.

\hypertarget{thought-i-and-a-worthy-fool-he-proved.}{%
\subsection{Thought I, and a worthy fool he
proved.}\label{thought-i-and-a-worthy-fool-he-proved.}}

Thought I, and a worthy fool he proved.

\hypertarget{a-scarlet-loincloth-completed-his-costume.}{%
\subsection{A scarlet loincloth completed his
costume.}\label{a-scarlet-loincloth-completed-his-costume.}}

A scarlet loincloth completed his costume.

\hypertarget{i-like-to-speculate-upon-the-glorious-future-of-man.}{%
\subsection{I like to speculate upon the glorious future of
man.}\label{i-like-to-speculate-upon-the-glorious-future-of-man.}}

I like to speculate upon the glorious future of man.

\hypertarget{christmas-is-an-easy-problem-compared-with-a-polynesian-giving-feast.}{%
\subsection{Christmas is an easy problem compared with a Polynesian
giving-feast.}\label{christmas-is-an-easy-problem-compared-with-a-polynesian-giving-feast.}}

Christmas is an easy problem compared with a Polynesian giving-feast.

\hypertarget{he-had-peeled-off-his-shirt-and-was-wildly-waving-it.}{%
\subsection{He had peeled off his shirt and was wildly waving
it.}\label{he-had-peeled-off-his-shirt-and-was-wildly-waving-it.}}

He had peeled off his shirt and was wildly waving it.

\hypertarget{and-how-would-we-ever-find-ourselves.}{%
\subsection{And how would we ever find
ourselves.}\label{and-how-would-we-ever-find-ourselves.}}

And how would we ever find ourselves.

\hypertarget{i-defy-any-man-to-get-a-solomon-island-sore-in-california.}{%
\subsection{I defy any man to get a Solomon Island sore in
California.}\label{i-defy-any-man-to-get-a-solomon-island-sore-in-california.}}

I defy any man to get a Solomon Island sore in California.

\hypertarget{a-bush-chief-had-died-a-natural-death.}{%
\subsection{A bush chief had died a natural
death.}\label{a-bush-chief-had-died-a-natural-death.}}

A bush chief had died a natural death.

\hypertarget{the-skippers-and-nakatas-gymnastics-served-as-a-translation-without-words.}{%
\subsection{The skipper's and Nakata's gymnastics served as a
translation without
words.}\label{the-skippers-and-nakatas-gymnastics-served-as-a-translation-without-words.}}

The skipper's and Nakata's gymnastics served as a translation without
words.

\hypertarget{last-night-he-showed-all-the-symptoms-of-coming-down-with-pneumonia.}{%
\subsection{Last night he showed all the symptoms of coming down with
pneumonia.}\label{last-night-he-showed-all-the-symptoms-of-coming-down-with-pneumonia.}}

Last night he showed all the symptoms of coming down with pneumonia.

\hypertarget{my-idea-was-that-he-would-have-more-influence-over-the-natives.}{%
\subsection{My idea was that he would have more influence over the
natives.}\label{my-idea-was-that-he-would-have-more-influence-over-the-natives.}}

My idea was that he would have more influence over the natives.

\hypertarget{it-is-merely-the-simple-superlative.}{%
\subsection{It is merely the simple
superlative.}\label{it-is-merely-the-simple-superlative.}}

It is merely the simple superlative.

\hypertarget{i-made-no-more-overtures.}{%
\subsection{I made no more overtures.}\label{i-made-no-more-overtures.}}

I made no more overtures.

\hypertarget{among-my-minor-afflictions-i-may-mention-a-new-and-mysterious-one.}{%
\subsection{Among my minor afflictions, I may mention a new and
mysterious
one.}\label{among-my-minor-afflictions-i-may-mention-a-new-and-mysterious-one.}}

Among my minor afflictions, I may mention a new and mysterious one.

\hypertarget{the-voyage-was-our-idea-of-a-good-time.}{%
\subsection{The voyage was our idea of a good
time.}\label{the-voyage-was-our-idea-of-a-good-time.}}

The voyage was our idea of a good time.

\hypertarget{at-sea-tuesday-march-17-1908.}{%
\subsection{At sea, Tuesday, March 17,
1908.}\label{at-sea-tuesday-march-17-1908.}}

At sea, Tuesday, March 17, 1908.

\hypertarget{yes-sir-he-answered-with-cheerful-alacrity.}{%
\subsection{Yes, sir, he answered, with cheerful
alacrity.}\label{yes-sir-he-answered-with-cheerful-alacrity.}}

Yes, sir, he answered, with cheerful alacrity.

\hypertarget{i-was-still-weak-from-my-prolonged-immersion.}{%
\subsection{I was still weak from my prolonged
immersion.}\label{i-was-still-weak-from-my-prolonged-immersion.}}

I was still weak from my prolonged immersion.

\hypertarget{the-boy-hesitated-then-mastered-his-temper.}{%
\subsection{The boy hesitated, then mastered his
temper.}\label{the-boy-hesitated-then-mastered-his-temper.}}

The boy hesitated, then mastered his temper.

\hypertarget{i-was-beneath-the-water-suffocating-and-drowning.}{%
\subsection{I was beneath the water, suffocating and
drowning.}\label{i-was-beneath-the-water-suffocating-and-drowning.}}

I was beneath the water, suffocating and drowning.

\hypertarget{the-pain-from-my-hurt-knee-was-agonizing.}{%
\subsection{The pain from my hurt knee was
agonizing.}\label{the-pain-from-my-hurt-knee-was-agonizing.}}

The pain from my hurt knee was agonizing.

\hypertarget{the-hunters-were-still-arguing-and-roaring-like-some-semi-human-amphibious-breed.}{%
\subsection{The hunters were still arguing and roaring like some
semi-human amphibious
breed.}\label{the-hunters-were-still-arguing-and-roaring-like-some-semi-human-amphibious-breed.}}

The hunters were still arguing and roaring like some semi-human
amphibious breed.

\hypertarget{i-have-been-robbed-sir-i-amended.}{%
\subsection{I have been robbed, sir, I
amended.}\label{i-have-been-robbed-sir-i-amended.}}

I have been robbed, sir, I amended.

\hypertarget{you-were-looking-squeamish-this-afternoon-he-began.}{%
\subsection{You were looking squeamish this afternoon, he
began.}\label{you-were-looking-squeamish-this-afternoon-he-began.}}

You were looking squeamish this afternoon, he began.

\hypertarget{how-could-i-answer-the-question-on-the-spur-of-the-moment.}{%
\subsection{How could I answer the question on the spur of the
moment.}\label{how-could-i-answer-the-question-on-the-spur-of-the-moment.}}

How could I answer the question on the spur of the moment.

\hypertarget{i-learned-it-myself-in-english-ships.}{%
\subsection{I learned it myself in English
ships.}\label{i-learned-it-myself-in-english-ships.}}

I learned it myself in English ships.

\hypertarget{an-altruistic-act-is-an-act-performed-for-the-welfare-of-others.}{%
\subsection{An altruistic act is an act performed for the welfare of
others.}\label{an-altruistic-act-is-an-act-performed-for-the-welfare-of-others.}}

An altruistic act is an act performed for the welfare of others.

\hypertarget{knowing-him-i-review-the-old-scandinavian-myths-with-clearer-understanding.}{%
\subsection{Knowing him, I review the old Scandinavian myths with
clearer
understanding.}\label{knowing-him-i-review-the-old-scandinavian-myths-with-clearer-understanding.}}

Knowing him, I review the old Scandinavian myths with clearer
understanding.

\hypertarget{yes-and-no-sir-was-the-slow-reply.}{%
\subsection{Yes, and no, sir, was the slow
reply.}\label{yes-and-no-sir-was-the-slow-reply.}}

Yes, and no, sir, was the slow reply.

\hypertarget{and-each-year-something-happened-and-i-did-not-go.}{%
\subsection{And each year something happened, and I did not
go.}\label{and-each-year-something-happened-and-i-did-not-go.}}

And each year something happened, and I did not go.

\hypertarget{how-in-hell-did-he-know-it-was-you-in-the-dark.}{%
\subsection{How in hell did he know it was you in the
dark.}\label{how-in-hell-did-he-know-it-was-you-in-the-dark.}}

How in hell did he know it was you in the dark.

\hypertarget{of-course-much-grumbling-went-on-and-little-outbursts-were-continually-occurring.}{%
\subsection{Of course much grumbling went on, and little outbursts were
continually
occurring.}\label{of-course-much-grumbling-went-on-and-little-outbursts-were-continually-occurring.}}

Of course much grumbling went on, and little outbursts were continually
occurring.

\hypertarget{you-have-all-the-advantage.}{%
\subsection{You have all the
advantage.}\label{you-have-all-the-advantage.}}

You have all the advantage.

\hypertarget{the-dirk-mentioned-by-wolf-larsen-rested-in-its-sheath-on-my-hip.}{%
\subsection{The dirk mentioned by Wolf Larsen rested in its sheath on my
hip.}\label{the-dirk-mentioned-by-wolf-larsen-rested-in-its-sheath-on-my-hip.}}

The dirk mentioned by Wolf Larsen rested in its sheath on my hip.

\hypertarget{have-you-ever-earned-a-dollar-by-your-own-labour.}{%
\subsection{Have you ever earned a dollar by your own
labour.}\label{have-you-ever-earned-a-dollar-by-your-own-labour.}}

Have you ever earned a dollar by your own labour.

\hypertarget{he-gave-no-reason-but-his-motive-was-obvious-enough.}{%
\subsection{He gave no reason, but his motive was obvious
enough.}\label{he-gave-no-reason-but-his-motive-was-obvious-enough.}}

He gave no reason, but his motive was obvious enough.

\hypertarget{ah-it-was-sweet-in-my-ears.}{%
\subsection{Ah, it was sweet in my
ears.}\label{ah-it-was-sweet-in-my-ears.}}

Ah, it was sweet in my ears.

\hypertarget{he-may-desire-to-escape-pain-or-to-enjoy-pleasure.}{%
\subsection{He may desire to escape pain, or to enjoy
pleasure.}\label{he-may-desire-to-escape-pain-or-to-enjoy-pleasure.}}

He may desire to escape pain, or to enjoy pleasure.

\hypertarget{it-was-impossible-to-hoist-sail-and-claw-off-that-shore.}{%
\subsection{It was impossible to hoist sail and claw off that
shore.}\label{it-was-impossible-to-hoist-sail-and-claw-off-that-shore.}}

It was impossible to hoist sail and claw off that shore.

\hypertarget{there-was-nothing-for-us-but-the-wide-raw-ocean.}{%
\subsection{There was nothing for us but the wide raw
ocean.}\label{there-was-nothing-for-us-but-the-wide-raw-ocean.}}

There was nothing for us but the wide raw ocean.

\hypertarget{i-arose-obediently-and-went-down-the-beach.}{%
\subsection{I arose obediently and went down the
beach.}\label{i-arose-obediently-and-went-down-the-beach.}}

I arose obediently and went down the beach.

\hypertarget{the-next-thing-to-watch-out-for-is-bed-sores.}{%
\subsection{The next thing to watch out for is bed
sores.}\label{the-next-thing-to-watch-out-for-is-bed-sores.}}

The next thing to watch out for is bed sores.

\hypertarget{at-that-moment-i-got-the-impression-that-she-was-willowy.}{%
\subsection{At that moment I got the impression that she was
willowy.}\label{at-that-moment-i-got-the-impression-that-she-was-willowy.}}

At that moment I got the impression that she was willowy.

\hypertarget{your-fathers-fifth-command-he-nodded.}{%
\subsection{Your father's fifth command, he
nodded.}\label{your-fathers-fifth-command-he-nodded.}}

Your father's fifth command, he nodded.

\hypertarget{on-occasion-on-this-traverse-the-cape-verde-islands-are-raised.}{%
\subsection{On occasion, on this traverse, the Cape Verde Islands are
raised.}\label{on-occasion-on-this-traverse-the-cape-verde-islands-are-raised.}}

On occasion, on this traverse, the Cape Verde Islands are raised.

\hypertarget{she-is-essentially-the-life-giving-life-conserving-female-of-the-species.}{%
\subsection{She is essentially the life-giving, life-conserving female
of the
species.}\label{she-is-essentially-the-life-giving-life-conserving-female-of-the-species.}}

She is essentially the life-giving, life-conserving female of the
species.

\hypertarget{this-was-when-the-explosion-occurred.}{%
\subsection{This was when the explosion
occurred.}\label{this-was-when-the-explosion-occurred.}}

This was when the explosion occurred.

\hypertarget{also-at-regular-intervals-he-would-mutter.}{%
\subsection{Also, at regular intervals, he would
mutter.}\label{also-at-regular-intervals-he-would-mutter.}}

Also, at regular intervals, he would mutter.

\hypertarget{it-is-a-very-tenable-hypothesis-and-will-bear-looking-into.}{%
\subsection{It is a very tenable hypothesis, and will bear looking
into.}\label{it-is-a-very-tenable-hypothesis-and-will-bear-looking-into.}}

It is a very tenable hypothesis, and will bear looking into.

\hypertarget{there-were-orange-green-gold-green-and-a-copper-green.}{%
\subsection{There were orange-green, gold-green, and a
copper-green.}\label{there-were-orange-green-gold-green-and-a-copper-green.}}

There were orange-green, gold-green, and a copper-green.

\hypertarget{the-gabriel-voice-of-the-samurai-rang-out.}{%
\subsection{The Gabriel voice of the Samurai rang
out.}\label{the-gabriel-voice-of-the-samurai-rang-out.}}

The Gabriel voice of the Samurai rang out.

\hypertarget{the-sunsets-grow-more-bizarre-and-spectacular-off-this-coast-of-the-argentine.}{%
\subsection{The sunsets grow more bizarre and spectacular off this coast
of the
Argentine.}\label{the-sunsets-grow-more-bizarre-and-spectacular-off-this-coast-of-the-argentine.}}

The sunsets grow more bizarre and spectacular off this coast of the
Argentine.

\hypertarget{the-history-of-our-westward-faring-race-is-written-in-it.}{%
\subsection{The history of our westward-faring race is written in
it.}\label{the-history-of-our-westward-faring-race-is-written-in-it.}}

The history of our westward-faring race is written in it.

\hypertarget{and-the-eurasian-chinese-englishman-bowed-himself-away.}{%
\subsection{And the Eurasian Chinese-Englishman bowed himself
away.}\label{and-the-eurasian-chinese-englishman-bowed-himself-away.}}

And the Eurasian Chinese-Englishman bowed himself away.

\hypertarget{they-were-babbling-and-chattering-all-together.}{%
\subsection{They were babbling and chattering all
together.}\label{they-were-babbling-and-chattering-all-together.}}

They were babbling and chattering all together.

\hypertarget{too-much-he-told-me-with-ominous-rolling-head.}{%
\subsection{Too much, he told me, with ominous rolling
head.}\label{too-much-he-told-me-with-ominous-rolling-head.}}

Too much, he told me, with ominous rolling head.

\hypertarget{he-is-a-candidate-rising-from-the-serf-class-to-our-class.}{%
\subsection{He is a candidate, rising from the serf class to our
class.}\label{he-is-a-candidate-rising-from-the-serf-class-to-our-class.}}

He is a candidate, rising from the serf class to our class.

\hypertarget{we-are-cooking-on-the-coal-stove-and-on-the-oil-burners.}{%
\subsection{We are cooking on the coal stove and on the oil
burners.}\label{we-are-cooking-on-the-coal-stove-and-on-the-oil-burners.}}

We are cooking on the coal stove and on the oil burners.

\hypertarget{the-steward-has-just-tendered-me-a-respectful-bit-of-advice.}{%
\subsection{The steward has just tendered me a respectful bit of
advice.}\label{the-steward-has-just-tendered-me-a-respectful-bit-of-advice.}}

The steward has just tendered me a respectful bit of advice.

\hypertarget{well-did-they-eat.}{%
\subsection{Well, did they eat.}\label{well-did-they-eat.}}

Well, did they eat.

\hypertarget{famine-had-been-my-great-ally.}{%
\subsection{Famine had been my great
ally.}\label{famine-had-been-my-great-ally.}}

Famine had been my great ally.

\hypertarget{nowhere-in-the-north-is-the-soil-so-prolific.}{%
\subsection{Nowhere in the North is the soil so
prolific.}\label{nowhere-in-the-north-is-the-soil-so-prolific.}}

Nowhere in the North is the soil so prolific.

\hypertarget{they-ran-the-canoe-in-and-climbed-the-high-earth-bank.}{%
\subsection{They ran the canoe in and climbed the high earth
bank.}\label{they-ran-the-canoe-in-and-climbed-the-high-earth-bank.}}

They ran the canoe in and climbed the high earth bank.

\hypertarget{the-land-exchanged-its-austere-robes-for-the-garb-of-a-smiling-wanton.}{%
\subsection{The land exchanged its austere robes for the garb of a
smiling
wanton.}\label{the-land-exchanged-its-austere-robes-for-the-garb-of-a-smiling-wanton.}}

The land exchanged its austere robes for the garb of a smiling wanton.

\hypertarget{there-were-stir-and-bustle-new-faces-and-fresh-facts.}{%
\subsection{There were stir and bustle, new faces, and fresh
facts.}\label{there-were-stir-and-bustle-new-faces-and-fresh-facts.}}

There were stir and bustle, new faces, and fresh facts.

\hypertarget{and-there-was-ethel-baird-whom-also-you-must-remember.}{%
\subsection{And there was Ethel Baird, whom also you must
remember.}\label{and-there-was-ethel-baird-whom-also-you-must-remember.}}

And there was Ethel Baird, whom also you must remember.

\hypertarget{he-had-become-a-man-very-early-in-life.}{%
\subsection{He had become a man very early in
life.}\label{he-had-become-a-man-very-early-in-life.}}

He had become a man very early in life.

\hypertarget{i-did-not-think-you-would-be-so-early.}{%
\subsection{I did not think you would be so
early.}\label{i-did-not-think-you-would-be-so-early.}}

I did not think you would be so early.

\hypertarget{he-did-not-know-what-went-on-in-the-minds-of-his-superiors.}{%
\subsection{He did not know what went on in the minds of his
superiors.}\label{he-did-not-know-what-went-on-in-the-minds-of-his-superiors.}}

He did not know what went on in the minds of his superiors.

\hypertarget{mops-sir-eagerly-answered-the-sailor-at-the-wheel.}{%
\subsection{Mops, sir, eagerly answered the sailor at the
wheel.}\label{mops-sir-eagerly-answered-the-sailor-at-the-wheel.}}

Mops, sir, eagerly answered the sailor at the wheel.

\hypertarget{some-one-had-thrust-a-large-sheath-knife-into-his-hand.}{%
\subsection{Some one had thrust a large sheath-knife into his
hand.}\label{some-one-had-thrust-a-large-sheath-knife-into-his-hand.}}

Some one had thrust a large sheath-knife into his hand.

\hypertarget{obrien-emitted-a-shriek-that-sank-swiftly-to-a-gurgling-sob.}{%
\subsection{O'Brien emitted a shriek that sank swiftly to a gurgling
sob.}\label{obrien-emitted-a-shriek-that-sank-swiftly-to-a-gurgling-sob.}}

O'Brien emitted a shriek that sank swiftly to a gurgling sob.

\hypertarget{sandel-would-never-become-a-world-champion.}{%
\subsection{Sandel would never become a world
champion.}\label{sandel-would-never-become-a-world-champion.}}

Sandel would never become a world champion.

\hypertarget{also-she-wouldnt-walk.}{%
\subsection{Also, she wouldn't walk.}\label{also-she-wouldnt-walk.}}

Also, she wouldn't walk.

\hypertarget{to-my-dearest-and-always-appreciated-friend-i-submit-myself.}{%
\subsection{To my dearest and always appreciated friend, I submit
myself.}\label{to-my-dearest-and-always-appreciated-friend-i-submit-myself.}}

To my dearest and always appreciated friend, I submit myself.

\hypertarget{you-used-to-joyride-like-the-very-devil.}{%
\subsection{You used to joyride like the very
devil.}\label{you-used-to-joyride-like-the-very-devil.}}

You used to joyride like the very devil.

\hypertarget{they-saw-each-other-for-the-first-time-in-boston.}{%
\subsection{They saw each other for the first time in
Boston.}\label{they-saw-each-other-for-the-first-time-in-boston.}}

They saw each other for the first time in Boston.

\hypertarget{isaac-ford-the-austere-soldier-of-the-lord-the-old-hypocrite.}{%
\subsection{Isaac Ford, the austere soldier of the Lord, the old
hypocrite.}\label{isaac-ford-the-austere-soldier-of-the-lord-the-old-hypocrite.}}

Isaac Ford, the austere soldier of the Lord, the old hypocrite.

\hypertarget{eighteen-he-added.}{%
\subsection{Eighteen, he added.}\label{eighteen-he-added.}}

Eighteen, he added.

\hypertarget{his-reward-should-have-been-peace-and-repose.}{%
\subsection{His reward should have been peace and
repose.}\label{his-reward-should-have-been-peace-and-repose.}}

His reward should have been peace and repose.

\hypertarget{he-was-an-amphibian-and-a-mountaineer.}{%
\subsection{He was an amphibian and a
mountaineer.}\label{he-was-an-amphibian-and-a-mountaineer.}}

He was an amphibian and a mountaineer.

\hypertarget{it-was-sanctification-and-salvation.}{%
\subsection{It was sanctification and
salvation.}\label{it-was-sanctification-and-salvation.}}

It was sanctification and salvation.

\hypertarget{the-history-of-the-eighteenth-century-is-written-ernest-prompted.}{%
\subsection{The history of the eighteenth century is written, Ernest
prompted.}\label{the-history-of-the-eighteenth-century-is-written-ernest-prompted.}}

The history of the eighteenth century is written, Ernest prompted.

\hypertarget{they-are-not-biologists-nor-sociologists.}{%
\subsection{They are not biologists nor
sociologists.}\label{they-are-not-biologists-nor-sociologists.}}

They are not biologists nor sociologists.

\hypertarget{the-more-his-opponents-grew-excited-the-more-ernest-deliberately-excited-them.}{%
\subsection{The more his opponents grew excited, the more Ernest
deliberately excited
them.}\label{the-more-his-opponents-grew-excited-the-more-ernest-deliberately-excited-them.}}

The more his opponents grew excited, the more Ernest deliberately
excited them.

\hypertarget{by-virtue-of-that-power-we-shall-remain-in-power.}{%
\subsection{By virtue of that power we shall remain in
power.}\label{by-virtue-of-that-power-we-shall-remain-in-power.}}

By virtue of that power we shall remain in power.

\hypertarget{one-guess-will-do-ernest-retorted.}{%
\subsection{One guess will do, Ernest
retorted.}\label{one-guess-will-do-ernest-retorted.}}

One guess will do, Ernest retorted.

\hypertarget{take-my-advice-and-accept-the-vacation.}{%
\subsection{Take my advice and accept the
vacation.}\label{take-my-advice-and-accept-the-vacation.}}

Take my advice and accept the vacation.

\hypertarget{i-could-not-agree-with-ernest.}{%
\subsection{I could not agree with
Ernest.}\label{i-could-not-agree-with-ernest.}}

I could not agree with Ernest.

\hypertarget{but-such-divergence-of-opinion-would-constitute-no-menace-to-society.}{%
\subsection{But such divergence of opinion would constitute no menace to
society.}\label{but-such-divergence-of-opinion-would-constitute-no-menace-to-society.}}

But such divergence of opinion would constitute no menace to society.

\hypertarget{it-is-dog-eat-dog-and-you-ate-them-up.}{%
\subsection{It is dog eat dog, and you ate them
up.}\label{it-is-dog-eat-dog-and-you-ate-them-up.}}

It is dog eat dog, and you ate them up.

\hypertarget{let-us-run-them-for-ourselves.}{%
\subsection{Let us run them for
ourselves.}\label{let-us-run-them-for-ourselves.}}

Let us run them for ourselves.

\hypertarget{it-was-introduced-by-representative-dick-of-ohio.}{%
\subsection{It was introduced by Representative Dick of
Ohio.}\label{it-was-introduced-by-representative-dick-of-ohio.}}

It was introduced by Representative Dick of Ohio.

\hypertarget{very-few-people-knew-of-the-existence-of-this-law.}{%
\subsection{Very few people knew of the existence of this
law.}\label{very-few-people-knew-of-the-existence-of-this-law.}}

Very few people knew of the existence of this law.

\hypertarget{the-very-thing-ernest-agreed.}{%
\subsection{The very thing, Ernest
agreed.}\label{the-very-thing-ernest-agreed.}}

The very thing, Ernest agreed.

\hypertarget{also-a-fellow-senator-chauncey-depew-said.}{%
\subsection{Also a fellow Senator, Chauncey Depew,
said.}\label{also-a-fellow-senator-chauncey-depew-said.}}

Also a fellow Senator, Chauncey Depew, said.

\hypertarget{ernest-saw-in-the-affair-the-most-sinister-import.}{%
\subsection{Ernest saw in the affair the most sinister
import.}\label{ernest-saw-in-the-affair-the-most-sinister-import.}}

Ernest saw in the affair the most sinister import.

\hypertarget{then-there-was-the-campaign.}{%
\subsection{Then there was the
campaign.}\label{then-there-was-the-campaign.}}

Then there was the campaign.

\hypertarget{he-was-manifestly-distressed-by-my-coming.}{%
\subsection{He was manifestly distressed by my
coming.}\label{he-was-manifestly-distressed-by-my-coming.}}

He was manifestly distressed by my coming.

\hypertarget{not-a-wheel-moved-in-his-empire.}{%
\subsection{Not a wheel moved in his
empire.}\label{not-a-wheel-moved-in-his-empire.}}

Not a wheel moved in his empire.

\hypertarget{the-reorganization-of-these-countries-took-the-form-of-revolution.}{%
\subsection{The reorganization of these countries took the form of
revolution.}\label{the-reorganization-of-these-countries-took-the-form-of-revolution.}}

The reorganization of these countries took the form of revolution.

\hypertarget{youre-going-in-for-grab-sharing.}{%
\subsection{You're going in for grab
sharing.}\label{youre-going-in-for-grab-sharing.}}

You're going in for grab sharing.

\hypertarget{the-oligarchy-will-encourage-such-ambition-and-the-consequent-competition.}{%
\subsection{The Oligarchy will encourage such ambition and the
consequent
competition.}\label{the-oligarchy-will-encourage-such-ambition-and-the-consequent-competition.}}

The Oligarchy will encourage such ambition and the consequent
competition.

\hypertarget{violation-of-this-law-was-made-a-high-misdemeanor-and-punished-accordingly.}{%
\subsection{Violation of this law was made a high misdemeanor and
punished
accordingly.}\label{violation-of-this-law-was-made-a-high-misdemeanor-and-punished-accordingly.}}

Violation of this law was made a high misdemeanor and punished
accordingly.

\hypertarget{without-discussion-it-was-the-agents-provocateurs-who-caused-the-peasant-revolt.}{%
\subsection{Without discussion, it was the agents provocateurs who
caused the Peasant
Revolt.}\label{without-discussion-it-was-the-agents-provocateurs-who-caused-the-peasant-revolt.}}

Without discussion, it was the agents provocateurs who caused the
Peasant Revolt.

\hypertarget{the-task-we-set-ourselves-was-threefold.}{%
\subsection{The task we set ourselves was
threefold.}\label{the-task-we-set-ourselves-was-threefold.}}

The task we set ourselves was threefold.

\hypertarget{many-other-similar-disconcerting-omissions-will-be-noticed-in-the-manuscript.}{%
\subsection{Many other similar disconcerting omissions will be noticed
in the
Manuscript.}\label{many-other-similar-disconcerting-omissions-will-be-noticed-in-the-manuscript.}}

Many other similar disconcerting omissions will be noticed in the
Manuscript.

\hypertarget{the-flower-of-the-artistic-and-intellectual-world-were-revolutionists.}{%
\subsection{The flower of the artistic and intellectual world were
revolutionists.}\label{the-flower-of-the-artistic-and-intellectual-world-were-revolutionists.}}

The flower of the artistic and intellectual world were revolutionists.

\hypertarget{this-the-iron-heel-foresaw-and-laid-its-schemes-accordingly.}{%
\subsection{This the Iron Heel foresaw and laid its schemes
accordingly.}\label{this-the-iron-heel-foresaw-and-laid-its-schemes-accordingly.}}

This the Iron Heel foresaw and laid its schemes accordingly.

\hypertarget{the-mob-came-on-but-it-could-not-advance.}{%
\subsection{The mob came on, but it could not
advance.}\label{the-mob-came-on-but-it-could-not-advance.}}

The mob came on, but it could not advance.

\hypertarget{but-why-continue-the-tirade-for-tirade-it-was.}{%
\subsection{But why continue the tirade, for tirade it
was.}\label{but-why-continue-the-tirade-for-tirade-it-was.}}

But why continue the tirade, for tirade it was.

\hypertarget{after-all-superfluous-flesh-is-gone-what-is-left-is-stringy-and-resistant.}{%
\subsection{After all superfluous flesh is gone what is left is stringy
and
resistant.}\label{after-all-superfluous-flesh-is-gone-what-is-left-is-stringy-and-resistant.}}

After all superfluous flesh is gone what is left is stringy and
resistant.

\hypertarget{beyond-refusing-to-sell-us-food-they-left-us-to-ourselves.}{%
\subsection{Beyond refusing to sell us food, they left us to
ourselves.}\label{beyond-refusing-to-sell-us-food-they-left-us-to-ourselves.}}

Beyond refusing to sell us food, they left us to ourselves.

\hypertarget{he-was-a-merry-monarch-especially-so-for-an-asiatic.}{%
\subsection{He was a merry monarch, especially so for an
Asiatic.}\label{he-was-a-merry-monarch-especially-so-for-an-asiatic.}}

He was a merry monarch, especially so for an Asiatic.

\hypertarget{what-an-excited-whispering-and-conferring-took-place.}{%
\subsection{What an excited whispering and conferring took
place.}\label{what-an-excited-whispering-and-conferring-took-place.}}

What an excited whispering and conferring took place.

\hypertarget{jacob-brinker-who-was-his-roadmate-brought-the-news.}{%
\subsection{Jacob Brinker, who was his roadmate, brought the
news.}\label{jacob-brinker-who-was-his-roadmate-brought-the-news.}}

Jacob Brinker, who was his roadmate, brought the news.

\hypertarget{thus-he-turned-the-tenets-and-jargon-of-psychology-back-on-me.}{%
\subsection{Thus he turned the tenets and jargon of psychology back on
me.}\label{thus-he-turned-the-tenets-and-jargon-of-psychology-back-on-me.}}

Thus he turned the tenets and jargon of psychology back on me.

\hypertarget{you-yellow-giant-thing-of-the-frost.}{%
\subsection{You yellow giant thing of the
frost.}\label{you-yellow-giant-thing-of-the-frost.}}

You yellow giant thing of the frost.

\hypertarget{never-so-strange-a-prophet-came-up-to-jerusalem.}{%
\subsection{Never so strange a prophet came up to
Jerusalem.}\label{never-so-strange-a-prophet-came-up-to-jerusalem.}}

Never so strange a prophet came up to Jerusalem.

\hypertarget{we-who-have-endured-so-much-surely-can-endure-a-little-more.}{%
\subsection{We who have endured so much surely can endure a little
more.}\label{we-who-have-endured-so-much-surely-can-endure-a-little-more.}}

We who have endured so much surely can endure a little more.

\hypertarget{i-have-seen-myself-that-one-man-contemplated-by-pascals-philosophic-eye.}{%
\subsection{I have seen myself that one man contemplated by Pascal's
philosophic
eye.}\label{i-have-seen-myself-that-one-man-contemplated-by-pascals-philosophic-eye.}}

I have seen myself that one man contemplated by Pascal's philosophic
eye.

\hypertarget{one-great-drawback-to-farming-in-california-is-our-long-dry-summer.}{%
\subsection{One great drawback to farming in California is our long dry
summer.}\label{one-great-drawback-to-farming-in-california-is-our-long-dry-summer.}}

One great drawback to farming in California is our long dry summer.

\hypertarget{i-remembered-the-red-wine-of-the-italian-rancho-and-shuddered-inwardly.}{%
\subsection{I remembered the red wine of the Italian rancho, and
shuddered
inwardly.}\label{i-remembered-the-red-wine-of-the-italian-rancho-and-shuddered-inwardly.}}

I remembered the red wine of the Italian rancho, and shuddered inwardly.

\hypertarget{i-said-and-dismissed-the-matter-as-not-worth-thinking-about.}{%
\subsection{I said, and dismissed the matter as not worth thinking
about.}\label{i-said-and-dismissed-the-matter-as-not-worth-thinking-about.}}

I said, and dismissed the matter as not worth thinking about.

\hypertarget{then-came-my-boy-code.}{%
\subsection{Then came my boy code.}\label{then-came-my-boy-code.}}

Then came my boy code.

\hypertarget{and-wherever-i-ranged-the-way-lay-along-alcohol-drenched-roads.}{%
\subsection{And wherever I ranged, the way lay along alcohol-drenched
roads.}\label{and-wherever-i-ranged-the-way-lay-along-alcohol-drenched-roads.}}

And wherever I ranged, the way lay along alcohol-drenched roads.

\hypertarget{and-as-we-hurried-up-town-joe-goose-explained.}{%
\subsection{And as we hurried up town, Joe Goose
explained.}\label{and-as-we-hurried-up-town-joe-goose-explained.}}

And as we hurried up town, Joe Goose explained.

\hypertarget{the-scents-of-strange-vegetation-blew-off-the-tropic-land.}{%
\subsection{The scents of strange vegetation blew off the tropic
land.}\label{the-scents-of-strange-vegetation-blew-off-the-tropic-land.}}

The scents of strange vegetation blew off the tropic land.

\hypertarget{the-life-there-was-healthful-and-athletic-but-too-juvenile.}{%
\subsection{The life there was healthful and athletic, but too
juvenile.}\label{the-life-there-was-healthful-and-athletic-but-too-juvenile.}}

The life there was healthful and athletic, but too juvenile.

\hypertarget{how-valiantly-i-went-at-it-that-first-day.}{%
\subsection{How valiantly I went at it that first
day.}\label{how-valiantly-i-went-at-it-that-first-day.}}

How valiantly I went at it that first day.

\hypertarget{it-would-help-to-tide-me-along-until-i-got-steady-employment.}{%
\subsection{It would help to tide me along until I got steady
employment.}\label{it-would-help-to-tide-me-along-until-i-got-steady-employment.}}

It would help to tide me along until I got steady employment.

\hypertarget{did-i-possess-too-much-vitality.}{%
\subsection{Did I possess too much
vitality.}\label{did-i-possess-too-much-vitality.}}

Did I possess too much vitality.

\hypertarget{in-his-anxiety-and-solicitude-and-love-they-did-not-count.}{%
\subsection{In his anxiety and solicitude and love they did not
count.}\label{in-his-anxiety-and-solicitude-and-love-they-did-not-count.}}

In his anxiety and solicitude and love they did not count.

\hypertarget{he-had-fulfilled-his-duty-and-paid-properly.}{%
\subsection{He had fulfilled his duty and paid
properly.}\label{he-had-fulfilled-his-duty-and-paid-properly.}}

He had fulfilled his duty and paid properly.

\hypertarget{he-knew-what-taboos-he-was-violating.}{%
\subsection{He knew what taboos he was
violating.}\label{he-knew-what-taboos-he-was-violating.}}

He knew what taboos he was violating.

\hypertarget{do-you-value-your-hide.}{%
\subsection{Do you value your hide.}\label{do-you-value-your-hide.}}

Do you value your hide.

\hypertarget{you-should-have-seen-them-when-they-heard-me-spitting-chinook.}{%
\subsection{You should have seen them when they heard me spitting
Chinook.}\label{you-should-have-seen-them-when-they-heard-me-spitting-chinook.}}

You should have seen them when they heard me spitting Chinook.

\hypertarget{he-plodded-on-for-half-an-hour-when-the-hallucination-arose-again.}{%
\subsection{He plodded on for half an hour, when the hallucination arose
again.}\label{he-plodded-on-for-half-an-hour-when-the-hallucination-arose-again.}}

He plodded on for half an hour, when the hallucination arose again.

\hypertarget{tomorrow-or-next-day-it-might-he-gone.}{%
\subsection{Tomorrow or next day it might he
gone.}\label{tomorrow-or-next-day-it-might-he-gone.}}

Tomorrow or next day it might he gone.

\hypertarget{but-already-he-had-composed-himself.}{%
\subsection{But already he had composed
himself.}\label{but-already-he-had-composed-himself.}}

But already he had composed himself.

\hypertarget{zilla-relaxed-her-sour-mouth-long-enough-to-sigh-her-satisfaction.}{%
\subsection{Zilla relaxed her sour mouth long enough to sigh her
satisfaction.}\label{zilla-relaxed-her-sour-mouth-long-enough-to-sigh-her-satisfaction.}}

Zilla relaxed her sour mouth long enough to sigh her satisfaction.

\hypertarget{eggshell-is-not-good-to-eat.}{%
\subsection{Eggshell is not good to
eat.}\label{eggshell-is-not-good-to-eat.}}

Eggshell is not good to eat.

\hypertarget{but-there-was-also-talk-of-witchcraft-in-the-village.}{%
\subsection{But there was also talk of witchcraft in the
village.}\label{but-there-was-also-talk-of-witchcraft-in-the-village.}}

But there was also talk of witchcraft in the village.

\hypertarget{yea-i-will-tell-thee.}{%
\subsection{Yea, I will tell thee.}\label{yea-i-will-tell-thee.}}

Yea, I will tell thee.

\hypertarget{hans-hurled-himself-upon-the-prostrate-man-striking-madly-with-his-fists.}{%
\subsection{Hans hurled himself upon the prostrate man, striking madly
with his
fists.}\label{hans-hurled-himself-upon-the-prostrate-man-striking-madly-with-his-fists.}}

Hans hurled himself upon the prostrate man, striking madly with his
fists.

\hypertarget{and-he-thought-of-oona-and-of-her-words.}{%
\subsection{And he thought of Oona, and of her
words.}\label{and-he-thought-of-oona-and-of-her-words.}}

And he thought of Oona, and of her words.

\hypertarget{nor-would-it-thaw-out-his-hands-and-feet.}{%
\subsection{Nor would it thaw out his hands and
feet.}\label{nor-would-it-thaw-out-his-hands-and-feet.}}

Nor would it thaw out his hands and feet.

\hypertarget{the-russian-music-player-the-count-was-her-obedient-slave.}{%
\subsection{The Russian music player, the Count, was her obedient
slave.}\label{the-russian-music-player-the-count-was-her-obedient-slave.}}

The Russian music player, the Count, was her obedient slave.

\hypertarget{so-far-as-flags-were-concerned-they-were-beyond-all-jurisdiction.}{%
\subsection{So far as flags were concerned, they were beyond all
jurisdiction.}\label{so-far-as-flags-were-concerned-they-were-beyond-all-jurisdiction.}}

So far as flags were concerned, they were beyond all jurisdiction.

\hypertarget{new-idea-he-volunteered-brand-new-idea.}{%
\subsection{New idea, he volunteered, brand new
idea.}\label{new-idea-he-volunteered-brand-new-idea.}}

New idea, he volunteered, brand new idea.

\hypertarget{thirty-pounds-said-the-captain-with-finality.}{%
\subsection{Thirty pounds, said the captain with
finality.}\label{thirty-pounds-said-the-captain-with-finality.}}

Thirty pounds, said the captain with finality.

\hypertarget{the-very-idea-of-it-was-preposterous.}{%
\subsection{The very idea of it was
preposterous.}\label{the-very-idea-of-it-was-preposterous.}}

The very idea of it was preposterous.

\hypertarget{captain-doanes-orders-were-swiftly-obeyed.}{%
\subsection{Captain Doane's orders were swiftly
obeyed.}\label{captain-doanes-orders-were-swiftly-obeyed.}}

Captain Doane's orders were swiftly obeyed.

\hypertarget{come-on-del-mar-challenged.}{%
\subsection{Come on, Del Mar
challenged.}\label{come-on-del-mar-challenged.}}

Come on, Del Mar challenged.

\hypertarget{he-had-a-big-chimpanzee-that-was-a-winner.}{%
\subsection{He had a big chimpanzee that was a
winner.}\label{he-had-a-big-chimpanzee-that-was-a-winner.}}

He had a big chimpanzee that was a winner.

\hypertarget{i-am-sure-it-must-have-been-some-adventure.}{%
\subsection{I am sure it must have been some
adventure.}\label{i-am-sure-it-must-have-been-some-adventure.}}

I am sure it must have been some adventure.

\hypertarget{that-longfellow-chap-most-likely-had-written-countless-books-of-poetry.}{%
\subsection{That Longfellow chap most likely had written countless books
of
poetry.}\label{that-longfellow-chap-most-likely-had-written-countless-books-of-poetry.}}

That Longfellow chap most likely had written countless books of poetry.

\hypertarget{his-abnormal-power-of-vision-made-abstractions-take-on-concrete-form.}{%
\subsection{His abnormal power of vision made abstractions take on
concrete
form.}\label{his-abnormal-power-of-vision-made-abstractions-take-on-concrete-form.}}

His abnormal power of vision made abstractions take on concrete form.

\hypertarget{ill-tell-you-the-librarian-said-with-a-brightening-face.}{%
\subsection{I'll tell you, the librarian said with a brightening
face.}\label{ill-tell-you-the-librarian-said-with-a-brightening-face.}}

I'll tell you, the librarian said with a brightening face.

\hypertarget{he-read-his-fragments-aloud.}{%
\subsection{He read his fragments
aloud.}\label{he-read-his-fragments-aloud.}}

He read his fragments aloud.

\hypertarget{typhoid-did-i-tell-you.}{%
\subsection{Typhoid -- did I tell you.}\label{typhoid-did-i-tell-you.}}

Typhoid -- did I tell you.

\hypertarget{but-she-had-become-an-automaton.}{%
\subsection{But she had become an
automaton.}\label{but-she-had-become-an-automaton.}}

But she had become an automaton.

\hypertarget{at-the-best-they-were-necessary-accessories.}{%
\subsection{At the best, they were necessary
accessories.}\label{at-the-best-they-were-necessary-accessories.}}

At the best, they were necessary accessories.

\hypertarget{you-were-making-them-talk-shop-ruth-charged-him.}{%
\subsection{You were making them talk shop, Ruth charged
him.}\label{you-were-making-them-talk-shop-ruth-charged-him.}}

You were making them talk shop, Ruth charged him.

\end{document}
